### 2022-10-08 source/paper/main.tex
Upload DDIV and main.tex

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{float}
\usepackage{subfig}
\usepackage{lscape} 
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage[authoryear]{natbib}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage[bottom]{footmisc}
\newcommand{\indep}{\perp \!\!\! \perp}
\usepackage[nolist]{acronym}
\newcommand\headercell[1]{%
   \smash[b]{\begin{tabular}[t]{@{}c@{}} #1 \end{tabular}}}
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
\usepackage{xcolor}%
\definecolor{webbrown}{rgb}{.6,0,0}
\usepackage{hyperref}%
\hypersetup{%
  breaklinks = true,%
  colorlinks = true,%
  anchorcolor = webbrown,%
  citecolor = webbrown,%
  filecolor = webbrown,%
  linkcolor = webbrown,%
  menucolor = webbrown,%
  urlcolor= webbrown,%
  citebordercolor= 1 0 0,%
  menubordercolor=1 0 0,%
  urlbordercolor=1 0 0,%
  runbordercolor=1 0 0,}
\usepackage{cleveref}

\usepackage{setspace}
\setstretch{1.5} %% set line spacing
\usepackage{booktabs}
\newcommand{\tabnotes}[2]{\bottomrule \multicolumn{#1}{@{}p{0.70\linewidth}@{}}{\footnotesize #2 }\end{tabular}\end{table}}

\begin{acronym}
  \acro{CI}{confidence interval}
  \acro{RCT}{randomized controlled trial}
  \acro{IV}{instrumental variable}
  \acro{LATE}{local average treatment effect}
  \acro{ATE}{average treatment effect}
  \acro{OLS}{ordinary least squares}
  \acro{RD}{regression discontinuity}
  \acro{MTE}{marginal treatment effect}
  \acro{ATT}{average treatment effect on the treated}
\end{acronym}

\title{TITLE:\texorpdfstring{\\}{} subtitle}
\author{Ray Huang\thanks{Contact:
    \href{mailto:ray_huang@brown.edu}{ray\_huang@brown.edu}.
     I thank Peter Hull at Brown University for serving as my advisor and for providing me with fantastic feedback.}
     \\Brown University, Honors Thesis}

\date{\today}

\begin{document}

\maketitle

\begin{abstract}
\noindent Aspirational abstract goes here
\end{abstract}

\clearpage

\section*{Introduction}

\section*{Motivation and Background}

\section*{Data description}

\section*{Empirical/Econometric Methods, Hypotheses tested}

%%%%%%%%%%%%%%%%%%%%%%%%BIB%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\singlespacing
\bibliographystyle{jpe}
\bibliography{cite.bib}

%%%%%%%%%%%%%%%%%%%%%%%%FIGURES%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage

\end{document}

### 2022-11-23 source/cleaning/construct_ucr_icpsr.py
#13 Clean icpsr ucr data

@@ -1,0 +1,39 @@
+import pandas as pd
+import time
+
+# Runtime: ~115 seconds
+def main():
+    # Load TSVs into ucr_dfs list as dataframes
+    ucr_dfs = []
+    ucr_years = [1982, 1983, 1984, 1985, 1986, 1987, 1988, 1989, 1990, 1991, 1992]
+    for ucr_year in ucr_years:
+        ucr_dfs.append(pd.read_csv('../../data/UCR_ICPSR/raw/icpsr_' + str(ucr_year) + '.tsv', sep='\t'))
+    # Clean each df
+    cleaned_dfs = []
+    for ucr_df in ucr_dfs:
+        ucr_df = groupby_state(drop_rows(ucr_df))
+        cleaned_dfs.append(ucr_df)
+    output = concatenate_dfs_vertically(cleaned_dfs)
+    # Export final df to csv
+    output.to_csv('../../data/UCR_ICPSR/clean/icpsr_ucr_all_yrs.csv')
+
+def drop_rows(df):
+    """ Drop rows not looking at possession of marijuana for a single df """
+    # Note: different years use different offense codes (mainly 1981)
+    return df.drop(df[(df.OFFENSE != '187') & (df.OFFENSE != '18F')].index)
+
+def groupby_state(df):
+    """ Group a dataframe by groupby_param """
+    var_names = {'YEAR':'year', 'POP':'pop', 'JW':'jw', 'JB':'jb', 'AW':'aw', 'AB':'ab'}
+    agg_input = {'YEAR':'mean', 'POP':'sum','JW':'sum', 'JB':'sum', 'AW':'sum', 'AB':'sum'}
+    grouped_df = df.groupby('STATE', as_index=False).agg(agg_input).rename(columns=var_names)
+    return grouped_df
+
+def concatenate_dfs_vertically(dfs):
+    """ Group all the dfs into one df """
+    return pd.concat(dfs, ignore_index=True)
+
+if __name__ == "__main__":
+    start_time = time.time()
+    main()
+    print("--- %s seconds ---" % (time.time() - start_time))()

### 2022-11-23 source/data_cleaning/ucr_clean.py

@@ -1,10 +1,0 @@
-import pandas as pd
-
-# Create list of filenames
-ucr_years = []
-for i in range(1980, 2015):
-    file_name = 'ucr_' + str(i)
-    ucr_years.append(file_name)
-
-for ucr_year in ucr_years:
-    arrests = pd.read_excel("../../Data/UCR/" + ucr_year + ".xls", engine='openpyxl')

### 2022-11-23 source/figures/britton_fig2.py

@@ -33,11 +33,6 @@ def gen_ucr_years(lb=1980, rb=2015):
     return ucr_years
 
 
-def clean_drop(arrest_datas:list):
-    for arrest_data in arrest_datas:
-        arrest_data = arrest_data.drop([36])
-
-
 def get_yaxis_data(ucr_year, age, race, offense_index=21):
     """ Get the data for plotting from a single year """
     # Check age
@@ -61,7 +56,7 @@ def get_yaxis_data(ucr_year, age, race, offense_index=21):
 def plot(y1, y2, y3, y4, t1, t2, t3, t4, title, outfile, y_label='Possession', x_label='Year'):
     plt.figure(figsize=(10, 10))
     xaxis = np.linspace(1980, 2014, 35)
-    # Overlay 4 plots
+    # Overlay plots
     plt.plot(xaxis, y1, linewidth=3, label=t1)
     plt.plot(xaxis, y2, linewidth=3, label=t2)
     plt.plot(xaxis, y3, linewidth=3, label=t3)

### 2022-11-23 source/cleaning/construct_ucr_icpsr.py
Update gitignore
Ignore csv and xlsx

@@ -15,7 +15,7 @@ def main():
         cleaned_dfs.append(ucr_df)
     output = concatenate_dfs_vertically(cleaned_dfs)
     # Export final df to csv
-    output.to_csv('../../data/UCR_ICPSR/clean/icpsr_ucr_all_yrs.csv')
+    output.to_csv('../../data/UCR_ICPSR/clean/icpsr_ucr_all_yrs.csv', index=False)
 
 def drop_rows(df):
     """ Drop rows not looking at possession of marijuana for a single df """

### 2022-11-25 source/cleaning/construct_ucr_icpsr.py
#13 Create table 2 and 3

@@ -1,7 +1,7 @@
 import pandas as pd
 import time
 
-# Runtime: ~115 seconds
+# Runtime: ~110 seconds
 def main():
     # Load TSVs into ucr_dfs list as dataframes
     ucr_dfs = []

### 2022-11-25 source/cleaning/groupby_state_cps.py
#9 Update data cleaning files

@@ -1,0 +1,14 @@
+import pandas as pd
+
+# Data is at the individual state-year level
+cps_educ = pd.read_stata("../../data/CPS/cps_educ.dta")
+print(cps_educ)
+
+def groupby_state_year(df):
+    """ Group a dataframe by groupby_param """
+    var_names = {'YEAR':'year', 'POP':'pop', 'JW':'jw', 'JB':'jb', 'AW':'aw', 'AB':'ab'}
+    agg_input = {'YEAR':'mean', 'POP':'sum','JW':'sum', 'JB':'sum', 'AW':'sum', 'AB':'sum'}
+    grouped_df = df.groupby(['statefip', 'year'], as_index=False).agg(agg_input).rename(columns=var_names)
+    return grouped_df
+
+#cps_educ_grouped = groupby_state_year(cps_educ)

### 2022-12-07 source/talk/dec_slides_overleaf/main.tex
#17 Upload slide files

\documentclass{beamer}
\usepackage{subfig}
\usepackage{epigraph} 
\usetheme{Madrid}
\usecolortheme{default}

%Information to be included in the title page:
\title{Changes in Drug Laws and College Enrollment}
\author{Ray Huang}
\institute{Senior Thesis}
\date{December 7, 2022}

\begin{document}

\frame{\titlepage}

%------------------------------------------------------------

\begin{frame}
\frametitle{Motivation}
\begin{quote}
  There’s 2.2 million people in the American prison system, and half a million of those are locked up for drug offenses. A lot of them were in the same boat as me: victims of the mandatory minimum... It’s the reason hundreds of thousands of nonviolent people—mostly black and brown people-- are rotting in prison. Rotting like the baloney and cheese sandwiches they serve for breakfast, lunch, and dinner...

  I’d been in prison for ten years by the time my petition reached the Supreme Court.
\end{quote}
\hspace*{\fill} - John Gargano, HONY
\end{frame}

%------------------------------------------------------------

\begin{frame}
\frametitle{Background I}
\begin{itemize}
    \item Anti-Drug Abuse Act of 1986 established mandatory sentencing minimums (with disparities across drugs)
    \begin{itemize}
        \item Increase in average time imprisoned for drug crimes from 22 months to 33 months
        \item Number of black people sent to federal prison skyrocketed from approximately 50 to 250 in 100,000 adults (Equal Justice Initiative)
    \end{itemize}
    \item Fair Sentencing Act of 2010 reduced disparities in sentencing and eliminated mandatory minimums
    \item Disparities in college attainment across race and gender have maintained across time
\end{itemize}
\end{frame}

%------------------------------------------------------------

\begin{frame}{Background II}
    \begin{figure}%
    \centering
    \subfloat[\centering College enrollment rates]{{\includegraphics[width=5cm]{britton_fig1.png} }}%
    \qquad
    \subfloat[\centering Drug possession arrest rate (per 100,000)]{{\includegraphics[width=5cm]{britton_fig2.png} }}%
    \caption{Education and possession trends over time (Britton, 2022)}
    \label{fig:example}%
\end{figure}
\end{frame}

%------------------------------------------------------------

\begin{frame}{Research questions}
    \begin{enumerate}
        \item Did the passage of the federal Anti-Drug Abuse Act of 1986 cause a fall in relative college enrollment for Black male students?
        \item Did the passage of the federal Fair Sentencing Act of 2010 cause an increase in relative college enrollment for Black male students?
    \end{enumerate}
\end{frame}

%------------------------------------------------------------

\begin{frame}
\frametitle{Data sources}
\begin{itemize}
  \item October Current Population Survey (CPS) education supplements 1982-2020
  \begin{itemize}
      \item Limitations: i) excludes incarcerated persons ii) cannot track movement across states
  \end{itemize}
  \item FBI Uniform Crime Reporting (UCR)
  \item Data on state-level possession/distribution penalties are manually collected from government publications
\end{itemize}
\end{frame}

%------------------------------------------------------------

\begin{frame}
\frametitle{1986 sample}
\include{presentation_sum_stats.tex}
\end{frame}

%------------------------------------------------------------

\begin{frame}
\frametitle{Empirical strategy}
\begin{itemize}
    \item Baseline approach: using young white males and young black females as counterfactuals
    \item Can we leverage variation in state-level laws and drug usage/arrest rates improve the robustness of our results?
\end{itemize}
\end{frame}

%------------------------------------------------------------

\begin{frame}
\frametitle{Pre-trends}
\begin{center}
\includegraphics[width=.4\textwidth]{college_enroll_byrace_1986.png}
\includegraphics[width=.4\textwidth]{college_enroll_bysex_1986.png}
\includegraphics[width=.4\textwidth]{college_enroll_byrace_2010.png}
\includegraphics[width=.4\textwidth]{college_enroll_bysex_2010.png}
\end{center} 
\end{frame}

%------------------------------------------------------------

\begin{frame}
\frametitle{DiD results I, Anti-Drug Abuse Act}
\input{britton_table2_DiD.tex}
\end{frame}

%------------------------------------------------------------

\begin{frame}
\frametitle{DiD results II, Fair Sentencing Act}

\input{fair_sentencing_DiD_t1.tex}
\end{frame}

%------------------------------------------------------------

\begin{frame}
\frametitle{Further work}
\begin{itemize}
    \item Overall, the results so far are encouraging but far from robust (sensitive to specifications, weights, dropped observations, counterfactual group, etc)
    \item Further test the robustness of the DiD estimates
    \item Implement the DDIV / DDD approaches (similar to strategy implemented in Duflo, 2001)
    \item Can we use the same empirical approach to study the impact of these laws on other outcomes?
\end{itemize}
\end{frame}

%------------------------------------------------------------

\begin{frame}
\frametitle{Pre-trends (DDIV)}
Are states that did not increase the punitiveness of their drug laws a valid counterfactual?
\begin{figure}%
    \centering
    \subfloat[\centering]{{\includegraphics[width=5cm]{eventstudy_black.png} }}%
    \qquad
    \subfloat[\centering]{{\includegraphics[width=5cm]{eventstudy_white.png} }}%
    \caption{Treatment: states that increased the punitiveness of their laws}%
    \label{fig:example}%
\end{figure}

Model: $Y_{it}=\phi_{i}+\lambda_{t}+\sum_{s\neq1986}1[t=s]\times treatment_{i}\times\beta_{s}+\epsilon_{is}$

\end{frame}

%------------------------------------------------------------

\end{document}

### 2023-01-04 source/paper/main.tex
Set up vscode

@@
 \documentclass{article}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{mathtools}
-\usepackage{graphicx}
-\usepackage{tabularx}
-\usepackage{float}
-\usepackage{subfig}
-\usepackage{lscape} 
-\usepackage{hyperref}
-\usepackage{setspace}
-\usepackage{booktabs}
-\usepackage[authoryear]{natbib}
-\usepackage{lmodern}
-\usepackage[T1]{fontenc}
-\usepackage[bottom]{footmisc}
-\newcommand{\indep}{\perp \!\!\! \perp}
-\usepackage[nolist]{acronym}
-\newcommand\headercell[1]{%
-   \smash[b]{\begin{tabular}[t]{@{}c@{}} #1 \end{tabular}}}
-\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
-\usepackage{xcolor}%
-\definecolor{webbrown}{rgb}{.6,0,0}
-\usepackage{hyperref}%
-\hypersetup{%
-  breaklinks = true,%
-  colorlinks = true,%
-  anchorcolor = webbrown,%
-  citecolor = webbrown,%
-  filecolor = webbrown,%
-  linkcolor = webbrown,%
-  menucolor = webbrown,%
-  urlcolor= webbrown,%
-  citebordercolor= 1 0 0,%
-  menubordercolor=1 0 0,%
-  urlbordercolor=1 0 0,%
-  runbordercolor=1 0 0,}
-\usepackage{cleveref}
-
-\usepackage{setspace}
-\setstretch{1.5} %% set line spacing
-\usepackage{booktabs}
-\newcommand{\tabnotes}[2]{\bottomrule \multicolumn{#1}{@{}p{0.70\linewidth}@{}}{\footnotesize #2 }\end{tabular}\end{table}}
-
-\begin{acronym}
-  \acro{CI}{confidence interval}
-  \acro{RCT}{randomized controlled trial}
-  \acro{IV}{instrumental variable}
-  \acro{LATE}{local average treatment effect}
-  \acro{ATE}{average treatment effect}
-  \acro{OLS}{ordinary least squares}
-  \acro{RD}{regression discontinuity}
-  \acro{MTE}{marginal treatment effect}
-  \acro{ATT}{average treatment effect on the treated}
-\end{acronym}
+\input{preamble.tex}
 
@@
 \begin{abstract}
-\noindent Aspirational abstract goes here
+\noindent Aspirational abstract goes here!
 \end{abstract}
@@
 
-\section*{Data description}
+\section*{Data Description}
 
 \section*{Empirical/Econometric Methods, Hypotheses tested}
+
+\section*{Figures}
+
+\begin{center}
+\includegraphics[width=.4\textwidth]{college_enroll_byrace_1986.png}
+\includegraphics[width=.4\textwidth]{college_enroll_bysex_1986.png}
+\includegraphics[width=.4\textwidth]{college_enroll_byrace_2010.png}
+\includegraphics[width=.4\textwidth]{college_enroll_bysex_2010.png}
+\end{center}
+
+\section*{Tables}
+\import{../../output/tables/}{britton_summ_stats.tex}
+
+\import{../../output/tables/}{britton_table2_DiD.tex}
+
+\import{../../output/tables/}{britton_table3_DiD.tex}
+
+\import{../../output/tables/}{fair_sentencing_DiD_t1.tex}
+
+\import{../../output/tables/}{fair_sentencing_DiD_t2.tex}
 
@@
 \clearpage
+\nocite{*}
 \singlespacing
 \bibliographystyle{jpe}
-\bibliography{cite.bib}
+\bibliography{citations.bib}
 

### 2023-01-06 source/paper/main.tex
#16 Fair sentencing control experiment
#16 Continue new DD and DDD analysis

@@
 
+\begin{center}
+  \includegraphics[width=.4\textwidth]{faminc_byrace_1986.png}
+  \includegraphics[width=.4\textwidth]{faminc_bysex_1986.png}
+  \includegraphics[width=.4\textwidth]{faminc_byrace_2010.png}
+  \includegraphics[width=.4\textwidth]{faminc_bysex_2010.png}
+  \end{center}
+
 \section*{Tables}
@@
 \import{../../output/tables/}{britton_table2_DiD.tex}
+\import{../../output/tables/}{britton_table2_DiD_control_experiment.tex}
 
 \import{../../output/tables/}{britton_table3_DiD.tex}
+\import{../../output/tables/}{britton_table3_DiD_control_experiment.tex}
 
 \import{../../output/tables/}{fair_sentencing_DiD_t1.tex}
+\import{../../output/tables/}{fair_sentencing_DiD_t1_control_experiment.tex}
 
 \import{../../output/tables/}{fair_sentencing_DiD_t2.tex}
+\import{../../output/tables/}{fair_sentencing_DiD_t2_control_experiment.tex}
+
+\import{../../output/tables/}{DiD_1986_high_low.tex}
 

### 2023-01-08 source/cleaning/construct_ucr_icpsr_2010.py
#9 Download 2010 UCR data

@@ -1,0 +1,2 @@
+import pandas as pd
+import time

### 2023-01-09 source/cleaning/construct_ucr_icpsr.py
#9 Cleaning 2010 UCR data

@@ -1,21 +1,24 @@
 import pandas as pd
 import time
 
-# Runtime: ~110 seconds
+# Runtime: ~46 seconds
 def main():
     # Load TSVs into ucr_dfs list as dataframes
     ucr_dfs = []
     ucr_years = [1982, 1983, 1984, 1985, 1986, 1987, 1988, 1989, 1990, 1991, 1992]
+    cols_to_readin = ['STATE', 'OFFENSE', 'YEAR', 'POP', 'JW', 'JB', 'AW', 'AB']
     for ucr_year in ucr_years:
-        ucr_dfs.append(pd.read_csv('../../data/UCR_ICPSR/raw/icpsr_' + str(ucr_year) + '.tsv', sep='\t'))
+        ucr_dfs.append(pd.read_csv('data/UCR_ICPSR/raw/icpsr_' + str(ucr_year) + '.tsv', sep='\t', usecols=cols_to_readin))
     # Clean each df
+    output_test1986 = concatenate_dfs_vertically(ucr_dfs)
+    output_test1986.to_csv('data/UCR_ICPSR/clean/icpsr_ucr_all_yrs_1986_TEST.csv', index=False)
     cleaned_dfs = []
     for ucr_df in ucr_dfs:
         ucr_df = groupby_state(drop_rows(ucr_df))
         cleaned_dfs.append(ucr_df)
     output = concatenate_dfs_vertically(cleaned_dfs)
     # Export final df to csv
-    output.to_csv('../../data/UCR_ICPSR/clean/icpsr_ucr_all_yrs.csv', index=False)
+    output.to_csv('data/UCR_ICPSR/clean/icpsr_ucr_all_yrs.csv', index=False)
 
 def drop_rows(df):
     """ Drop rows not looking at possession of marijuana for a single df """

### 2023-01-09 source/cleaning/construct_ucr_icpsr_2010.py

@@ -1,2 +1,44 @@
 import pandas as pd
 import time
+
+# Runtime: ~XY seconds
+def main():
+    # Load data files into ucr_dfs list as dataframes
+    ucr_dfs, ucr_years, cleaned_dfs = [], [], []
+    start_year, last_year = 2004, 2016  # can be adjusted
+    cols_to_readin = ['STATE', 'OFFENSE', 'YEAR', 'POP', 'JW', 'JB', 'AW', 'AB']
+    for year in range(start_year, last_year + 1):
+        ucr_years.append(year)
+    for ucr_year in ucr_years:
+        ucr_dfs.append(pd.read_stata('data/UCR_ICPSR/raw/icpsr_' + str(ucr_year) + '.dta', columns=cols_to_readin, preserve_dtypes=False))
+    # Clean each df
+    output_test = concatenate_dfs_vertically(ucr_dfs)
+    output_test.to_csv('data/UCR_ICPSR/clean/icpsr_ucr_all_yrs_2010_TEST.csv', index=False)
+    for ucr_df in ucr_dfs:
+        ucr_df.apply(pd.to_numeric, errors='ignore')
+        ucr_df = groupby_state(drop_rows(ucr_df))
+        cleaned_dfs.append(ucr_df)
+    output = concatenate_dfs_vertically(cleaned_dfs)
+    # Export final df to csv
+    output.to_csv('data/UCR_ICPSR/clean/icpsr_ucr_all_yrs_2010.csv', index=False)
+
+def drop_rows(df):
+    """ Drop rows not looking at possession of marijuana for a single df """
+    # Note: different years use different offense codes (mainly 1981)
+    return df.drop(df[(df.OFFENSE != '187') & (df.OFFENSE != '18F')].index)
+
+def groupby_state(df):
+    """ Group a dataframe by groupby_param """
+    var_names = {'YEAR':'year', 'POP':'pop', 'JW':'jw', 'JB':'jb', 'AW':'aw', 'AB':'ab'}
+    agg_input = {'YEAR':'mean', 'POP':'sum','JW':'sum', 'JB':'sum', 'AW':'sum', 'AB':'sum'}
+    grouped_df = df.groupby('STATE', as_index=False).agg(agg_input).rename(columns=var_names)
+    return grouped_df
+
+def concatenate_dfs_vertically(dfs):
+    """ Group all the dfs into one df """
+    return pd.concat(dfs, ignore_index=True)
+
+if __name__ == "__main__":
[…]

### 2023-01-09 source/cleaning/construct_ucr_icpsr.py
#16 Fix UCR data, rerun analysis

@@ -1,7 +1,7 @@
 import pandas as pd
 import time
+from helpers_ucr_icpsr import *
 
-# Runtime: ~46 seconds
 def main():
     # Load TSVs into ucr_dfs list as dataframes
     ucr_dfs = []
@@ -9,32 +9,21 @@ def main():
     cols_to_readin = ['STATE', 'OFFENSE', 'YEAR', 'POP', 'JW', 'JB', 'AW', 'AB']
     for ucr_year in ucr_years:
         ucr_dfs.append(pd.read_csv('data/UCR_ICPSR/raw/icpsr_' + str(ucr_year) + '.tsv', sep='\t', usecols=cols_to_readin))
+    
     # Clean each df
-    output_test1986 = concatenate_dfs_vertically(ucr_dfs)
-    output_test1986.to_csv('data/UCR_ICPSR/clean/icpsr_ucr_all_yrs_1986_TEST.csv', index=False)
-    cleaned_dfs = []
+    #output_test1986 = concatenate_dfs(ucr_dfs)
+    #output_test1986.to_csv('data/UCR_ICPSR/clean/icpsr_ucr_all_yrs_1986_TEST.csv', index=False)
+    cleaned_avg_dfs, cleaned_sum_dfs = [], []
     for ucr_df in ucr_dfs:
-        ucr_df = groupby_state(drop_rows(ucr_df))
-        cleaned_dfs.append(ucr_df)
-    output = concatenate_dfs_vertically(cleaned_dfs)
-    # Export final df to csv
-    output.to_csv('data/UCR_ICPSR/clean/icpsr_ucr_all_yrs.csv', index=False)
-
-def drop_rows(df):
-    """ Drop rows not looking at possession of marijuana for a single df """
-    # Note: different years use different offense codes (mainly 1981)
-    return df.drop(df[(df.OFFENSE != '187') & (df.OFFENSE != '18F')].index)
-
-def groupby_state(df):
-    """ Group a dataframe by groupby_param """
-    var_names = {'YEAR':'year', 'POP':'pop', 'JW':'jw', 'JB':'jb', 'AW':'aw', 'AB':'ab'}
-    agg_input = {'YEAR':'mean', 'POP':'sum','JW':'sum', 'JB':'sum', 'AW':'sum', 'AB':'sum'}
-    grouped_df = df.groupby('STATE', as_index=False).agg(agg_input).rename(columns=var_names)
-    return grouped_df
-
-def concatenate_dfs_vertically(dfs):
[…]

### 2023-01-09 source/cleaning/construct_ucr_icpsr_2010.py

@@ -1,44 +1,34 @@
 import pandas as pd
 import time
+from helpers_ucr_icpsr import *
 
-# Runtime: ~XY seconds
 def main():
     # Load data files into ucr_dfs list as dataframes
-    ucr_dfs, ucr_years, cleaned_dfs = [], [], []
-    start_year, last_year = 2004, 2016  # can be adjusted
+    ucr_dfs, ucr_years = [], []
+    start_year, last_year = 2000, 2016  # can be adjusted
     cols_to_readin = ['STATE', 'OFFENSE', 'YEAR', 'POP', 'JW', 'JB', 'AW', 'AB']
     for year in range(start_year, last_year + 1):
         ucr_years.append(year)
     for ucr_year in ucr_years:
         ucr_dfs.append(pd.read_stata('data/UCR_ICPSR/raw/icpsr_' + str(ucr_year) + '.dta', columns=cols_to_readin, preserve_dtypes=False))
+    
     # Clean each df
-    output_test = concatenate_dfs_vertically(ucr_dfs)
-    output_test.to_csv('data/UCR_ICPSR/clean/icpsr_ucr_all_yrs_2010_TEST.csv', index=False)
+    #output_test = concatenate_dfs(ucr_dfs)
+    #output_test.to_csv('data/UCR_ICPSR/clean/icpsr_ucr_all_yrs_2010_TEST.csv', index=False)
+    cleaned_avg_dfs, cleaned_sum_dfs = [], []
     for ucr_df in ucr_dfs:
         ucr_df.apply(pd.to_numeric, errors='ignore')
-        ucr_df = groupby_state(drop_rows(ucr_df))
-        cleaned_dfs.append(ucr_df)
-    output = concatenate_dfs_vertically(cleaned_dfs)
-    # Export final df to csv
-    output.to_csv('data/UCR_ICPSR/clean/icpsr_ucr_all_yrs_2010.csv', index=False)
+        grouped_sum_df = groupby_state(drop_rows(ucr_df))
+        grouped_avg_df = groupby_state_avg(drop_rows(ucr_df))
+        cleaned_avg_dfs.append(grouped_avg_df)
+        cleaned_sum_dfs.append(grouped_sum_df)
+    output_sum, output_avg = concatenate_dfs(cleaned_sum_dfs), concatenate_dfs(cleaned_avg_dfs)
 
-def drop_rows(df):
-    """ Drop rows not looking at possession of marijuana for a single df """
[…]

### 2023-01-09 source/cleaning/helpers_ucr_icpsr.py

@@ -1,0 +1,26 @@
+import pandas as pd
+
+
+def drop_rows(df):
+    """ Drop rows not looking at possession of marijuana for a single df """
+    # Note: different years use different offense codes (mainly 1981)
+    df = df.drop(df[(df.AB == 99999) | (df.AB == 'None/not reported')].index)
+    return df.drop(df[(df.OFFENSE != '187') & (df.OFFENSE != '18F')].index)
+
+def groupby_state(df):
+    """ Group a dataframe by state, taking sum of arrests """
+    var_names = {'YEAR':'year', 'POP':'pop', 'JW':'jw', 'JB':'jb', 'AW':'aw', 'AB':'ab'}
+    agg_input = {'YEAR':'mean', 'POP':'sum','JW':'sum', 'JB':'sum', 'AW':'sum', 'AB':'sum'}
+    grouped_df = df.groupby('STATE', as_index=False).agg(agg_input).rename(columns=var_names)
+    return grouped_df
+
+def groupby_state_avg(df):
+    """ Group a dataframe by state, taking average of all vars """
+    var_names = {'YEAR':'year', 'POP':'pop', 'JW':'jw', 'JB':'jb', 'AW':'aw', 'AB':'ab'}
+    agg_input = {'YEAR':'mean', 'POP':'mean','JW':'mean', 'JB':'mean', 'AW':'mean', 'AB':'mean'}
+    grouped_df = df.groupby('STATE', as_index=False).agg(agg_input).rename(columns=var_names)
+    return grouped_df
+
+def concatenate_dfs(dfs):
+    """ Group all the dfs into one df """
+    return pd.concat(dfs, ignore_index=True)

### 2023-01-10 source/cleaning/construct_ucr_icpsr_1986.py
#9 Fix UCR 2010 merge

@@ -11,8 +11,6 @@ def main():
         ucr_dfs.append(pd.read_csv('data/UCR_ICPSR/raw/icpsr_' + str(ucr_year) + '.tsv', sep='\t', usecols=cols_to_readin))
     
     # Clean each df
-    #output_test1986 = concatenate_dfs(ucr_dfs)
-    #output_test1986.to_csv('data/UCR_ICPSR/clean/icpsr_ucr_all_yrs_1986_TEST.csv', index=False)
     cleaned_avg_dfs, cleaned_sum_dfs = [], []
     for ucr_df in ucr_dfs:
         grouped_sum_df = groupby_state(drop_rows(ucr_df))
@@ -28,4 +26,4 @@ def main():
 if __name__ == "__main__":
     start_time = time.time()
     main()
-    print("--- %s seconds ---" % (time.time() - start_time))()
+    print("-------" + str(time.time() - start_time) + "seconds ------")

### 2023-01-10 source/cleaning/construct_ucr_icpsr_2010.py

@@ -5,30 +5,37 @@ from helpers_ucr_icpsr import *
 def main():
     # Load data files into ucr_dfs list as dataframes
     ucr_dfs, ucr_years = [], []
-    start_year, last_year = 2000, 2016  # can be adjusted
-    cols_to_readin = ['STATE', 'OFFENSE', 'YEAR', 'POP', 'JW', 'JB', 'AW', 'AB']
+    start_year, last_year = 2000, 2016 
+    cols_to_readin = ['STATE', 'OFFENSE', 'YEAR', 'POP', 'AB']
     for year in range(start_year, last_year + 1):
         ucr_years.append(year)
     for ucr_year in ucr_years:
         ucr_dfs.append(pd.read_stata('data/UCR_ICPSR/raw/icpsr_' + str(ucr_year) + '.dta', columns=cols_to_readin, preserve_dtypes=False))
     
     # Clean each df
-    #output_test = concatenate_dfs(ucr_dfs)
-    #output_test.to_csv('data/UCR_ICPSR/clean/icpsr_ucr_all_yrs_2010_TEST.csv', index=False)
     cleaned_avg_dfs, cleaned_sum_dfs = [], []
     for ucr_df in ucr_dfs:
         ucr_df.apply(pd.to_numeric, errors='ignore')
-        grouped_sum_df = groupby_state(drop_rows(ucr_df))
-        grouped_avg_df = groupby_state_avg(drop_rows(ucr_df))
+        ucr_df['state_num'] = ucr_df.apply(lambda row: label_state(row), axis=1)
+        # Delete 'STATE' column and replace with 'state_num'
+        ucr_df = ucr_df.drop('STATE', axis=1)
+        ucr_df = ucr_df.rename({'state_num': 'STATE'}, axis=1)
+        ucr_df['AB'] = pd.factorize(ucr_df['AB'])[0]  # convert categorical variable to numeric
+
+        grouped_sum_df = groupby_state2010(drop_rows(ucr_df))
+        grouped_avg_df = groupby_state_avg2010(drop_rows(ucr_df))
         cleaned_avg_dfs.append(grouped_avg_df)
         cleaned_sum_dfs.append(grouped_sum_df)
+    
+    # Concatenate into one df
     output_sum, output_avg = concatenate_dfs(cleaned_sum_dfs), concatenate_dfs(cleaned_avg_dfs)
 
     # Export final dfs to csvs
[…]

### 2023-01-10 source/cleaning/helpers_ucr_icpsr.py

@@ -21,6 +21,73 @@ def groupby_state_avg(df):
     grouped_df = df.groupby('STATE', as_index=False).agg(agg_input).rename(columns=var_names)
     return grouped_df
 
+def groupby_state2010(df):
+    """ Group a dataframe by state, taking sum of arrests """
+    var_names = {'YEAR':'year', 'POP':'pop', 'AB':'ab'}
+    agg_input = {'YEAR':'mean', 'POP':'sum','AB':'sum'}
+    grouped_df = df.groupby('STATE', as_index=False).agg(agg_input).rename(columns=var_names)
+    return grouped_df
+
+def groupby_state_avg2010(df):
+    """ Group a dataframe by state, taking average of all vars """
+    var_names = {'YEAR':'year', 'POP':'pop', 'AB':'ab'}
+    agg_input = {'YEAR':'mean', 'POP':'sum','AB':'sum'}
+    grouped_df = df.groupby('STATE', as_index=False).agg(agg_input).rename(columns=var_names)
+    return grouped_df
+
 def concatenate_dfs(dfs):
     """ Group all the dfs into one df """
     return pd.concat(dfs, ignore_index=True)
+
+def label_state(row):
+    if row['STATE'] == 'Alabama': return 1
+    if row['STATE'] == 'Arizona': return 2
+    if row['STATE'] == 'Arkansas': return 3
+    if row['STATE'] == 'California': return 4
+    if row['STATE'] == 'Colorado': return 5
+    if row['STATE'] == 'Connecticut': return 6
+    if row['STATE'] == 'Delaware': return 7
+    if row['STATE'] == 'District of Columbia': return 8
+    if row['STATE'] == 'Florida': return 9
+    if row['STATE'] == 'Georgia': return 10
+    if row['STATE'] == 'Idaho': return 11
+    if row['STATE'] == 'Illinois': return 12
+    if row['STATE'] == 'Indiana': return 13
+    if row['STATE'] == 'Iowa': return 14
+    if row['STATE'] == 'Kansas': return 15
+    if row['STATE'] == 'Kentucky': return 16
+    if row['STATE'] == 'Louisiana': return 17
+    if row['STATE'] == 'Maine': return 18
+    if row['STATE'] == 'Maryland': return 19
+    if row['STATE'] == 'Massachusetts': return 20
+    if row['STATE'] == 'Michigan': return 21
+    if row['STATE'] == 'Minnesota': return 22
[…]

### 2023-01-13 source/paper/main.tex
#16 Test parallel trends for high/low
#16 Fix UCR data, rerun analysis
#16 Check pretrends for 2010 high/low marijuana arrests
#16 Update year range of pre0trends

@@
 
+Note: all figures are limited to ages 18-24 inclusive.
+
 \begin{center}
-\includegraphics[width=.4\textwidth]{college_enroll_byrace_1986.png}
-\includegraphics[width=.4\textwidth]{college_enroll_bysex_1986.png}
-\includegraphics[width=.4\textwidth]{college_enroll_byrace_2010.png}
-\includegraphics[width=.4\textwidth]{college_enroll_bysex_2010.png}
+\includegraphics[width=.4\textwidth]{pretrends/1986/college_enroll_byrace_1986.png}
+\includegraphics[width=.4\textwidth]{pretrends/1986/college_enroll_bysex_1986.png}
+\includegraphics[width=.4\textwidth]{pretrends/2010/college_enroll_byrace_2010.png}
+\includegraphics[width=.4\textwidth]{pretrends/2010/college_enroll_bysex_2010.png}
 \end{center}
@@
 \begin{center}
-  \includegraphics[width=.4\textwidth]{faminc_byrace_1986.png}
-  \includegraphics[width=.4\textwidth]{faminc_bysex_1986.png}
-  \includegraphics[width=.4\textwidth]{faminc_byrace_2010.png}
-  \includegraphics[width=.4\textwidth]{faminc_bysex_2010.png}
+  \includegraphics[width=.4\textwidth]{pretrends/1986/faminc_byrace_1986.png}
+  \includegraphics[width=.4\textwidth]{pretrends/1986/faminc_bysex_1986.png}
+  \includegraphics[width=.4\textwidth]{pretrends/2010/faminc_byrace_2010.png}
+  \includegraphics[width=.4\textwidth]{pretrends/2010/faminc_bysex_2010.png}
 \end{center}
+
+\includegraphics[width=0.7\textwidth]{pretrends/1986/college_enroll_bydrugarrests_1986.png}
+
+\includegraphics[width=0.7\textwidth]{pretrends/2010/college_enroll_bydrugarrests_2010.png}
+
+\includegraphics[width=0.7\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_1986.png}
+
+\includegraphics[width=0.7\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_2010.png}
 
@@
 
+\import{../../output/tables/}{ddd_1986.tex}
+
 %%%%%%%%%%%%%%%%%%%%%%%%BIB%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-01-13 source/analysis/pretrends_roth.R
Add additional UCR data, fix weights and event study

@@ -1,0 +1,3 @@
+devtools::install_github("jonathandroth/pretrends")
+
+library(pretrends)

### 2023-01-13 source/cleaning/ucr/construct_ucr_icpsr_18f_1986.py

@@ -1,0 +1,29 @@
+import pandas as pd
+import time
+from helpers_ucr_icpsr import *
+
+def main():
+    # Load TSVs into ucr_dfs list as dataframes
+    ucr_dfs = []
+    ucr_years = [1982, 1983, 1984, 1985, 1986, 1987, 1988, 1989, 1990, 1991, 1992]
+    cols_to_readin = ['STATE', 'OFFENSE', 'YEAR', 'POP', 'JW', 'JB', 'AW', 'AB']
+    for ucr_year in ucr_years:
+        ucr_dfs.append(pd.read_csv('data/UCR_ICPSR/raw/icpsr_' + str(ucr_year) + '.tsv', sep='\t', usecols=cols_to_readin))
+    
+    # Clean each df
+    cleaned_avg_dfs, cleaned_sum_dfs = [], []
+    for ucr_df in ucr_dfs:
+        grouped_sum_df = groupby_state(drop_rows(ucr_df))
+        grouped_avg_df = groupby_state_avg(drop_rows(ucr_df))
+        cleaned_avg_dfs.append(grouped_avg_df)
+        cleaned_sum_dfs.append(grouped_sum_df)
+    output_sum, output_avg = concatenate_dfs(cleaned_sum_dfs), concatenate_dfs(cleaned_avg_dfs)
+    
+    # Export final dfs to csvs
+    output_sum.to_csv('data/UCR_ICPSR/clean/ucr_sum_18f_1986.csv', index=False)
+    output_avg.to_csv('data/UCR_ICPSR/clean/ucr_avg_18f_1986.csv', index=False)
+
+if __name__ == "__main__":
+    start_time = time.time()
+    main()
+    print("-------" + str(time.time() - start_time) + "seconds ------")

### 2023-01-13 source/cleaning/ucr/construct_ucr_icpsr_1986.py

@@ -1,6 +1,6 @@
 import pandas as pd
 import time
-from helpers_ucr_icpsr import *
+import helpers_ucr_icpsr
 
 def main():
     # Load TSVs into ucr_dfs list as dataframes
@@ -11,17 +11,44 @@ def main():
         ucr_dfs.append(pd.read_csv('data/UCR_ICPSR/raw/icpsr_' + str(ucr_year) + '.tsv', sep='\t', usecols=cols_to_readin))
     
     # Clean each df
-    cleaned_avg_dfs, cleaned_sum_dfs = [], []
+    cleaned_avg_dfs, cleaned_sum_dfs, cleaned_jb_avg_dfs = [], [], []
     for ucr_df in ucr_dfs:
-        grouped_sum_df = groupby_state(drop_rows(ucr_df))
+        #grouped_sum_df = groupby_state(drop_rows(ucr_df))
         grouped_avg_df = groupby_state_avg(drop_rows(ucr_df))
+        grouped_avg_jb_df = groupby_state_avg(drop_rows_jb(ucr_df))
         cleaned_avg_dfs.append(grouped_avg_df)
-        cleaned_sum_dfs.append(grouped_sum_df)
-    output_sum, output_avg = concatenate_dfs(cleaned_sum_dfs), concatenate_dfs(cleaned_avg_dfs)
-    
+        cleaned_jb_avg_dfs.append(grouped_avg_jb_df)
+        #cleaned_sum_dfs.append(grouped_sum_df)
+    #output_sum = helpers_ucr_icpsr.concatenate_dfs(cleaned_sum_dfs), 
+    output_avg = helpers_ucr_icpsr.concatenate_dfs(cleaned_avg_dfs)
+    output_jb_avg = helpers_ucr_icpsr.concatenate_dfs(cleaned_jb_avg_dfs)
+
+    # Drop unnecessary columns to avoid errors down the road
+    output_avg = helpers_ucr_icpsr.drop_columns(output_avg, ['aw', 'jb', 'jw'])
+    output_jb_avg = helpers_ucr_icpsr.drop_columns(output_jb_avg, ['ab', 'aw', 'jw'])
+
     # Export final dfs to csvs
-    output_sum.to_csv('data/UCR_ICPSR/clean/ucr_sum_1986.csv', index=False)
-    output_avg.to_csv('data/UCR_ICPSR/clean/ucr_avg_1986.csv', index=False)
[…]

### 2023-01-13 source/cleaning/ucr/helpers_ucr_icpsr.py

@@ -1,11 +1,14 @@
 import pandas as pd
 
+def drop_columns(df, columns: list):
+    df = df.drop(columns, axis=1)
+    return df
 
 def drop_rows(df):
     """ Drop rows not looking at possession of marijuana for a single df """
     # Note: different years use different offense codes (mainly 1981)
-    df = df.drop(df[(df.AB == 99999) | (df.AB == 'None/not reported')].index)
-    return df.drop(df[(df.OFFENSE != '187') & (df.OFFENSE != '18F')].index)
+    df = df.drop(df[(df.AB == 99998)| (df.AB == 99999) | (df.AB == 'None/not reported')].index)
+    return df[(df.OFFENSE.str.contains("18"))]
 
 def groupby_state(df):
     """ Group a dataframe by state, taking sum of arrests """

### 2023-01-17 source/paper/main.tex
#16 Additional summary stats
Add additional UCR data, fix weights and event study
Data cleaning, paper reorg, R package

@@
 
-\section*{Figures}
+%%%%%%%%%%%%%%%%%%%%%%%%BIB%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\clearpage
+\nocite{*}
+\singlespacing
+\bibliographystyle{jpe}
+\bibliography{citations.bib}
+
+%%%%%%%%%%%%%%%%%%%%%%%%FIGURES%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\clearpage
 
@@
 
+\clearpage
+
 \begin{center}
@@
 
-\includegraphics[width=0.7\textwidth]{pretrends/1986/college_enroll_bydrugarrests_1986.png}
+\clearpage
 
-\includegraphics[width=0.7\textwidth]{pretrends/2010/college_enroll_bydrugarrests_2010.png}
+\begin{figure}[h]
+  \caption{College enrollment overtime 1986}
+  \centering
+  \includegraphics[width=1\textwidth]{pretrends/1986/college_enroll_bydrugarrests_1986.png}
+  \label{fig:TBD}
+\end{figure}
 
-\includegraphics[width=0.7\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_1986.png}
+\clearpage
 
-\includegraphics[width=0.7\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_2010.png}
+\begin{figure}[h]
+  \caption{College enrollment overtime 2010}
+  \centering
+  \includegraphics[width=1\textwidth]{pretrends/2010/college_enroll_bydrugarrests_2010.png}
+  \label{fig:TBD}
+\end{figure}
 
-\section*{Tables}
-\import{../../output/tables/}{britton_summ_stats.tex}
+\clearpage
+
+\begin{figure}[h]
+  \caption{Event study 1986, AB arrest rate 18F}
+  \centering
+  \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_1986.png}
+  \label{fig:TBD}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[h]
+  \caption{Event study 2010, AB arrest rate 18F}
+  \centering
+  \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_2010.png}
+  \label{fig:TBD}
+\end{figure}
+
+\clearpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%TABLES%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\import{../../output/tables/summ_stats/}{cps_summ_stats.tex}
+\import{../../output/tables/summ_stats/}{ucr_summ_stats.tex}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%BIB%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\clearpage
-\nocite{*}
-\singlespacing
-\bibliographystyle{jpe}
-\bibliography{citations.bib}
-
-%%%%%%%%%%%%%%%%%%%%%%%%FIGURES%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\clearpage
-
 \end{document}

### 2023-01-17 source/analysis/pretrends_roth.R

@@ -1,3 +1,28 @@
 devtools::install_github("jonathandroth/pretrends")
 
 library(pretrends)
+
+#Load the coefficients, covariance matrix, and time periods
+beta <- pretrends::HeAndWangResults$beta
+sigma <- pretrends::HeAndWangResults$sigma
+tVec <- pretrends::HeAndWangResults$tVec
+referencePeriod <- -1 #This is the omitted period in the regression
+data.frame(t = tVec, beta = beta)
+
+#Compute slope that gives us 50% power
+slope50 <-
+  slope_for_power(sigma = sigma,
+                  targetPower = 0.5,
+                  tVec = tVec,
+                  referencePeriod = referencePeriod)
+slope50
+
+pretrendsResults <- 
+  pretrends(betahat = beta, 
+            sigma = sigma, 
+            tVec = tVec, 
+            referencePeriod = referencePeriod,
+            deltatrue = slope50 * (tVec - referencePeriod))
+
+pretrendsResults$event_plot
+

### 2023-01-17 source/cleaning/ucr/construct_ucr_icpsr_18f_1986.py

@@ -2,6 +2,7 @@ import pandas as pd
 import time
 from helpers_ucr_icpsr import *
 
+
 def main():
     # Load TSVs into ucr_dfs list as dataframes
     ucr_dfs = []
@@ -22,6 +23,7 @@ def main():
     # Export final dfs to csvs
     output_sum.to_csv('data/UCR_ICPSR/clean/ucr_sum_18f_1986.csv', index=False)
     output_avg.to_csv('data/UCR_ICPSR/clean/ucr_avg_18f_1986.csv', index=False)
+
 
 if __name__ == "__main__":
     start_time = time.time()

### 2023-01-17 source/cleaning/ucr/construct_ucr_icpsr_18f_2010.py

@@ -2,6 +2,7 @@ import pandas as pd
 import time
 from helpers_ucr_icpsr import *
 
+
 def main():
     # Load data files into ucr_dfs list as dataframes
     ucr_dfs, ucr_years = [], []

### 2023-01-17 source/cleaning/ucr/construct_ucr_icpsr_1986.py

@@ -1,6 +1,7 @@
 import pandas as pd
 import time
-import helpers_ucr_icpsr
+from helpers_ucr_icpsr import *
+
 
 def main():
     # Load TSVs into ucr_dfs list as dataframes
@@ -11,44 +12,20 @@ def main():
         ucr_dfs.append(pd.read_csv('data/UCR_ICPSR/raw/icpsr_' + str(ucr_year) + '.tsv', sep='\t', usecols=cols_to_readin))
     
     # Clean each df
-    cleaned_avg_dfs, cleaned_sum_dfs, cleaned_jb_avg_dfs = [], [], []
+    cleaned_avg_dfs, cleaned_jb_avg_dfs = [], []
     for ucr_df in ucr_dfs:
-        #grouped_sum_df = groupby_state(drop_rows(ucr_df))
-        grouped_avg_df = groupby_state_avg(drop_rows(ucr_df))
-        grouped_avg_jb_df = groupby_state_avg(drop_rows_jb(ucr_df))
-        cleaned_avg_dfs.append(grouped_avg_df)
-        cleaned_jb_avg_dfs.append(grouped_avg_jb_df)
-        #cleaned_sum_dfs.append(grouped_sum_df)
-    #output_sum = helpers_ucr_icpsr.concatenate_dfs(cleaned_sum_dfs), 
-    output_avg = helpers_ucr_icpsr.concatenate_dfs(cleaned_avg_dfs)
-    output_jb_avg = helpers_ucr_icpsr.concatenate_dfs(cleaned_jb_avg_dfs)
+        cleaned_avg_dfs.append(groupby_state_avg_alloffenses(drop_rows_alloffenses(ucr_df))) # drop unneeded rows, groupby, append to lst of clean dfs
+        cleaned_jb_avg_dfs.append(groupby_state_avg_alloffenses(drop_rows_jb_alloffenses(ucr_df)))
+    output_avg = concatenate_dfs(cleaned_avg_dfs)
+    output_jb_avg = concatenate_dfs(cleaned_jb_avg_dfs)
 
     # Drop unnecessary columns to avoid errors down the road
-    output_avg = helpers_ucr_icpsr.drop_columns(output_avg, ['aw', 'jb', 'jw'])
-    output_jb_avg = helpers_ucr_icpsr.drop_columns(output_jb_avg, ['ab', 'aw', 'jw'])
-
[…]

### 2023-01-17 source/cleaning/ucr/construct_ucr_icpsr_2010.py

@@ -1,0 +1,45 @@
+import pandas as pd
+import time
+from helpers_ucr_icpsr import * 
+
+
+def main():
+    # Load data files into ucr_dfs list as dataframes
+    ucr_dfs, ucr_years = [], []
+    start_year, last_year = 2000, 2016 
+    cols_to_readin = ['STATE', 'OFFENSE', 'YEAR', 'POP', 'JW', 'JB', 'AW', 'AB']
+    for year in range(start_year, last_year + 1):
+        ucr_years.append(year)
+    for ucr_year in ucr_years:
+        ucr_dfs.append(pd.read_stata('data/UCR_ICPSR/raw/icpsr_' + str(ucr_year) + '.dta', columns=cols_to_readin, preserve_dtypes=False))
+    
+    # Clean each df
+    cleaned_avg_dfs, cleaned_jb_avg_dfs = [], []
+    for ucr_df in ucr_dfs:
+        ucr_df.apply(pd.to_numeric, errors='ignore')
+        ucr_df['state_num'] = ucr_df.apply(lambda row: label_state(row), axis=1)
+        # Delete 'STATE' column and replace with 'state_num'
+        ucr_df = ucr_df.drop('STATE', axis=1)
+        ucr_df = ucr_df.rename({'state_num': 'STATE'}, axis=1)
+        # Convert categorical vars to numeric
+        for group in ['AB', 'JB', 'JW', 'AW']:
+            ucr_df[group] = pd.factorize(ucr_df[group])[0]
+        cleaned_avg_dfs.append(groupby_state_avg_alloffenses(drop_rows_alloffenses(ucr_df)))
+        cleaned_jb_avg_dfs.append(groupby_state_avg_alloffenses(drop_rows_jb_alloffenses(ucr_df)))
+    # Concatenate into one df
+    output_avg = concatenate_dfs(cleaned_avg_dfs) 
+    output_jb_avg = concatenate_dfs(cleaned_jb_avg_dfs)
+
+    # Drop unnecessary colmns to avoid errors down the road
+    output_avg = drop_columns(output_avg, ['aw', 'jb', 'jw'])
+    output_jb_avg = drop_columns(output_jb_avg, ['ab', 'aw', 'jw'])
+
+    # Export final dfs to csvs
+    output_avg.to_csv('data/UCR_ICPSR/clean/ucr_avg_ab_alloffenses_2010.csv', index=False)
[…]

### 2023-01-17 source/cleaning/ucr/helpers_ucr_icpsr.py

@@ -1,8 +1,25 @@
 import pandas as pd
 
+def drop_rows_alloffenses(df):
+    """ Drop rows not looking at possession of marijuana for a single df """
+    # Note: different years use different offense codes (mainly 1981)
+    df = df.drop(df[(df.AB == 99998)| (df.AB == 99999) | (df.AB == 'None/not reported') | (df.AB=='Not applicable')].index)
+    return df[(df.OFFENSE.str.contains("18"))]
+
+def drop_rows_jb_alloffenses(df):
+    """ Drop rows not looking at possession of marijuana for a single df """
+    # Note: different years use different offense codes (mainly 1981)
+    df = df.drop(df[(df.JB == 99998)| (df.JB == 99999) | (df.JB == 'None/not reported') | (df.JB=='Not applicable')].index)
+    return df[(df.OFFENSE.str.contains("18"))]
+
+def groupby_state_avg_alloffenses(df):
+    """ Group a dataframe by state, taking average of all vars """
+    var_names = {'YEAR':'year', 'POP':'pop', 'JW':'jw', 'JB':'jb', 'AW':'aw', 'AB':'ab'}
+    agg_input = {'YEAR':'mean', 'POP':'mean','JW':'mean', 'JB':'mean', 'AW':'mean', 'AB':'mean'}
+    return df.groupby(['STATE', 'OFFENSE'], as_index=False).agg(agg_input).rename(columns=var_names)
+
 def drop_columns(df, columns: list):
-    df = df.drop(columns, axis=1)
-    return df
+    return df.drop(columns, axis=1)
 
 def drop_rows(df):
     """ Drop rows not looking at possession of marijuana for a single df """
@@ -35,8 +52,7 @@ def groupby_state_avg2010(df):
     """ Group a dataframe by state, taking average of all vars """
     var_names = {'YEAR':'year', 'POP':'pop', 'AB':'ab'}
     agg_input = {'YEAR':'mean', 'POP':'sum','AB':'sum'}
-    grouped_df = df.groupby('STATE', as_index=False).agg(agg_input).rename(columns=var_names)
-    return grouped_df
+    return df.groupby('STATE', as_index=False).agg(agg_input).rename(columns=var_names)
 
 def concatenate_dfs(dfs):
     """ Group all the dfs into one df """
@@ -94,3 +110,4 @@ def label_state(row):
     if row['STATE'] == 'Wyoming': return 49
     if row['STATE'] == 'Alaska': return 50
[…]

### 2023-01-18 source/analysis/pretrends_roth.R
DDD, pretrends, new datasets

@@ -3,9 +3,18 @@ devtools::install_github("jonathandroth/pretrends")
 library(pretrends)
 
 #Load the coefficients, covariance matrix, and time periods
-beta <- pretrends::HeAndWangResults$beta
-sigma <- pretrends::HeAndWangResults$sigma
-tVec <- pretrends::HeAndWangResults$tVec
+beta <- c(-159.57987, -142.62841, -72.994561, 116.48307, 216.60878, 339.87964, 0)
+
+sigma <- matrix(c(19451.866, 12441.605, 5325.1719, -1520.1857, -2540.8618, -5247.2621,0,
+                  12441.605, 9783.414, 4275.8322, -2165.672, -4300.2952, -6634.0827,0,
+                  5325.1719, 4275.8322, 2543.7204, -1111.3112, -2485.4035,-3763.9298,0,
+                  -1520.1857,-2165.672,-1111.3112,8866.4137, 12543.886, 13942.985,0,
+                  -2540.8618, -4300.2952,-2485.4035, 12543.886, 21874.095, 24929.135,0,
+                  -5247.2621, -6634.0827, -3763.9298, 13942.985, 24929.135, 30176.604,0,
+                  0,0,0,0,0,0,0)
+                , nrow = 7, ncol = 7)
+isSymmetric(sigma)
+tVec <- c(-4,-3,-2,0,1,2,-1)
 referencePeriod <- -1 #This is the omitted period in the regression
 data.frame(t = tVec, beta = beta)
 
@@ -26,3 +35,7 @@ pretrendsResults <-
 
 pretrendsResults$event_plot
 
+#df_power shows stats about power of pre-test against hypothesized trend
+pretrendsResults$df_power
+
+pretrendsResults$event_plot_pretest

### 2023-01-19 source/cleaning/ucr/construct_ucr_icpsr_18f_1986.py
Data cleaning, DDIV

@@ -21,8 +21,8 @@ def main():
     output_sum, output_avg = concatenate_dfs(cleaned_sum_dfs), concatenate_dfs(cleaned_avg_dfs)
     
     # Export final dfs to csvs
-    output_sum.to_csv('data/UCR_ICPSR/clean/ucr_sum_18f_1986.csv', index=False)
-    output_avg.to_csv('data/UCR_ICPSR/clean/ucr_avg_18f_1986.csv', index=False)
+    output_sum.to_csv('data/UCR_ICPSR/clean/ucr_sum_ab_18f_1986.csv', index=False)
+    output_avg.to_csv('data/UCR_ICPSR/clean/ucr_avg_ab_18f_1986.csv', index=False)
 
 
 if __name__ == "__main__":

### 2023-01-19 source/cleaning/ucr/construct_ucr_icpsr_18f_2010.py

@@ -32,8 +32,8 @@ def main():
     output_sum, output_avg = concatenate_dfs(cleaned_sum_dfs), concatenate_dfs(cleaned_avg_dfs)
 
     # Export final dfs to csvs
-    output_sum.to_csv('data/UCR_ICPSR/clean/ucr_sum_2010.csv', index=False)
-    output_avg.to_csv('data/UCR_ICPSR/clean/ucr_avg_2010.csv', index=False)
+    output_sum.to_csv('data/UCR_ICPSR/clean/ucr_sum_ab_18f_2010.csv', index=False)
+    output_avg.to_csv('data/UCR_ICPSR/clean/ucr_avg_ab_18f_2010.csv', index=False)
 
 
 if __name__ == "__main__":

### 2023-01-20 output/tables/ddiv_show.tex
DDIV

\begin{table}[htbp]\centering
\begin{flushright}
\caption{Replication of Panel A in Table 3 of Duflo (2001)}
\resizebox{0.9\linewidth}{!}{
\begin{tabular}{l*{6}{c}} \hline \\ \hline
& \multicolumn{3}{c}{College enrollment} & \multicolumn{3}{c}{Fam inc}\\ \cline{2-4} \cline{5-7}
& \multicolumn{3}{c}{Level of drug arrests} & \multicolumn{3}{c}{Level of drug arrests}\\ \cline{2-4} \cline{5-7}
& High & Low & Diff. & High & Low & Diff. \\
& (1) & (2) & (3) & (4) & (5) & (6) \\ \hline
\input{ddiv.tex} \\ \hline
\multicolumn{4}{l}{\footnotesize Clustered (state-year) robust standard errors in parentheses}\\
\multicolumn{4}{l}{\footnotesize CPS education supplement weights used. Males only}\\
\end{tabular}
}
\end{flushright}
\end{table}

### 2023-02-07 source/cleaning/state_unemployment/state_unemployment.py
Clean unemployment data

@@ -1,0 +1,77 @@
+import pandas as pd
+# to run in terminal: python3 source/cleaning/state_unemployment/state_unemployment.py
+
+def label_state(row):
+    if row['STATE'] == 'Alabama': return 1
+    if row['STATE'] == 'Arizona': return 2
+    if row['STATE'] == 'Arkansas': return 3
+    if row['STATE'] == 'California': return 4
+    if row['STATE'] == 'Colorado': return 5
+    if row['STATE'] == 'Connecticut': return 6
+    if row['STATE'] == 'Delaware': return 7
+    if row['STATE'] == 'District of Columbia': return 8
+    if row['STATE'] == 'Florida': return 9
+    if row['STATE'] == 'Georgia': return 10
+    if row['STATE'] == 'Idaho': return 11
+    if row['STATE'] == 'Illinois': return 12
+    if row['STATE'] == 'Indiana': return 13
+    if row['STATE'] == 'Iowa': return 14
+    if row['STATE'] == 'Kansas': return 15
+    if row['STATE'] == 'Kentucky': return 16
+    if row['STATE'] == 'Louisiana': return 17
+    if row['STATE'] == 'Maine': return 18
+    if row['STATE'] == 'Maryland': return 19
+    if row['STATE'] == 'Massachusetts': return 20
+    if row['STATE'] == 'Michigan': return 21
+    if row['STATE'] == 'Minnesota': return 22
+    if row['STATE'] == 'Mississippi': return 23
+    if row['STATE'] == 'Missouri': return 24
+    if row['STATE'] == 'Montana': return 25
+    if row['STATE'] == 'Nebraska': return 26
+    if row['STATE'] == 'Nevada': return 27
+    if row['STATE'] == 'New Hampshire': return 28
+    if row['STATE'] == 'New Jersey': return 29
+    if row['STATE'] == 'New Mexico': return 30
+    if row['STATE'] == 'New York': return 31
+    if row['STATE'] == 'North Carolina': return 32
+    if row['STATE'] == 'North Dakota': return 33
+    if row['STATE'] == 'Ohio': return 34
+    if row['STATE'] == 'Oklahoma': return 35
+    if row['STATE'] == 'Oregon': return 36
+    if row['STATE'] == 'Pennsylvania': return 37
+    if row['STATE'] == 'Rhode Island': return 38
+    if row['STATE'] == 'South Carolina': return 39
+    if row['STATE'] == 'South Dakota': return 40
[…]

### 2023-02-09 source/paper/main.tex
DDIV, event study black/white
Data cleaning, DDIV
DDIV
Fix FE, add unemployment control

@@
 
-\title{TITLE:\texorpdfstring{\\}{} subtitle}
+\title{College Enrollment and Earnings:
+\texorpdfstring{\\}{} Examining the Impact of Two Federal Drug Acts}
 \author{Ray Huang\thanks{Contact:
     \href{mailto:ray_huang@brown.edu}{ray\_huang@brown.edu}.
-     I thank Peter Hull at Brown University for serving as my advisor and for providing me with fantastic feedback.}
+     I thank Peter Hull at Brown University for serving as my advisor and for providing me with fantastic feedback. I would also like to thank Alison Lodermeier and Francesco Ferlenga.}
      \\Brown University, Honors Thesis}
@@
 \begin{abstract}
-\noindent Aspirational abstract goes here!
+\noindent (aspirational abstract) I examine the impact of two federal drug acts on college enrollments and earnings among black males by using a variety of counterfactual groups.
+The Anti-Drug Act of 1986 transformed the formerly rehabilitation-focused justice system into a punitive one, imposed sentencing minimums and disparities.
+The Fair Sentencing Act of 2010 undid many of these policies.
+I construct estimates of the impact of these two acts on black males aged 18-24 using three unique counterfactual groups: 1) white males, 2) black females, and 3) black men aged 28-34.
+I also leverage the variation between high and low drug arrest states.
+I estimate that the Anti-Drug Act of 1986 resulted in a change in college enrollment rates between XX and XX and a change in earnings between XX and XX.
+For this subpopulation, this implies estimates of economic returns to education ranging from XX to XX.
+
 \end{abstract}
@@
 
-\section*{Motivation and Background}
+Anti-Drug Act of 1986:
+\begin{itemize}[itemsep=0.05mm, parsep=0pt]
+  \item Created minimum sentencing laws re possession of many drugs. 
+  \item Crack/powdered cocaine was particularly relevant (significantly harder rules on crack, which was cheaper and used by minorities much more, 100-1 ratio)
+  \item The law led to an increase in the average time imprisoned for drug crimes from 22 months to 33 months (Shewan)
+\end{itemize}
 
-\section*{Data Description}
+Fair Sentencing Act of 2010:
+\begin{itemize}[itemsep=0.05mm, parsep=0pt]
+  \item Reduced the disparity between the amount of crack cocaine and powder cocaine needed to trigger certain federal criminal penalties from a 100:1 weight ratio to an 18:1 weight ratio 
+  \item Elimated minimum sentencing for crack cocaine 
+  \item Congressional Budget Office has estimated that implementing the Fair Sentencing Act of 2010 will reduce the prison population by 1,550 person-years over the time period from 2011–2015, creating a monetary savings of \$42 million during that period
+\end{itemize}
+
+Existing literature:
+\begin{itemize}[itemsep=0.05mm, parsep=0pt]
+  \item The Labor Market Consequences of Incarceration- Western, Kling, Weiman (2016)
+  \item Juvenile Incarceration, Human Capital, and Future Crime: Evidence from Randomly Assigned Judges - Aizer, Doyle (2015)
+  \item Evan Rose papers: The Impact of Incarceration on Employment and Earnings, etc
+\end{itemize}
+
+\section*{Data}
+
+\begin{itemize}[itemsep=0.05mm, parsep=0pt]
+  \item CPS October supplement
+  \item UCR from ICPSR (missing data problem, many counties failed to report arrest rates for the relevant crimes)
+  \item ACS
+\end{itemize}
 
 \section*{Empirical/Econometric Methods, Hypotheses tested}
+
+\textbf{Counterfactual groups}
+\begin{itemize}[itemsep=0.05mm, parsep=0pt]
+  \item Black males vs white males
+  \begin{itemize}
+    \item Identifying assumption: absent of the Anti-Drug Abuse Act of 1986, black and white male educational outcomes would have trended similarly.
+  \end{itemize}
+  \item Black males vs black females
+  \item Black males aged 18-24 vs black males aged 28-34 at the time of the act
+  \item High vs low drug use
+\end{itemize}
+
+\textbf{Empirical tools:}
+\begin{itemize}[itemsep=0.05mm, parsep=0pt]
+  \item DiD / DDD / Event study.
+  \item \begin{itemize}
+    \item Using Roth's pretrend \& honest did suggestions
+  \end{itemize}
+  \item DDIV
+\end{itemize}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%FIGURES%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+a
 \clearpage
@@
 
+\begin{figure*}[h]
+  \caption{Pretrends for Event study 1986, AB arrest rate 18F}
+  \includegraphics[width=1\textwidth]{roth_test.png}
+\end{figure*}
+
+Power: 0.499. Bayes.Factor: 0.550.  Likelihood.Ratio: 2.024
+
 \clearpage
@@
 
+\import{../../output/tables/}{ddiv_show.tex}
+
 \end{document}

### 2023-02-09 source/cleaning/state_unemployment/state_unemployment.py

@@ -55,7 +55,7 @@ def label_state(row):
     if row['STATE'] == 'Hawaii': return 51
     else: return "Error, missing state check data."
 
-
+# Read in data as df
 unemployment_df = pd.read_excel('data/state_unemployment/state_year_unemployment_raw.xls')
 
 # Unpivot
@@ -69,9 +69,17 @@ unemployment_df = unemployment_df.reset_index(level=0)
 unemployment_df = unemployment_df.rename({'year': 'year', 'Area': 'STATE', 'unemploy':'unemployment'}, axis=1)
 
 # Relabel states
-unemployment_df['state_num'] = unemployment_df.apply(lambda row: label_state(row), axis=1)
+unemployment_df['state'] = unemployment_df.apply(lambda row: label_state(row), axis=1)
 
 # Remove United States obs
 unemployment_df = unemployment_df.drop(unemployment_df[unemployment_df.STATE == 'United States'].index)
 
+# Drop state names
+unemployment_df = unemployment_df.drop('STATE', axis=1)
+
+# Covert to numeric
+unemployment_df['year'] = unemployment_df['year'].astype(int)
+unemployment_df['state'] = unemployment_df['state'].astype(int)
+
+# Export to csv
 unemployment_df.to_csv('data/state_unemployment/state_year_unemployment_clean.csv', index=False)

### 2023-02-14 source/cleaning/ucr/construct_ucr_icpsr_1986.py
Add years of 1986 CPS data, event study

@@ -6,7 +6,7 @@ from helpers_ucr_icpsr import *
 def main():
     # Load TSVs into ucr_dfs list as dataframes
     ucr_dfs = []
-    ucr_years = [1982, 1983, 1984, 1985, 1986, 1987, 1988, 1989, 1990, 1991, 1992]
+    ucr_years = [1980, 1981, 1982, 1983, 1984, 1985, 1986, 1987, 1988, 1989, 1990, 1991, 1992]
     cols_to_readin = ['STATE', 'OFFENSE', 'YEAR', 'POP', 'JW', 'JB', 'AW', 'AB']
     for ucr_year in ucr_years:
         ucr_dfs.append(pd.read_csv('data/UCR_ICPSR/raw/icpsr_' + str(ucr_year) + '.tsv', sep='\t', usecols=cols_to_readin))
@@ -14,6 +14,8 @@ def main():
     # Clean each df
     cleaned_avg_dfs, cleaned_jb_avg_dfs = [], []
     for ucr_df in ucr_dfs:
+        # Debug: convert col of offense codes to str
+        ucr_df['OFFENSE'] = ucr_df['OFFENSE'].astype(str)
         cleaned_avg_dfs.append(groupby_state_avg_alloffenses(drop_rows_alloffenses(ucr_df))) # drop unneeded rows, groupby, append to lst of clean dfs
         cleaned_jb_avg_dfs.append(groupby_state_avg_alloffenses(drop_rows_jb_alloffenses(ucr_df)))
     output_avg = concatenate_dfs(cleaned_avg_dfs)
@@ -30,4 +32,4 @@ def main():
 if __name__ == "__main__":
     start_time = time.time()
     main()
-    print("-------" + str(time.time() - start_time) + "seconds ------")
+    print("-------" + str(time.time() - start_time) + " seconds ------")

### 2023-02-14 source/cleaning/ucr/helpers_ucr_icpsr.py

@@ -1,14 +1,12 @@
 import pandas as pd
 
 def drop_rows_alloffenses(df):
-    """ Drop rows not looking at possession of marijuana for a single df """
-    # Note: different years use different offense codes (mainly 1981)
+    """ Drop rows with missing data """
     df = df.drop(df[(df.AB == 99998)| (df.AB == 99999) | (df.AB == 'None/not reported') | (df.AB=='Not applicable')].index)
     return df[(df.OFFENSE.str.contains("18"))]
 
 def drop_rows_jb_alloffenses(df):
-    """ Drop rows not looking at possession of marijuana for a single df """
-    # Note: different years use different offense codes (mainly 1981)
+    """ Drop rows with missing data """
     df = df.drop(df[(df.JB == 99998)| (df.JB == 99999) | (df.JB == 'None/not reported') | (df.JB=='Not applicable')].index)
     return df[(df.OFFENSE.str.contains("18"))]
 

### 2023-03-13 source/paper/main.tex
Add years of 1986 CPS data, event study
Fixing models
Normalize arrest rate, fix outcome var
Fix AB event study

@@
   \item CPS October supplement
+  \begin{itemize}
+    \item Dropped observations with missing family income data
+  \end{itemize}
   \item UCR from ICPSR (missing data problem, many counties failed to report arrest rates for the relevant crimes)
+  \begin{itemize}
+    \item Arrest data normalized to state population data. State population data are based on U.S. Census Bureau midyear population estimates.
+  \end{itemize}
   \item ACS
@@
 \end{itemize}
+
+\textbf{Basic event study model}
+\begin{equation} \label{eq:1}
+  y_{it} = \alpha_i + \gamma_t + q'_{it} \phi + \sum_{m=-G}^{M} \beta_m z_{i,t-m} + C_{it} +\epsilon_{it}
+\end{equation}
+
+where $\alpha_i$ and $\gamma_t$ are individual and time fixed effects,
 
@@
 \begin{figure}[h]
-  \caption{Event study 1986, AB arrest rate 18F}
+  \caption{Effect of Anti-Drug Abuse Act on Drug-related Arrest Rate of Black Men}
   \centering
   \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_1986.png}
-  \label{fig:TBD}
+  \label{fig:ab_es_1986}
 \end{figure}
+
+\begin{footnotesize}
+  \noindent Note: This figure reports coefficients from the estimation of equation \ref{eq:1} evaluating the impact of the Anti-Drug Abuse Act of 1986 on arrest rates per 100,000 related to drug violations using CPS and UCR data from 1982-1992.
+Event time $0 \coloneqq 1986$.
+The coefficients represent the change in outcomes for high-drug arrest states relative to non-high-drug arrest states, where high-drug arrest states are defined to be those above the 75th percentile in 1984.
+The sample is defined as black males aged 18-24 in 1986 who are not currently incarcerated.
+Control variables include population and unemployment rates at the state-year level.
+\end{footnotesize}
+
+\clearpage
 
@@
 \begin{figure}[h]
-  \caption{Event study 2010, AB arrest rate 18F}
+  \caption{Effect of Fair Sentencing Act on Drug-related Arrest Rate of Black Men}
   \centering
   \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_2010.png}
-  \label{fig:TBD}
+  \label{fig:ab_es_2010}
 \end{figure}
+
+\begin{footnotesize}
+  \noindent Note: This figure reports coefficients from the estimation of equation \ref{eq:1} evaluating the impact of the Fair Sentencing act of 2010 on arrest rates per 100,000 related to drug violations using CPS and UCR data from 2005-2015.
+Event time $0 \coloneqq 2010$.
+The coefficients represent the change in outcomes for high-drug arrest states relative to non-high-drug arrest states, where high-drug arrest states are defined to be those above the 75th percentile in 2008.
+The sample is defined as black males aged 18-24 in 2010 who are not currently incarcerated.
+Control variables include population and unemployment rates at the state-year level.
+\end{footnotesize}
 

### 2023-03-25 source/paper/figures.tex
General update

% 1986 pretrends

\begin{figure}[h]
    \centering
    \caption{College Enrollment Around 1984}%
    \subfloat[\centering Race]{{\includegraphics[width=7cm]{pretrends/1986/college_enroll_byrace_1986.png} }}%
    \qquad
    \subfloat[\centering Sex]{{\includegraphics[width=7cm]{pretrends/1986/college_enroll_bysex_1986.png} }}%
    \label{fig:raw_college_1986}%
  \end{figure}

  \begin{figure}[h]
    \centering
    \caption{Family Income Around 1984}%
    \subfloat[\centering Race]{{\includegraphics[width=7cm]{pretrends/1986/faminc_byrace_1986.png} }}%
    \qquad
    \subfloat[\centering Sex]{{\includegraphics[width=7cm]{pretrends/1986/faminc_bysex_1986.png} }}%
    \label{fig:raw_faminc_1986}%
  \end{figure}

  \begin{footnotesize}
    \noindent Note: These figures report the outcomes for various subgroups plotted over time using CPS data from 1984-1992. Figure \ref{fig:raw_college_1986} reports the proportion enrolled in college, while figure \ref{fig:raw_faminc_1986} reports the average family income. A vertical line is drawn to denote the passage of the Anti-Drug Abuse Act of 1986. The universe of samples is defined as participants aged 18-24 in 1986 who were not incarcerated at the time of the survey.
  \end{footnotesize}

  \clearpage

  % 2010 pretrends

  \begin{figure}[h]
    \centering
    \caption{College Enrollment Around 2010}%
    \subfloat[\centering label 1]{{\includegraphics[width=7cm]{pretrends/2010/college_enroll_byrace_2010.png} }}%
    \qquad
    \subfloat[\centering label 2]{{\includegraphics[width=7cm]{pretrends/2010/college_enroll_bysex_2010.png} }}%
    \label{fig:raw_college_2010}%
  \end{figure}

  \begin{figure}[h]
    \centering
    \caption{Family Income Around 2010}%
    \subfloat[\centering Race]{{\includegraphics[width=7cm]{pretrends/2010/faminc_byrace_2010.png} }}%
    \qquad
    \subfloat[\centering Sex]{{\includegraphics[width=7cm]{pretrends/2010/faminc_bysex_2010.png} }}%
    \label{fig:raw_faminc_2010}%
  \end{figure}

  \begin{footnotesize}
    \noindent Note: These figures report the outcomes for various subgroups plotted over time using CPS data from 2005-2016. Figure \ref{fig:raw_college_2010} reports the proportion enrolled in college, while figure \ref{fig:raw_faminc_2010} reports the average family income. A vertical line is drawn to denote the passage of the Fair Sentencing Act of 2010. The universe of samples is defined as participants aged 18-24 in 2010 who were not incarcerated at the time of the survey.
  \end{footnotesize}

  \clearpage

  % High vs low arrest states pretrends
  \begin{figure}[h]
    \centering
    \caption{College Enrollment By States with High vs Low Black Adult Drug Arrest Rates}%
    \subfloat[\centering 1986]{{\includegraphics[width=7cm]{pretrends/1986/college_enroll_bydrugarrests_1986.png} }}%
    \qquad
    \subfloat[\centering 2010]{{\includegraphics[width=7cm]{pretrends/2010/college_enroll_bydrugarrests_2010.png} }}%
    \label{fig:raw_college_highlowab_1986}%
  \end{figure}
  \begin{figure}[h]
    \centering
    \caption{College Enrollment By States with High vs Low Black Juvenile Drug Arrest Rates}%
    \subfloat[\centering 1986]{{\includegraphics[width=7cm]{pretrends/1986/college_enroll_bydrugarrests_jb_1986.png} }}%
    \qquad
    \subfloat[\centering 2010]{{\includegraphics[width=7cm]{pretrends/2010/college_enroll_bydrugarrests_jb_2010.png} }}%
    \label{fig:raw_college_highlowjb_1986}%
  \end{figure}
  \begin{footnotesize}
    \noindent Note: These figures report the proportion enrolled in college plotted over time using CPS data from 1984-1992 and 2005-2016 for high black adult/juvenile drug arrest states and low black adult/juvenile drug arrest states, where high black adult/juvenile drug arrest states are defined to be those above the 75th percentile in 1984 and 2008. A vertical line is drawn to denote the passage of the Anti-Drug Abuse Act of 1986s and the Fair Sentencing Act of 2010. The sample is defined as black males aged 18-24 in 1986 and 2010 who were not incarcerated at the time of the survey.
  \end{footnotesize}

  \clearpage

  \begin{figure}[h]
    \caption{Effect of Anti-Drug Abuse Act on Drug-related Arrest Rate of Black Men, Comparing States with High and Low Black Adult Drug-Related Arrest Raten}
    \centering
    \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_1986.png}
    \label{fig:ab_es_1986}
  \end{figure}

  \begin{footnotesize}
    \noindent Note: This figure reports coefficients from the estimation of equation \ref{eq:1} evaluating the impact of the Anti-Drug Abuse Act of 1986 on arrest rates per 100,000 related to drug violations using CPS and UCR data from 1982-1992. Event time $0 \coloneqq 1986$. The coefficients represent the change in outcomes for high-drug arrest states relative to non-high-drug arrest states, where high black adult drug arrest states are defined to be those above the 75th percentile in 1984. The sample is defined as black males aged 18-24 in 1986 who were not incarcerated at the time of the survey. Control variables include population and unemployment rates at the state-year level. 
  \end{footnotesize}

  \clearpage

  \begin{figure*}[h]
    \caption{Pretrends for Event study 1986, AB arrest rate 18F}
    \includegraphics[width=1\textwidth]{roth_test.png}
  \end{figure*}

  Power: 0.499. Bayes.Factor: 0.550.  Likelihood.Ratio: 2.024

  \clearpage

  \begin{figure}[h]
    \caption{Effect of Fair Sentencing Act on Drug-related Arrest Rate of Black Men, Comparing States with High and Low Black Adult Drug-Related Arrest Rate}
    \centering
    \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_2010.png}
    \label{fig:ab_es_2010}
  \end{figure}

  \begin{footnotesize}
    \noindent Note: This figure reports coefficients from the estimation of equation \ref{eq:1} evaluating the impact of the Fair Sentencing act of 2010 on arrest rates per 100,000 related to drug violations using CPS and UCR data from 2005-2015. Event time $0 \coloneqq 2010$. The coefficients represent the change in outcomes for high black adult drug arrest states relative to non-high-drug arrest states, where high-drug arrest states are defined to be those above the 75th percentile in 2008. The sample is defined as black males aged 18-24 in 2010 who were not incarcerated at the time of the survey. Control variables include population and unemployment rates at the state-year level. 
  \end{footnotesize}

\clearpage

  \begin{figure}[h]
    \caption{Effect of Anti-Drug Abuse Act on Drug-related Arrest Rate of Black Men, Comparing States with High and Low Black Juvenile Drug-Related Arrest Rate}
    \centering
    \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_1986_jb.png}
    \label{fig:jb_es_1986}
  \end{figure}

  \begin{footnotesize}
    \noindent Note: This figure reports coefficients from the estimation of equation \ref{eq:1} evaluating the impact of the Anti-Drug Abuse Act of 1986 on arrest rates per 100,000 related to drug violations using CPS and UCR data from 1982-1992. Event time $0 \coloneqq 1986$. The coefficients represent the change in outcomes for high black juvenile drug arrest states relative to non-high-drug arrest states, where high-drug arrest states are defined to be those above the 75th percentile in 1984. The sample is defined as black males aged 18-24 in 1986 who were not incarcerated at the time of the survey. Control variables include population and unemployment rates at the state-year level. 
  \end{footnotesize}

\clearpage

\begin{figure}[h]
    \caption{Effect of Fair Sentencing Act on Drug-related Arrest Rate of Black Men, Comparing States with High and Low Black Juvenile Drug-Related Arrest Rate}
    \centering
    \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_2010_jb.png}
    \label{fig:jb_es_2010}
  \end{figure}

  \begin{footnotesize}
    \noindent Note: This figure reports coefficients from the estimation of equation \ref{eq:1} evaluating the impact of the Fair Sentencing act of 2010 on arrest rates per 100,000 related to drug violations using CPS and UCR data from 2005-2015. Event time $0 \coloneqq 2010$. The coefficients represent the change in outcomes for high black juvenile drug arrest states relative to non-high-drug arrest states, where high-drug arrest states are defined to be those above the 75th percentile in 2008. The sample is defined as black males aged 18-24 in 2010 who were not incarcerated at the time of the survey. Control variables include population and unemployment rates at the state-year level. 
  \end{footnotesize}

  \clearpage

  \begin{figure}[h]
    \centering
    \caption{Distribution of Black Juvenile Drug-Related Arrest Rates By State / Year}%
    \subfloat[\centering 1986]{{\includegraphics[width=7cm]{descriptive/norm_jb_100000_density_1986} }}%
    \qquad
    \subfloat[\centering 2010]{{\includegraphics[width=7cm]{descriptive/norm_jb_100000_density_2010.png} }}%
    \label{fig:density_jb}%
  \end{figure}
  \begin{footnotesize}
    \noindent Note:
    The sample is defined as black males aged 18-24 in 1986 and 2010 who were not incarcerated at the time of the survey. 
  \end{footnotesize}

### 2023-03-25 source/paper/main.tex
General update

--- 2023-02-09 source/paper/main.tex
@@
     \href{mailto:ray_huang@brown.edu}{ray\_huang@brown.edu}.
-     I thank Peter Hull at Brown University for serving as my advisor and for providing me with fantastic feedback. I would also like to thank Alison Lodermeier and Francesco Ferlenga.}
+     I thank Peter Hull at Brown University for serving as my advisor and for providing me with fantastic feedback.
+I would also like to thank Alison Lodermeier and Francesco Ferlenga for their guidance and support.}
      \\Brown University, Honors Thesis}
@@
 \begin{abstract}
-\noindent (aspirational abstract) I examine the impact of two federal drug acts on college enrollments and earnings among black males by using a variety of counterfactual groups.
+\noindent (to be updated abstract) I examine the impact of two federal drug acts on college enrollments and earnings among black males by using a variety of counterfactual groups.
 The Anti-Drug Act of 1986 transformed the formerly rehabilitation-focused justice system into a punitive one, imposed sentencing minimums and disparities.
@@
   \item CPS October supplement
+  \begin{itemize}
+    \item Dropped observations with missing family income data
+    \item Edtype is the variable used for college enrollment, 
+  \end{itemize}
   \item UCR from ICPSR (missing data problem, many counties failed to report arrest rates for the relevant crimes)
+  \begin{itemize}
+    \item Arrest data normalized per 100000. State population data are based on U.S. Census Bureau midyear population estimates.
+  \end{itemize}
   \item ACS
@@
 %%%%%%%%%%%%%%%%%%%%%%%%FIGURES%%%%%%%%%%%%%%%%%%%%%%%%%%%
-a
-\clearpage
-
-Note: all figures are limited to ages 18-24 inclusive.
-
-\begin{center}
-  \includegraphics[width=.4\textwidth]{pretrends/1986/college_enroll_byrace_1986.png}
-  \includegraphics[width=.4\textwidth]{pretrends/1986/college_enroll_bysex_1986.png}
-  \includegraphics[width=.4\textwidth]{pretrends/2010/college_enroll_byrace_2010.png}
-  \includegraphics[width=.4\textwidth]{pretrends/2010/college_enroll_bysex_2010.png}
-\end{center}
 
@@
 
-\begin{center}
-  \includegraphics[width=.4\textwidth]{pretrends/1986/faminc_byrace_1986.png}
-  \includegraphics[width=.4\textwidth]{pretrends/1986/faminc_bysex_1986.png}
-  \includegraphics[width=.4\textwidth]{pretrends/2010/faminc_byrace_2010.png}
-  \includegraphics[width=.4\textwidth]{pretrends/2010/faminc_bysex_2010.png}
-\end{center}
-
-\clearpage
-
-\begin{figure}[h]
-  \caption{College enrollment overtime 1986}
-  \centering
-  \includegraphics[width=1\textwidth]{pretrends/1986/college_enroll_bydrugarrests_1986.png}
-  \label{fig:TBD}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[h]
-  \caption{College enrollment overtime 2010}
-  \centering
-  \includegraphics[width=1\textwidth]{pretrends/2010/college_enroll_bydrugarrests_2010.png}
-  \label{fig:TBD}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[h]
-  \caption{Event study 1986, AB arrest rate 18F}
-  \centering
-  \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_1986.png}
-  \label{fig:TBD}
-\end{figure}
-
-\begin{figure*}[h]
-  \caption{Pretrends for Event study 1986, AB arrest rate 18F}
-  \includegraphics[width=1\textwidth]{roth_test.png}
-\end{figure*}
-
-Power: 0.499. Bayes.Factor: 0.550.  Likelihood.Ratio: 2.024
-
-\clearpage
-
-\begin{figure}[h]
-  \caption{Event study 2010, AB arrest rate 18F}
-  \centering
-  \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_2010.png}
-  \label{fig:TBD}
-\end{figure}
+\input{figures.tex}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%TABLES%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\input{tables.tex}
 
-\import{../../output/tables/summ_stats/}{cps_summ_stats.tex}
-\import{../../output/tables/summ_stats/}{ucr_summ_stats.tex}
+\clearpage
 
-\import{../../output/tables/}{britton_table2_DiD.tex}
-\import{../../output/tables/}{britton_table2_DiD_control_experiment.tex}
-
-\import{../../output/tables/}{britton_table3_DiD.tex}
-\import{../../output/tables/}{britton_table3_DiD_control_experiment.tex}
-
-\import{../../output/tables/}{fair_sentencing_DiD_t1.tex}
-\import{../../output/tables/}{fair_sentencing_DiD_t1_control_experiment.tex}
-
-\import{../../output/tables/}{fair_sentencing_DiD_t2.tex}
-\import{../../output/tables/}{fair_sentencing_DiD_t2_control_experiment.tex}
-
-\import{../../output/tables/}{DiD_1986_high_low.tex}
-
-\import{../../output/tables/}{ddd_1986.tex}
-
-\import{../../output/tables/}{ddiv_show.tex}
+%%%%%%%%%%%%%%%%%%%%%%%%APPENDIX%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2023-03-25 source/paper/tables.tex
General update

\import{../../output/tables/summ_stats/}{cps_summ_stats.tex}

\begin{footnotesize}
  \noindent Note: Sample means (with education weights) are displayed from the CPS October supplement merged with the UCR dataset from 1984-1992 and 2000-2016. The sample in columns 1 and 2 are defined as persons aged 18-24 in 1986, and the sample in columns 3 and 4 are defined as persons aged 18-24 in 2010, who were not incarcerated at the time of the survey. This table is partially replicated from \cite{britton2022}.
\end{footnotesize}

\import{../../output/tables/summ_stats/}{ucr_summ_stats.tex}

% Britton Table 2
\import{../../output/tables/}{britton_table2_DiD.tex}
\begin{footnotesize}
  \noindent Note: Estimates are weighted using CPS October supplement weights. Robust standard errors are clustered at the state level. Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income. The sample is defined as black and white males aged 18-24 in 1986 who were not incarcerated at the time of the survey.
  This table is partially replicated from \cite{britton2022}.
\end{footnotesize}

\import{../../output/tables/}{britton_table2_DiD_control_experiment.tex}
\begin{footnotesize}
  \noindent Note: Estimates are weighted using CPS October supplement weights. Robust standard errors are clustered at the state level. Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income. The sample is defined as black and white males aged 30-50 in 1986 who were not incarcerated at the time of the survey.
  This table is a control experiment for table 2 in \cite{britton2022}.
\end{footnotesize}
\clearpage

\import{../../output/tables/}{britton_table3_DiD.tex}
\begin{footnotesize}
  \noindent Note: Estimates are weighted using CPS October supplement weights. Robust standard errors are clustered at the state level. Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income. The sample is defined as black males and black females aged 18-24 in 1986 who were not incarcerated at the time of the survey.
  This table is partially replicated from \cite{britton2022}.
\end{footnotesize}

\import{../../output/tables/}{britton_table3_DiD_control_experiment.tex}
\begin{footnotesize}
  \noindent Note: Estimates are weighted using CPS October supplement weights. Robust standard errors are clustered at the state level. Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income. The sample is defined as black males and black females aged 30-50 in 1986 who were not incarcerated at the time of the survey.
  This table is a control experiment for table 3 in \cite{britton2022}.
\end{footnotesize}
\clearpage

\import{../../output/tables/}{fair_sentencing_DiD_t1.tex}
\begin{footnotesize}
  \noindent Note: Estimates are weighted using CPS October supplement weights. Robust standard errors are clustered at the state level. Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income. The sample is defined as black and white males aged 18-24 in 2010 who were not incarcerated at the time of the survey.
\end{footnotesize}

\import{../../output/tables/}{fair_sentencing_DiD_t1_control_experiment.tex}
\begin{footnotesize}
  \noindent Note: Estimates are weighted using CPS October supplement weights. Robust standard errors are clustered at the state level. Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income. The sample is defined as black and white males aged 30-50 in 2010 who were not incarcerated at the time of the survey.
\end{footnotesize}
\clearpage

\import{../../output/tables/}{fair_sentencing_DiD_t2.tex}
\begin{footnotesize}
  \noindent Note: Estimates are weighted using CPS October supplement weights. Robust standard errors are clustered at the state level. Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income. The sample is defined as black males and females aged 18-24 in 2010 who were not incarcerated at the time of the survey.
\end{footnotesize}

\import{../../output/tables/}{fair_sentencing_DiD_t2_control_experiment.tex}
\begin{footnotesize}
  \noindent Note: Estimates are weighted using CPS October supplement weights. Robust standard errors are clustered at the state level. Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income. The sample is defined as black males and females aged 30-50 in 2010 who were not incarcerated at the time of the survey.
\end{footnotesize}
\clearpage

\import{../../output/tables/}{DiD_1986_high_low.tex}
\begin{footnotesize}
  \noindent Note: Treated observations are defined as those living in states with a high-drug arrest rate for black adults, where high black adult drug arrest states are defined to be those above the 75th percentile in 1984. Estimates are weighted using CPS October supplement weights. Robust standard errors are clustered at the state level. Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income. The sample is defined as males aged 18-24 in 1986 who were not incarcerated at the time of the survey.
\end{footnotesize}

\import{../../output/tables/}{DiD_1986_high_low_cont.tex}
\begin{footnotesize}
  \noindent Note: Treatment is continuous. Estimates are weighted using CPS October supplement weights. Robust standard errors are clustered at the state level. Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income. The sample is defined as males aged 18-24 in 1986 who were not incarcerated at the time of the survey.
\end{footnotesize}
\clearpage

\import{../../output/tables/}{DiD_1986_high_low_jb.tex}
\begin{footnotesize}
  \noindent Note: Treated observations are defined as those living in states with a high-drug arrest rate for black juveniles, where high black juvenile drug arrest states are defined to be those above the 75th percentile in 1984. Estimates are weighted using CPS October supplement weights. Robust standard errors are clustered at the state level. Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income. The sample is defined as males aged 18-24 in 1986 who were not incarcerated at the time of the survey.
\end{footnotesize}
\import{../../output/tables/}{DiD_1986_high_low_jb_cont.tex}
\clearpage

\import{../../output/tables/}{DiD_1986_high_low_jb_cont_control_experiment_female.tex}
\import{../../output/tables/}{DiD_1986_high_low_jb_cont_control_experiment_old.tex}

\clearpage

\import{../../output/tables/}{DiD_2010_high_low.tex}
\begin{footnotesize}
  \noindent Note: Treated observations are defined as those living in states with a high-drug arrest rate for black adults, where high black adult drug arrest states are defined to be those above the 75th percentile in 2008. Estimates are weighted using CPS October supplement weights. Robust standard errors are clustered at the state level. Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income. The sample is defined as males aged 18-24 in 1986 who were not incarcerated at the time of the survey.
\end{footnotesize}

\import{../../output/tables/}{DiD_2010_high_low_cont.tex}
\begin{footnotesize}
  \noindent Note: Treatment is continuous. Estimates are weighted using CPS October supplement weights. Robust standard errors are clustered at the state level. Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income. The sample is defined as males aged 18-24 in 2010 who were not incarcerated at the time of the survey.
\end{footnotesize}
\clearpage

\import{../../output/tables/}{ddd_1986.tex}

\import{../../output/tables/}{ddiv_show.tex}

### 2023-04-09 source/paper/figures.tex
General update

@@
   \begin{figure}[h]
-    \caption{Effect of Anti-Drug Abuse Act on Drug-related Arrest Rate of Black Men, Comparing States with High and Low Black Adult Drug-Related Arrest Raten}
+    \caption{Effect of Anti-Drug Abuse Act on Drug-related Arrest Rate of Black Men, Comparing States with High and Low Black Adult Drug-Related Arrest Rates}
     \centering
-    \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_1986.png}
+    \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_drug_eventstudy_1986.png}
     \label{fig:ab_es_1986}
@@
     \centering
-    \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_2010.png}
+    \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_drug_eventstudy_2010_ab.png}
     \label{fig:ab_es_2010}
@@
   \begin{footnotesize}
-    \noindent Note: This figure reports coefficients from the estimation of equation \ref{eq:1} evaluating the impact of the Fair Sentencing act of 2010 on arrest rates per 100,000 related to drug violations using CPS and UCR data from 2005-2015.
+    \noindent Note: This figure reports coefficients from the estimation of equation \ref{eq:1} evaluating the impact of the Fair Sentencing Act of 2010 on arrest rates per 100,000 related to drug violations using CPS and UCR data from 2005-2015.
 Event time $0 \coloneqq 2010$.
@@
     \centering
-    \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_1986_jb.png}
+    \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_drug_eventstudy_1986_jb.png}
     \label{fig:jb_es_1986}
@@
     \centering
-    \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_2010_jb.png}
+    \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_drug_eventstudy_2010_jb.png}
     \label{fig:jb_es_2010}

### 2023-04-09 source/paper/main.tex
General update

@@
     \href{mailto:ray_huang@brown.edu}{ray\_huang@brown.edu}.
-     I thank Peter Hull at Brown University for serving as my advisor and for providing me with fantastic feedback.
-I would also like to thank Alison Lodermeier and Francesco Ferlenga for their guidance and support.}
+     I thank Peter Hull at Brown University for serving as my advisor and for providing me with fantastic feedback and guidance.
+I would also like to thank Alison Lodermeier and Francesco Ferlenga for their generous comments and support.
+A replication archive with instructions is available at https://github.com/rayhuang11/EconSeniorThesisRH.}
      \\Brown University, Honors Thesis}
@@
 \begin{abstract}
-\noindent (to be updated abstract) I examine the impact of two federal drug acts on college enrollments and earnings among black males by using a variety of counterfactual groups.
+\noindent I examine the impact of two federal drug acts on college enrollments and earnings among black males by using a variety of counterfactual groups.
 The Anti-Drug Act of 1986 transformed the formerly rehabilitation-focused justice system into a punitive one, imposed sentencing minimums and disparities.
@@
 I also leverage the variation between high and low drug arrest states.
-I estimate that the Anti-Drug Act of 1986 resulted in a change in college enrollment rates between XX and XX and a change in earnings between XX and XX.
-For this subpopulation, this implies estimates of economic returns to education ranging from XX to XX.
+I find that
 
@@
 
-\section*{Introduction}
+\section{Introduction}
 
@@
   \item Elimated minimum sentencing for crack cocaine 
-  \item Congressional Budget Office has estimated that implementing the Fair Sentencing Act of 2010 will reduce the prison population by 1,550 person-years over the time period from 2011–2015, creating a monetary savings of \$42 million during that period
+  \item Congressional Budget Office has estimated that implementing the Fair Sentencing Act of 2010 will reduce the prison population by 1,550 person-years over the period from 2011–2015, creating a monetary savings of \$42 million during that period
 \end{itemize}
@@
 
-\section*{Data}
+\section{Empirical Strategy}
 
-\begin{itemize}[itemsep=0.05mm, parsep=0pt]
-  \item CPS October supplement
-  \begin{itemize}
-    \item Dropped observations with missing family income data
-    \item Edtype is the variable used for college enrollment, 
-  \end{itemize}
-  \item UCR from ICPSR (missing data problem, many counties failed to report arrest rates for the relevant crimes)
-  \begin{itemize}
-    \item Arrest data normalized per 100000. State population data are based on U.S. Census Bureau midyear population estimates.
-  \end{itemize}
-  \item ACS
-\end{itemize}
+I take three discrete approaches to my empirical strategy, establishing three unique counterfactual groups for identifying the impact of the Anti-Drug Abuse Act of 1986 and the Fair Sentencing Act of 2010 on college enrollment rates.
 
-\section*{Empirical/Econometric Methods, Hypotheses tested}
+My first empirical approach looks at changes in college enrollment rates in high drug arrest states relative to the low drug arrest states before and after the passage of both the 1986 and 2010 acts where high drug arrest states are defined as states above the 75th percentile two years before the passage of the federal law.
+I also utilize both the adult and juvenile arrest rates in two parallel analyses.
+I examine both the first-stage impact where the outcome is the change in drug-related arrest rates and the reduced-form impact where the outcome is college-enrollment.
+The first stage is evaluated using an event-study model that allows me to assess the evolution of relative outcomes while controlling for fixed differences across states and national trends over time.
+Using data at the state ($s$) by year ($t$) level, I estimate:
+
+\begin{equation} \label{eq:state_level_es}
+  y_{st} = \alpha_s + \gamma_t + X'_{st} \phi + \sum_{m=-G}^{M} \beta_m z_{s,t-m} + \epsilon_{st}
+\end{equation}
+
+where $\alpha_s$ and $\gamma_t$ are individual and time fixed effects, $X'_{st}$ is a vector of control variables, and $\epsilon_{st}$ represents a shock uncorrelated with the policy.
+The coefficients $\{\beta_m \}^{M}_{m=-G}$ summarize the magnitude of the dynamic effects and are summarized in an event-study plot.
+
+In addition to the event study analyses, I also include traditional difference-in-differences estimates as a summary of the effect across all post-expansion years using the following regression specification at the individual ($i$) by year ($t$) level:
+
+\begin{equation} \label{eq:did}
+  y_{it} = \alpha + \delta D_i + \gamma Post_t + \beta D_i Post_t + X'_{it}\phi + \epsilon_{it}
+\end{equation}
+
+where $D_{i}$ is an indicator for belonging to the treatment group (in this case, states with high drug arrests), $Post_t$ is a time indicator for belonging to the post-period, $D_i Post_t$ is the interaction term where $\beta$ is potentially the causal effect of the federal policy if the identifying assumptions are satisfied, and $X'_{it}$ is a vector of control variables.
+
+My second and third empirical approaches mirror the approach taken in \cite {britton2022}.
+In my second empirical strategy, I look at changes in college enrollment rates in black males aged 18-24 at the time of the federal law passage relative to white males aged 18-24 at the time of the federal law passage.
+
+My third approach is very similar to the second approach, where I look at the change in college enrollment rates in black males aged 18-24 at the time of the federal law passage relative to female blacks aged 18-24 at the time of the federal law passage.
+
+Finally, I also include a triple difference-differences specification, where I compare
+
+In all the regression specifications, I follow the recommendations outlined in \cite{duflo_did} and use robust standard errors clustered at the state level.
 
@@
 
-\textbf{Basic event study model}
-\begin{equation} \label{eq:1}
-  y_{it} = \alpha_i + \gamma_t + q'_{it} \phi + \sum_{m=-G}^{M} \beta_m z_{i,t-m} + C_{it} +\epsilon_{it}
-\end{equation}
-
-where $\alpha_i$ and $\gamma_t$ are individual and time fixed effects,
-
 \textbf{Empirical tools:}
@@
 \end{itemize}
+
+\section{Data and Descriptive Statistics}
+
+\subsection{Data}
+% CPS
+To conduct my analysis, I use data from three sources.
+My primary data source is the Current Population Survey (CPS) October Education Supplement from 1980-2016, which I accessed via the IPUMS-CPS database \citep{ipums_cps}.
+The Current Population Survey Education Supplement (CPS) is an annual cross-sectional survey conducted by the United States Census Bureau and the Bureau of Labor Statistics, collecting data from a nationally representative sample of approximately 60,000 households.
+Focused on educational attainment, enrollment status, and related socio-economic factors, the CPS provides a snapshot of the U.S.
+population's educational landscape, which is instrumental in shaping educational policies and understanding trends, and the CPS is commonly used in the social sciences.
+Following the approach in \cite{britton2022}, I excluded observations missing relevant data such as family income and educational attainment, which reduced the sample by about five percent.
+I defined college enrollment to be persons who had 1 year or more of higher education, and I limited my analysis to persons aged 18-24 in the year the federal law was passed (1986 and 2010).
+One notable limitation of the CPS is that it excludes the currently incarcerated population, which would result in an underestimate of the impact of both the Anti-Drug Abuse Act of 1986 and the Fair Sentencing Act of 2010.
+The CPS also does not account for movement across state lines.
+
+%UCR
+For data on arrests, I used the Uniform Crime Reporting (UCR) Program Data from the \cite{ucr}.
+The UCR Program is a data collection initiative led by the FBI, which amasses crime statistics from local law enforcement agencies throughout the United States, and the UCR data is commonly used for crime-related social science research topics.
+The UCR Program has data at the county-year level and includes information on the number of arrests for each arrest type (e.g.
+drug possession, drug distribution, assault, robbery, etc) and also records data on the age \footnote{The UCR data is broken down into adult and juvenile arrests.} and race of the arrested.
+In my analysis, I use black adult arrests and black juvenile arrests related to all drug crimes \footnote{The UCR includes data on drug offenses at a more granular level, such as type of drug, weight, and sale to a minor.}.
+Since I needed arrest data at the state and year level, I constructed a normalized arrest rate per 100,000 by averaging the counties in a state together and dividing by the state's population in a given year \footnote{The population in each state-year was taken from the CPS.}.
+In any analysis where I used both UCR and CPS data, I merged the two datasets at the state and year level.
+
+It is important to note that the UCR data has several limitations.
+First and foremost, many counties failed to report their arrest rates for certain years.
+Secondly, the UCR's hierarchical reporting system requires that only the most severe crime be recorded in cases of multiple offenses, which may skew the data.
+Finally, variations in reporting practices among different law enforcement agencies, as well as changes in reporting standards over time, can affect the consistency and comparability of the data.
+Notably, in the my sample, in certain years, one state failed to report any arrest data, which resulted in all persons living in said state being dropped from the analysis \footnote{Approximately 10,000 observations per year were dropped, which was less than 10\% of the total sample.}.
+Further, arrest data from Florida is missing from many years, particularly in years relevant to the Fair Sentencing Act of 2010.
+This is likely to bias our estimates downwards, as Florida has high rates of drug use and sales \footnote{Florida is the epicenter of the recent prescription drug epidemic in the United States \citep{lee}, and most Colombian cocaine was initially transported to the United States through the Caribbean and Florida \citep{williams}.}.
+What does the criminology literature have to say on the matter?
+\cite{gove} conclude that the personal characteristics of the offender have minor effects on whether the crime is reported and that the UCR is a valid indicator for serious crimes.
+\cite{lynch} conclude that "missing data are substantial in the UCR program and certainly worthy of attention.
+They are not randomly distributed and cannot, therefore, simply be ignored.
+Much of the work done with the unimputed UCR data has overrepresented the experience of larger urban places and underrepresented smaller and less urban places (LaFree, 1998).
+It is difficult to determine if this overrepresentation has substantial effects on conclusions based on these data.
+The imputation strategies employed by the UCR program are reasonable and appear to reduce the overrepresentation of larger places.
+However, these methodologies can clearly be improved upon."
+
+Finally, I used unemployment data at the state by year level from the \cite{unemployment_data}. For analysis at the state by year level, I simply collapse the dataset.
+
+\subsection{Descripitive Statistics}
+
+Tables 1 and 2 report sample means separately for the pre and post-periods of both the Anti-Drug Abuse Act of 1986 and the Fair Sentencing Act of 2010.
+Table 1 uses the CPS-UCR linked dataset (which drops unmerged observations), while Table 2 uses the CPS dataset only.
+Comparing Table 1 to Table 2 provides a rough test for evaluating whether the state-years with missing UCR data are substantially different from the state-years without missing data.
+The number of observations is slightly smaller in the CPS-UCR merged dataset, except for the 2010-2016 period which is much smaller (likely due to the missing UCR data from Florida).
+The "enrolled in college" row is approximately identical between Table 1 and Table 2, and the proportion of blacks and males is also largely the same.
+
+Looking at Table 1, in all periods, about 15\% of the sample is black.
+
+Overall, my summary statistics table is similar to the one presented in \cite{britton2022}, but there are some minor differences.
+
+\section{Results}
+
+\subsection{First Stage Estimates}
+
+\subsection{Placebo Tests}
+
+\section{Conclusion}
+
+estimates are downards biased -cps and ucr missing key data
+
+\subsection{Future Research}
+synthetic control methods, etc
+other datasets e.g. ACA
+better arrest data, county/metropolitan level
+other outcomes
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%FIGURES%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \clearpage
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%TABLES%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \clearpage
 
-%%%%%%%%%%%%%%%%%%%%%%%%TABLES%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \input{tables.tex}
 
+%%%%%%%%%%%%%%%%%%%%%%%%APPENDIX%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \clearpage
 
-%%%%%%%%%%%%%%%%%%%%%%%%APPENDIX%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{appendices}
+  \section{Additional Results}
+  The contents...
+  \section{section 2}
+\end{appendices}
 

### 2023-04-09 source/paper/tables.tex
General update

@@
-\import{../../output/tables/summ_stats/}{cps_summ_stats.tex}
+\import{../../output/tables/summ_stats/}{cps_ucr_summ_stats.tex}
 
@@
 
-\import{../../output/tables/summ_stats/}{ucr_summ_stats.tex}
+\import{../../output/tables/summ_stats/}{cps_only_summ_stats.tex}
+\clearpage
+
+%\import{../../output/tables/summ_stats/}{ucr_summ_stats.tex}
 
@@
 
-\import{../../output/tables/}{ddd_1986.tex}
+\import{../../output/tables/ddd}{ddd_1986_ab.tex}
+\begin{footnotesize}
+  \noindent Note: CPS data from 1984-1992.
+  The sample is defined as males aged 18-24 in 1986 who were not incarcerated at the time of the survey.
+\end{footnotesize}
 
-\import{../../output/tables/}{ddiv_show.tex}
+\clearpage
+
+\import*{../../output/tables/ddd}{ddd_1986_jb.tex}
+
+\clearpage
+
+\import*{../../output/tables/ddd}{ddd_2010_ab.tex}
+
+\clearpage
+
+\import*{../../output/tables/ddd}{ddd_2010_jb.tex}
+
+\import{../../output/tables}{ddiv_show.tex}

### 2023-04-12 source/paper/figures.tex
Update

@@
+  % High vs low arrest states pretrends
+
+  \begin{figure}[h]
+    \centering
+    \caption{College Enrollment By States with High vs Low Black Adult Drug Arrest Rates}%
+    \subfloat[\centering 1986]{{\includegraphics[width=7cm]{pretrends/1986/college_enroll_bydrugarrests_1986.png} }}%
+    \qquad
+    \subfloat[\centering 2010]{{\includegraphics[width=7cm]{pretrends/2010/college_enroll_bydrugarrests_2010.png} }}%
+    \label{fig:raw_college_highlowab_1986}%
+  \end{figure}
+  \begin{figure}[h]
+    \centering
+    \caption{College Enrollment By States with High vs Low Black Juvenile Drug Arrest Rates}%
+    \subfloat[\centering 1986]{{\includegraphics[width=7cm]{pretrends/1986/college_enroll_bydrugarrests_jb_1986.png} }}%
+    \qquad
+    \subfloat[\centering 2010]{{\includegraphics[width=7cm]{pretrends/2010/college_enroll_bydrugarrests_jb_2010.png} }}%
+    \label{fig:raw_college_highlowjb_1986}%
+  \end{figure}
+
+  \begin{footnotesize}
+    \noindent Note: These figures report the proportion enrolled in college plotted over time using CPS data from 1984-1992 and 2005-2016 for high black adult/juvenile drug arrest states and low black adult/juvenile drug arrest states, where high black adult/juvenile drug arrest states are defined to be those above the 75th percentile in 1984 and 2008.
+A vertical line is drawn to denote the passage of the Anti-Drug Abuse Act of 1986 and the Fair Sentencing Act of 2010.
+The sample is defined as black males aged 18-24 in 1986 and 2010 who were not incarcerated at the time of the survey.
+  \end{footnotesize}
+
+  \clearpage
+
+  % Arrest rate pretrends
+
+  \begin{figure}[h]
+    \centering
+    \caption{Adult Black Arrest Rate Per 100,000}%
+    \subfloat[\centering 1986]{{\includegraphics[width=7cm]{pretrends/1986/ab.png} }}%
+    \qquad
+    \subfloat[\centering 2010]{{\includegraphics[width=7cm]{pretrends/2010/ab.png} }}%
+    \label{fig:raw_ab}%
+  \end{figure}
+  \begin{figure}[h]
+    \centering
+    \caption{Juvenile Black Arrest Rate Per 100,000}%
+    \subfloat[\centering 1986]{{\includegraphics[width=7cm]{pretrends/1986/ab.png} }}%
+    \qquad
+    \subfloat[\centering 2010]{{\includegraphics[width=7cm]{pretrends/2010/jb.png} }}%
+    \label{fig:raw_jb}%
+  \end{figure}
+
+  \begin{footnotesize}
+    \noindent Note: These figures report the drug crime arrest rate per 100,000 for black adults and black juveniles separately over time using CPS-UCR merged data from 1984-1992 and 2005-2016.
+A vertical line is drawn to denote the passage of the Anti-Drug Abuse Act of 1986 and the Fair Sentencing Act of 2010.
+  \end{footnotesize}
+
+  \clearpage
+
 % 1986 pretrends
@@
     \caption{College Enrollment Around 1984}%
-    \subfloat[\centering Race]{{\includegraphics[width=7cm]{pretrends/1986/college_enroll_byrace_1986.png} }}%
+    \subfloat[\centering By race]{{\includegraphics[width=7cm]{pretrends/1986/college_enroll_byrace_1986.png} }}%
     \qquad
-    \subfloat[\centering Sex]{{\includegraphics[width=7cm]{pretrends/1986/college_enroll_bysex_1986.png} }}%
+    \subfloat[\centering By sex]{{\includegraphics[width=7cm]{pretrends/1986/college_enroll_bysex_1986.png} }}%
     \label{fig:raw_college_1986}%
@@
     \caption{Family Income Around 1984}%
-    \subfloat[\centering Race]{{\includegraphics[width=7cm]{pretrends/1986/faminc_byrace_1986.png} }}%
+    \subfloat[\centering By race]{{\includegraphics[width=7cm]{pretrends/1986/faminc_byrace_1986.png} }}%
     \qquad
-    \subfloat[\centering Sex]{{\includegraphics[width=7cm]{pretrends/1986/faminc_bysex_1986.png} }}%
+    \subfloat[\centering By sex]{{\includegraphics[width=7cm]{pretrends/1986/faminc_bysex_1986.png} }}%
     \label{fig:raw_faminc_1986}%
@@
     \caption{College Enrollment Around 2010}%
-    \subfloat[\centering label 1]{{\includegraphics[width=7cm]{pretrends/2010/college_enroll_byrace_2010.png} }}%
+    \subfloat[\centering By race]{{\includegraphics[width=7cm]{pretrends/2010/college_enroll_byrace_2010.png} }}%
     \qquad
-    \subfloat[\centering label 2]{{\includegraphics[width=7cm]{pretrends/2010/college_enroll_bysex_2010.png} }}%
+    \subfloat[\centering By sex]{{\includegraphics[width=7cm]{pretrends/2010/college_enroll_bysex_2010.png} }}%
     \label{fig:raw_college_2010}%
@@
     \caption{Family Income Around 2010}%
-    \subfloat[\centering Race]{{\includegraphics[width=7cm]{pretrends/2010/faminc_byrace_2010.png} }}%
+    \subfloat[\centering By race]{{\includegraphics[width=7cm]{pretrends/2010/faminc_byrace_2010.png} }}%
     \qquad
-    \subfloat[\centering Sex]{{\includegraphics[width=7cm]{pretrends/2010/faminc_bysex_2010.png} }}%
+    \subfloat[\centering By sex]{{\includegraphics[width=7cm]{pretrends/2010/faminc_bysex_2010.png} }}%
     \label{fig:raw_faminc_2010}%
@@
 
-  % High vs low arrest states pretrends
   \begin{figure}[h]
-    \centering
-    \caption{College Enrollment By States with High vs Low Black Adult Drug Arrest Rates}%
-    \subfloat[\centering 1986]{{\includegraphics[width=7cm]{pretrends/1986/college_enroll_bydrugarrests_1986.png} }}%
-    \qquad
-    \subfloat[\centering 2010]{{\includegraphics[width=7cm]{pretrends/2010/college_enroll_bydrugarrests_2010.png} }}%
-    \label{fig:raw_college_highlowab_1986}%
-  \end{figure}
-  \begin{figure}[h]
-    \centering
-    \caption{College Enrollment By States with High vs Low Black Juvenile Drug Arrest Rates}%
-    \subfloat[\centering 1986]{{\includegraphics[width=7cm]{pretrends/1986/college_enroll_bydrugarrests_jb_1986.png} }}%
-    \qquad
-    \subfloat[\centering 2010]{{\includegraphics[width=7cm]{pretrends/2010/college_enroll_bydrugarrests_jb_2010.png} }}%
-    \label{fig:raw_college_highlowjb_1986}%
-  \end{figure}
-  \begin{footnotesize}
-    \noindent Note: These figures report the proportion enrolled in college plotted over time using CPS data from 1984-1992 and 2005-2016 for high black adult/juvenile drug arrest states and low black adult/juvenile drug arrest states, where high black adult/juvenile drug arrest states are defined to be those above the 75th percentile in 1984 and 2008.
-A vertical line is drawn to denote the passage of the Anti-Drug Abuse Act of 1986s and the Fair Sentencing Act of 2010.
-The sample is defined as black males aged 18-24 in 1986 and 2010 who were not incarcerated at the time of the survey.
-  \end{footnotesize}
-
-  \clearpage
-
-  \begin{figure}[h]
-    \caption{Effect of Anti-Drug Abuse Act on Drug-related Arrest Rate of Black Men, Comparing States with High and Low Black Adult Drug-Related Arrest Rates}
+    \caption{Effect of Anti-Drug Abuse Act on Drug-related Arrest Rate of Adult Black Men, Comparing States with High and Low Black Adult Drug-Related Arrest Rates}
     \centering
@@
   \begin{footnotesize}
-    \noindent Note: This figure reports coefficients from the estimation of equation \ref{eq:1} evaluating the impact of the Anti-Drug Abuse Act of 1986 on arrest rates per 100,000 related to drug violations using CPS and UCR data from 1982-1992.
+    \noindent Note: This figure reports coefficients from the estimation of equation \ref{eq:state_level_es} evaluating the impact of the Anti-Drug Abuse Act of 1986 on arrest rates per 100,000 related to drug violations using CPS and UCR data from 1982-1992.
 Event time $0 \coloneqq 1986$.
@@
 Control variables include population and unemployment rates at the state-year level.
+Right tail arrest rate outliers were winsorizing at the 95\% level.
   \end{footnotesize}
@@
 
-  \begin{figure*}[h]
-    \caption{Pretrends for Event study 1986, AB arrest rate 18F}
-    \includegraphics[width=1\textwidth]{roth_test.png}
-  \end{figure*}
+  %\begin{figure*}[h]
+   % \caption{Pretrends for Event study 1986, AB arrest rate 18F}
+   % \includegraphics[width=1\textwidth]{roth_test.png}
+  %\end{figure*}
 
-  Power: 0.499. Bayes.Factor: 0.550.  Likelihood.Ratio: 2.024
+  %Power: 0.499. Bayes.Factor: 0.550.  Likelihood.Ratio: 2.024
 
-  \clearpage
+  %\clearpage
 
   \begin{figure}[h]
-    \caption{Effect of Fair Sentencing Act on Drug-related Arrest Rate of Black Men, Comparing States with High and Low Black Adult Drug-Related Arrest Rate}
+    \caption{Effect of Fair Sentencing Act on Drug-related Arrest Rate of Adult Black Men, Comparing States with High and Low Black Adult Drug-Related Arrest Rate}
     \centering
@@
   \begin{footnotesize}
-    \noindent Note: This figure reports coefficients from the estimation of equation \ref{eq:1} evaluating the impact of the Fair Sentencing Act of 2010 on arrest rates per 100,000 related to drug violations using CPS and UCR data from 2005-2015.
+    \noindent Note: This figure reports coefficients from the estimation of equation 1 evaluating the impact of the Fair Sentencing Act of 2010 on arrest rates per 100,000 related to drug violations using CPS and UCR data from 2005-2015.
 Event time $0 \coloneqq 2010$.
@@
   \begin{footnotesize}
-    \noindent Note: This figure reports coefficients from the estimation of equation \ref{eq:1} evaluating the impact of the Anti-Drug Abuse Act of 1986 on arrest rates per 100,000 related to drug violations using CPS and UCR data from 1982-1992.
+    \noindent Note: This figure reports coefficients from the estimation of equation 1 evaluating the impact of the Anti-Drug Abuse Act of 1986 on arrest rates per 100,000 related to drug violations using CPS and UCR data from 1982-1992.
 Event time $0 \coloneqq 1986$.
@@
 \begin{figure}[h]
-    \caption{Effect of Fair Sentencing Act on Drug-related Arrest Rate of Black Men, Comparing States with High and Low Black Juvenile Drug-Related Arrest Rate}
+    \caption{Effect of Fair Sentencing Act on Drug-related Arrest Rate of Juvenile Black Men, Comparing States with High and Low Black Juvenile Drug-Related Arrest Rate}
     \centering
@@
   \begin{footnotesize}
-    \noindent Note:
-    The sample is defined as black males aged 18-24 in 1986 and 2010 who were not incarcerated at the time of the survey. 
+    \noindent Note: These figures report the kernel density estimates for the normalized drug-related black juvenile arrest rate at the state-by-year level. 
   \end{footnotesize}

### 2023-04-12 source/paper/main.tex
Update

@@
     \href{mailto:ray_huang@brown.edu}{ray\_huang@brown.edu}.
-     I thank Peter Hull at Brown University for serving as my advisor and for providing me with fantastic feedback and guidance.
+     I am grateful to Peter Hull at Brown University for serving as my advisor and for providing me with fantastic feedback and guidance.
 I would also like to thank Alison Lodermeier and Francesco Ferlenga for their generous comments and support.
-A replication archive with instructions is available at https://github.com/rayhuang11/EconSeniorThesisRH.}
+A replication archive is available at https://github.com/rayhuang11/EconSeniorThesisRH.}
      \\Brown University, Honors Thesis}
@@
 \begin{abstract}
-\noindent I examine the impact of two federal drug acts on college enrollments and earnings among black males by using a variety of counterfactual groups.
+\noindent I examine the impact of two federal drug acts on college enrollments and earnings among Black males by using a variety of counterfactual groups.
 The Anti-Drug Act of 1986 transformed the formerly rehabilitation-focused justice system into a punitive one, imposed sentencing minimums and disparities.
 The Fair Sentencing Act of 2010 undid many of these policies.
-I construct estimates of the impact of these two acts on black males aged 18-24 using three unique counterfactual groups: 1) white males, 2) black females, and 3) black men aged 28-34.
-I also leverage the variation between high and low drug arrest states.
+I construct estimates of the impact of these two acts on Black males aged 18-24 using three unique counterfactual groups: 1) White males, 2) Black females, and 3) states with (reverse order) I also leverage the variation between high and low drug arrest states.
 I find that
@@
 
-Anti-Drug Act of 1986:
-\begin{itemize}[itemsep=0.05mm, parsep=0pt]
-  \item Created minimum sentencing laws re possession of many drugs. 
-  \item Crack/powdered cocaine was particularly relevant (significantly harder rules on crack, which was cheaper and used by minorities much more, 100-1 ratio)
-  \item The law led to an increase in the average time imprisoned for drug crimes from 22 months to 33 months (Shewan)
-\end{itemize}
+\begin{quote}
+  There’s 2.2 million people in the American prison system, and half a million of those are locked up for drug offenses.
+A lot of them were in the same boat as me: victims of the mandatory minimum.
+Passed by Congress in 1986, it’s the reason hundreds of thousands of nonviolent people, mostly black and brown people, are rotting in prison...
+I’d been in prison for ten years by the time my petition reached the Supreme Court.
+(HONY)
+\end{quote}
 
-Fair Sentencing Act of 2010:
-\begin{itemize}[itemsep=0.05mm, parsep=0pt]
-  \item Reduced the disparity between the amount of crack cocaine and powder cocaine needed to trigger certain federal criminal penalties from a 100:1 weight ratio to an 18:1 weight ratio 
-  \item Elimated minimum sentencing for crack cocaine 
-  \item Congressional Budget Office has estimated that implementing the Fair Sentencing Act of 2010 will reduce the prison population by 1,550 person-years over the period from 2011–2015, creating a monetary savings of \$42 million during that period
-\end{itemize}
+College enrollment rates provide insights into several aspects of the educational landscape, such as access to higher education, socioeconomic factors, and workforce development.
+Troubling enough, in the decades following 1970, the rate of college enrollment growth for black males began to fall behind all other groups, including white females and black females.
+Simultaneously,
+
+The Anti-Drug Abuse Act of \citeyear{antidrugabuseact1986} was passed in October of 1986 as part of Reagan's War on Drugs in response to the growing concerns over drug abuse, particularly the crack cocaine epidemic.
+The Anti-Drug Abuse Act of 1986 marked a pivotal shift in the nation's approach to drug policy, emphasizing punitive measures and significantly impacting the criminal justice system.
+Several notable changes in drug policy were introduced, including the establishment of mandatory minimum sentences for drug offenses.
+One of the most controversial aspects of the legislation was the implementation of the 100-to-1 sentencing disparity between crack and powder cocaine offenses.
+This disparity mandated that possession of 5 grams of crack cocaine resulted in a minimum 5-year prison sentence, while it took 500 grams of powder cocaine to trigger the same penalty.
+Critics argued that this disparity disproportionately affected minority and low-income communities, as crack cocaine was more prevalent in these populations.
+The \cite{eji} claims that after the act, the number of Black people in federal prison increased from 50 in 100,000 to 250 in 100,000, yet there was no change in the number of White people in federal prison \footnote{The Equal Justice Initiative did not include their source, and I could not find any other source making the same claim.}.
+The act also allocated substantial funds for drug enforcement, treatment, and prevention programs, reflecting the government's commitment to addressing the drug crisis comprehensively.
+The \cite{drug_control_money} estimated that drug control funding increased from \$2.9 billion in 1986 to \$4.8 billion in 1987.
+
+It is important to note that due to the War on Drugs, arrest rates and sentencing times were trending up even before the Anti-Drug Abuse Act of 1986.
+\cite{bjs_1986} reported that from 1980 to 1986, the number of federal drug law violations that resulted in convictions increased by 134\% to a total of 12,285 convictions in 1986 \footnote{Federal convictions of all other types increased by 27\%.}.
+The same report also notes that average prison sentences for drug offenders increased by 33\% less than four years to over five years.
+
+The Fair Sentencing Act of 2010 was a piece of legislation enacted by the United States Congress to address the sentencing disparities between crack and powder cocaine offenses, which had been established by the Anti-Drug Abuse Act of 1986.
+The 2010 act aimed to reduce the disproportionate impact of drug laws on minority and low-income communities by amending the previously imposed 100-to-1 sentencing disparity.
+Under the new legislation, the ratio was reduced to 18-to-1, meaning that it now took 28 grams of crack cocaine to trigger a mandatory minimum sentence of 5 years, instead of the previous 5 grams, while the threshold for powder cocaine remained at 500 grams.
+Furthermore, the Fair Sentencing Act eliminated the mandatory minimum sentence for simple possession of crack cocaine, emphasizing a more equitable approach to drug offenses.
+Though the act did not completely equalize the sentencing for crack and powder cocaine, it represented a significant step toward a fairer criminal justice system and demonstrated the government's commitment to addressing the consequences of previous drug policies.
+A \cite{ussc} report estimated that implementing the Fair Sentencing Act of 2010 resulted in the saving of 29,653 bed years \footnote{The same report also found that the Fair Sentencing Act of 2010 did not "disrupt the ongoing decline in the number of people who reported using crack cocaine in the last year."}.
 
@@
 
-My first empirical approach looks at changes in college enrollment rates in high drug arrest states relative to the low drug arrest states before and after the passage of both the 1986 and 2010 acts where high drug arrest states are defined as states above the 75th percentile two years before the passage of the federal law.
+My first and primary empirical approach looks at changes in college enrollment rates in high drug arrest states relative to the low drug arrest states before and after the passage of both the 1986 and 2010 acts where high drug arrest states are defined as states above the 75th percentile two years before the passage of the federal law \footnote{For the Anti-Drug Abuse Act of 1986, states with high Black adult normalized arrest rates include CT, DC, GA, IL, MD, MA, MO, NJ, NY, and TN.
+States with high Black juvenile normalized arrest rates include AR, CT, DE, DC, ME, MD, MA, MT, NJ, SD, and TN.
+For the Fair Sentencing Act of 2010, states with high Black adult normalized arrest rates include AL, AR, DE, DC, GA, KY, LA, MD, MS, MO, NJ, NC, TN, and VA.
+States with high Black juvenile normalized arrest rates include AL, DE, DC, GA, IL, KY, LA, MD, MS, MO, NJ, NC, PA, and SC.
+Note that states without any UCR Program drug arrest data are omitted from this analysis.}.
 I also utilize both the adult and juvenile arrest rates in two parallel analyses.
-I examine both the first-stage impact where the outcome is the change in drug-related arrest rates and the reduced-form impact where the outcome is college-enrollment.
+This approach has the advantage of allowing me to examine both the first-stage and reduced-form impact of the federal acts enabling me to calculate an instrumented difference-in-differences (DDIV) estimate.
+I examine the first-stage impact where the outcome is the change in drug-related arrest rates and the reduced-form impact where the outcome is college-enrollment.
 The first stage is evaluated using an event-study model that allows me to assess the evolution of relative outcomes while controlling for fixed differences across states and national trends over time.
@@
 where $\alpha_s$ and $\gamma_t$ are individual and time fixed effects, $X'_{st}$ is a vector of control variables, and $\epsilon_{st}$ represents a shock uncorrelated with the policy.
-The coefficients $\{\beta_m \}^{M}_{m=-G}$ summarize the magnitude of the dynamic effects and are summarized in an event-study plot.
+The coefficients $\{\beta_m \}^{M}_{m=-G}$ summarize the magnitude of the dynamic effects and are displayed in an event-study plot.
+If the first-stage arrest rates are trending similarly before the passage of the Anti-Drug Abuse Act of 1986 and the Fair Sentencing Act of 2010, I expect the coefficients associated with pre-periods to be small and statistically insignificant.
 
-In addition to the event study analyses, I also include traditional difference-in-differences estimates as a summary of the effect across all post-expansion years using the following regression specification at the individual ($i$) by year ($t$) level:
+For the reduced form estimates, I follow a similar approach where use an event-study model identical to the model specified in \ref{eq:state_level_es}, except I replace ($s$) with($i$), as data is at the individual by year level.
+In addition to the event study analyses, I also report traditional difference-in-differences estimates as a summary of the effect across all post-expansion years using the following regression specification at the individual ($i$) by year ($t$) level:
 
 \begin{equation} \label{eq:did}
-  y_{it} = \alpha + \delta D_i + \gamma Post_t + \beta D_i Post_t + X'_{it}\phi + \epsilon_{it}
+  y_{it} = \alpha + \zeta_s + \xi_t + \delta D_i + \gamma Post_t + \beta D_i Post_t + X'_{it}\phi + \epsilon_{it}
 \end{equation}
 
-where $D_{i}$ is an indicator for belonging to the treatment group (in this case, states with high drug arrests), $Post_t$ is a time indicator for belonging to the post-period, $D_i Post_t$ is the interaction term where $\beta$ is potentially the causal effect of the federal policy if the identifying assumptions are satisfied, and $X'_{it}$ is a vector of control variables.
+where $\zeta_s$ and $\xi_t$ are fixed effects at the state and year level, $D_{i}$ is an indicator for belonging to the treatment group (in this case, states with high drug arrests), $Post_t$ is a time indicator for belonging to the post-period, $D_i Post_t$ is the interaction term where $\beta$ is potentially the causal effect of the federal policy if the identifying assumptions are satisfied, and $X'_{it}$ is a vector of control variables.
+For the reduced form estimates, I report three specifications of the difference-in-difference estimates: the first omits control variables and fixed effects, the second omits fixed effects, and the third is the full regression as specified in \ref{eq:did}.
 
-My second and third empirical approaches mirror the approach taken in \cite {britton2022}.
-In my second empirical strategy, I look at changes in college enrollment rates in black males aged 18-24 at the time of the federal law passage relative to white males aged 18-24 at the time of the federal law passage.
+My second and third empirical strategies mirror the approach taken in \cite {britton2022}.
+In my second empirical strategy, I compare changes in college enrollment rates in Black males aged 18-24 relative to white males aged 18-24 at the time of the federal law passage.
+My third approach is very similar to the second approach, where I look at the change in college enrollment rates in Black males aged 18-24 at the time of the federal law passage relative to female Blacks aged 18-24 at the time of the federal law passage.
+I report traditional difference-in-difference estimates using the regression specified in \ref{eq:did}, except in the second empirical approach $D_i$ is an indicator for being Black (while the entire sample is limited to Black and White males), and in the third empirical approach $D_i$ is an indicator for being a Black male (while the entire sample is limited to Blacks aged 18-24 at the time of the federal law passage.).
 
-My third approach is very similar to the second approach, where I look at the change in college enrollment rates in black males aged 18-24 at the time of the federal law passage relative to female blacks aged 18-24 at the time of the federal law passage.
+Finally, I also include a triple difference-differences specification, where the first difference is pre and post-time periods, the second difference is race, and the third difference is living in a high or low-Black drug arrest state.
+The identifying assumption for the triple difference is
 
-Finally, I also include a triple difference-differences specification, where I compare
+To test whether the identifying assumptions for the three counterfactual groups were satisfied, aside from including event-study plots, I included plots of the raw outcomes over time.
 
-In all the regression specifications, I follow the recommendations outlined in \cite{duflo_did} and use robust standard errors clustered at the state level.
+In all the regression specifications, I estimate the equation using ordinary least squares (OLS).
+I also follow the recommendations outlined in \cite{duflo_did} and report heteroskedasticity-robust standard errors that are clustered at the state level.
+All analyses use CPS October supplement final person weights and limit the sample to Black males aged 18-24 at the time of the passage of the federal act.
 
@@
 
-\textbf{Empirical tools:}
-\begin{itemize}[itemsep=0.05mm, parsep=0pt]
-  \item DiD / DDD / Event study.
-  \item \begin{itemize}
-    \item Using Roth's pretrend \& honest did suggestions
-  \end{itemize}
-  \item DDIV
-\end{itemize}
-
 \section{Data and Descriptive Statistics}
@@
 To conduct my analysis, I use data from three sources.
-My primary data source is the Current Population Survey (CPS) October Education Supplement from 1980-2016, which I accessed via the IPUMS-CPS database \citep{ipums_cps}.
+My primary data source is the Current Population Survey (CPS) October Education Supplement from 1980-2016, which I accessed via the IPUMS-CPS database \citep{ipums_cps} \footnote{Following \cite{britton2022}, for most of my analysis of the Anti-Drug Abuse Act of 1986, I only use years from 1984 onwards.
+Further discussion of this point is included in the appendix.}.
 The Current Population Survey Education Supplement (CPS) is an annual cross-sectional survey conducted by the United States Census Bureau and the Bureau of Labor Statistics, collecting data from a nationally representative sample of approximately 60,000 households.
@@
 The UCR Program has data at the county-year level and includes information on the number of arrests for each arrest type (e.g.
-drug possession, drug distribution, assault, robbery, etc) and also records data on the age \footnote{The UCR data is broken down into adult and juvenile arrests.} and race of the arrested.
-In my analysis, I use black adult arrests and black juvenile arrests related to all drug crimes \footnote{The UCR includes data on drug offenses at a more granular level, such as type of drug, weight, and sale to a minor.}.
+drug possession, drug distribution, assault, robbery, etc) and also records data on the age \footnote{The UCR data separately tracks arrest rates for adult and juvenile cases.} and race of the arrested.
+In my analysis, I use Black adult arrests and Black juvenile arrests related to all drug crimes \footnote{The UCR includes data on drug offenses at a more granular level, such as type of drug, weight, and sale to a minor.}.
 Since I needed arrest data at the state and year level, I constructed a normalized arrest rate per 100,000 by averaging the counties in a state together and dividing by the state's population in a given year \footnote{The population in each state-year was taken from the CPS.}.
@@
 Finally, variations in reporting practices among different law enforcement agencies, as well as changes in reporting standards over time, can affect the consistency and comparability of the data.
-Notably, in the my sample, in certain years, one state failed to report any arrest data, which resulted in all persons living in said state being dropped from the analysis \footnote{Approximately 10,000 observations per year were dropped, which was less than 10\% of the total sample.}.
+Notably, in my sample, in certain years, one state failed to report any arrest data, which resulted in all persons living in said state being dropped from the analysis \footnote{Approximately 10,000 observations per year were dropped, which was less than 10\% of the total sample.}.
 Further, arrest data from Florida is missing from many years, particularly in years relevant to the Fair Sentencing Act of 2010.
@@
 The imputation strategies employed by the UCR program are reasonable and appear to reduce the overrepresentation of larger places.
-However, these methodologies can clearly be improved upon."
+However, these methodologies can clearly be improved upon." Notably, there were a few observations in certain years that were extreme outliers.
+For example, the 99th percentile was 142 arrests in a certain state year, but the outlier would have over 1000 arrests.
+To deal with these extreme outliers (which are very likely to be erroneous), I implement a 95\% right tail winsorization \footnote{I use winsorization over trimming because it is likely the case that the outliers still belong to the distribution.}.
 
@@
 Table 1 uses the CPS-UCR linked dataset (which drops unmerged observations), while Table 2 uses the CPS dataset only.
-Comparing Table 1 to Table 2 provides a rough test for evaluating whether the state-years with missing UCR data are substantially different from the state-years without missing data.
+Comparing Table 1 to Table 2 provides a rough test for evaluating whether the states with missing UCR data certain years in are substantially different from the state without missing data.
 The number of observations is slightly smaller in the CPS-UCR merged dataset, except for the 2010-2016 period which is much smaller (likely due to the missing UCR data from Florida).
-The "enrolled in college" row is approximately identical between Table 1 and Table 2, and the proportion of blacks and males is also largely the same.
+The "enrolled in college" row is approximately identical between Table 1 and Table 2, and the proportion of Blacks and males is also largely the same.
 
-Looking at Table 1, in all periods, about 15\% of the sample is black.
+Looking at Table 1, in all periods, about 15\% of the sample is Black.
 
@@
 
-\subsection{First Stage Estimates}
+\subsection{Anti-Drug Abuse Act of 1986}
 
-\subsection{Placebo Tests}
+\subsubsection{First Stage Estimates}
+
+\subsubsection{Placebo Tests}
+
+\subsection{Fair Sentencing Act of 2010}
+
+Notably, any effect is likely not due to the mandatory sentencing minimum, but rather, is due to the overall lightening of sentences / prosecutions. \cite{ussc} found that
+
+\subsubsection{First Stage Estimates}
+
+\subsubsection{Reduced form estimates}
+
+\subsubsection{Placebo Tests}
 
 \section{Conclusion}
+
+\subsection{Future Research}
 
@@
   The contents...
-  \section{section 2}
+  \section{First stage arrest rate estimates}
+  In \cite{britton2022}, when examining the impact of the Anti-Drug Abuse Act of 1986, she commences her analysis in 1984 due to "fluctuations in Black college enrollment during the early 1980s that were unrelated to the emergence of drug markets \cite{nces}".
+  % Start appendix figures
+  \clearpage
+
+  \begin{figure}[h]
+    \caption{Effect of Anti-Drug Abuse Act on Drug-related Arrest Rate of Adult Black Men, Comparing States with High and Low Black Adult Drug-Related Arrest Rates}
+    \centering
+    \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_drug_eventstudy_1986_extended_years.png}
+    \label{fig:b1}
+  \end{figure}
+
+  \begin{footnotesize}
+    \noindent Note: footnote
+  \end{footnotesize}
+
 \end{appendices}

### 2023-04-18 output/tables/ddiv/ddiv_show2.tex
Update

\begin{table}[htbp]
\centering
\caption{Mean of Drug-related Arrest Rate and College Enrollment Rate By Time and High/low Drug Arrest State}
\resizebox{0.9\linewidth}{!}{
\begin{tabular}{l*{6}{c}} 
\hline
\hline
& \multicolumn{3}{c}{Drug-Related Arrest Rate} & \multicolumn{3}{c}{College Enrollment} \\ 
\cline{2-4} \cline{5-7}
& \multicolumn{3}{c}{Level of drug arrests} & \multicolumn{3}{c}{Level of drug arrests} \\ 
\cline{2-4} \cline{5-7}
& High & Low & Diff. & High & Low & Diff. \\
& (1) & (2) & (3) & (4) & (5) & (6) \\ 
\hline
\input{ddiv_high_low.tex} \\ 
\hline

\end{tabular}
}
\end{table}

### 2023-04-18 source/paper/figures.tex
Update

@@
   \begin{figure}[h]
-    \caption{Effect of Anti-Drug Abuse Act on Drug-related Arrest Rate of Adult Black Men, Comparing States with High and Low Black Adult Drug-Related Arrest Rates}
+    \caption{Black Adult Drug-related Arrest Rate in 1984}
     \centering
-    \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_drug_eventstudy_1986.png}
+    \includegraphics[width=1\textwidth]{heatmap/ab1986.png}
+    \label{fig:heatmap}
+  \end{figure}
+
+  \begin{footnotesize}
+    \noindent Note: This figure presents a heatmap of the United States at the state level using UCR Program data.
+The data is from 1984, and I use all drug-related arrests for Black adult men.
+Although New York's normalized arrest rate is at 48, I capped the maximum at 30 for clarity of states with low normalized drug arrest rates, since the distribution is heavily right-skewed.
+High drug arrest states are defined as states above the 75th percentile, and the 75th percentile is at 17.4 Black adult arrests per 100,000.
+  \end{footnotesize}
+
+  \clearpage
+  % Event study
+  \begin{figure}[h]
+    \caption{Effect of Anti-Drug Abuse Act on Drug-related Arrest Rate of Adult Black Men, Comparing States with High and Low Black Adult Drug-Related Arrest Rates (with Fixed Effects)}
+    \centering
+    \includegraphics[width=0.8\textwidth]{eventstudy/high_drug_use/high_drug_eventstudy_1986.png}
     \label{fig:ab_es_1986}
+  \end{figure}
+
+  \begin{figure}[H]
+    \caption{Effect of Anti-Drug Abuse Act on Drug-related Arrest Rate of Adult Black Men, Comparing States with High and Low Black Adult Drug-Related Arrest Rates (without Fixed Effects)}
+    \centering
+    \includegraphics[width=0.8\textwidth]{eventstudy/high_drug_use/high_drug_eventstudy_nofe_1986.png}
+    \label{fig:ab_es_1986_nofe}
   \end{figure}
@@
   \clearpage
-
-  %\begin{figure*}[h]
-   % \caption{Pretrends for Event study 1986, AB arrest rate 18F}
-   % \includegraphics[width=1\textwidth]{roth_test.png}
-  %\end{figure*}
-
-  %Power: 0.499. Bayes.Factor: 0.550.  Likelihood.Ratio: 2.024
-
-  %\clearpage
 
@@
     \centering
-    \caption{Distribution of Black Juvenile Drug-Related Arrest Rates By State / Year}%
-    \subfloat[\centering 1986]{{\includegraphics[width=7cm]{descriptive/norm_jb_100000_density_1986} }}%
+    \caption{Distribution of Black Adult Drug-Related Arrest Rates}%
+    \subfloat[\centering 1984]{{\includegraphics[width=7cm]{descriptive/norm_jb_100000_density_1986} }}%
     \qquad
-    \subfloat[\centering 2010]{{\includegraphics[width=7cm]{descriptive/norm_jb_100000_density_2010.png} }}%
+    \subfloat[\centering 2008]{{\includegraphics[width=7cm]{descriptive/norm_jb_100000_density_2010.png} }}%
     \label{fig:density_jb}%
@@
   \begin{footnotesize}
-    \noindent Note: These figures report the kernel density estimates for the normalized drug-related black juvenile arrest rate at the state-by-year level. 
+    \noindent Note: These figures report the kernel density estimates for the normalized drug-related Black adult arrest rate in 1984 and 2008.
+The vertical line denotes the 75th percentile.
+Right tail outliers were winsorized at the 95\% level for both figures.
   \end{footnotesize}
+
+\clearpage
+
+\begin{figure}[h]
+  \centering
+  \caption{Effect of ADAA and FSA on the College Enrollment Rate of Adult Black Men, Comparing States with High and Low Black Adult Drug-Related Arrest Rates}%
+  \subfloat[\centering 1986]{{\includegraphics[width=7cm]{eventstudy/high_drug_use/reducedform_ab1986.png} }}%
+  \qquad
+  \subfloat[\centering 2010]{{\includegraphics[width=7cm]{eventstudy/high_drug_use/reducedform_ab2010.png} }}%
+  \label{fig:reducedform_ab}%
+\end{figure}
+\begin{figure}[h]
+  \centering
+  \caption{Effect of ADAA and FSA on the College Enrollment Rate of Adult Black Men, Comparing States with High and Low Black Juvenile Drug-Related Arrest Rates}%
+  \subfloat[\centering 1986]{{\includegraphics[width=7cm]{eventstudy/high_drug_use/reducedform_jb1986.png} }}%
+  \qquad
+  \subfloat[\centering 2010]{{\includegraphics[width=7cm]{eventstudy/high_drug_use/reducedform_ab1986.png} }}%
+  \label{fig:reducedform_jb}%
+\end{figure}

### 2023-04-18 source/paper/main.tex
Update

@@
 
-\title{College Enrollment and Earnings:
-\texorpdfstring{\\}{} Examining the Impact of Two Federal Drug Acts}
+\title{Arrest Rates and College Enrollment:
+\texorpdfstring{\\}{} Examining the Impact of Two Federal Drug Control Acts}
 \author{Ray Huang\thanks{Contact:
@@
 The Anti-Drug Act of 1986 transformed the formerly rehabilitation-focused justice system into a punitive one, imposed sentencing minimums and disparities.
-The Fair Sentencing Act of 2010 undid many of these policies.
-I construct estimates of the impact of these two acts on Black males aged 18-24 using three unique counterfactual groups: 1) White males, 2) Black females, and 3) states with (reverse order) I also leverage the variation between high and low drug arrest states.
+The Fair Sentencing Act of 2010 was intended to reverse some of these policies.
+I construct estimates of the impact of these two acts on the college enrollment of Black males aged 18-24 using three distinct counterfactual groups: 1) comparing states with high drug arrests to states with low drug arrests, 2) Black males to White males, and 3) Black males to Black females.
+I also evaluate the first stage impact of the two Acts on drug-related arrests.
 I find that
@@
 
+% Motivation
+
 \begin{quote}
@@
 I’d been in prison for ten years by the time my petition reached the Supreme Court.
-(HONY)
+(HONY Interview)
 \end{quote}
@@
 College enrollment rates provide insights into several aspects of the educational landscape, such as access to higher education, socioeconomic factors, and workforce development.
-Troubling enough, in the decades following 1970, the rate of college enrollment growth for black males began to fall behind all other groups, including white females and black females.
-Simultaneously,
+In the decades following 1970, the rate of college enrollment growth for black males began to fall behind all other groups, including white females and black females.
+Simultaneously, incarceration rates for black males began to climb during this period, as demonstrated in figure \ref{fig:raw_ab}.
+Many blame the Anti-Drug Abuse Act of 1986 for the increase in minority incarcerations.
+In 2010, the Fair Sentencing Act was passed, which aimed to undo many of the racial disparities potentially caused by the Anti-Drug Abuse Act.
+In this paper, I look to investigate the link between drug enforcement policies and educational outcomes, as I examine the impact of the Anti-Drug Abuse Act of 1986 and Fair Sentencing Act of 2010 on both drug-related arrest rates and college enrollment among Black males.
+
+% Challenges???
+
+The endogeneity problem at hand
+
+% This paper
+
+This paper has two main objectives.
+First, I look to estimate the impact of the Anti-Drug Abuse Act of 1986 and the Fair Sentencing Act of 2010 on drug-related arrests.
+The second objective is to evaluate the impact of the two acts on college enrollment rates for Black males.
+Additionally, I examine the relationship between drug-related arrest rates and college enrollment.
+
+% Methods
+
+I use three separate research designs.
+The first and primary research design leverages variations in the intensity of drug arrests across different states.
+High-intensity states are defined as states with Black adult drug-related arrest rates above the 75th percentile two years before the passage of the federal drug act (e.g.
+for the Anti-Drug Abuse Act, 1984 was used.) I compare high-intensity states to low-intensity states, and I calculate both the first stage and reduced form estimates where the first stage is the impact of the act on Black adult drug-related arrest rates and the reduced form is the impact of the act on college enrollment.
+For additional supplemental analysis, I adapt the second and third research designs in \cite{britton2022} to estimate the impact of the federal drug acts on college enrollment at the individual level.
+
+% Data
+
+I use repeated cross-sectional data from the Current Population Survey October education supplement for data at the individual level, and I limit my analysis to persons aged 18-24 at the time of the passage of the act.
+For data on arrests, I use data from the Uniform Crime Reporting Program, which contains information on the number of arrests by race, crime type, and juvenile crimes.
+To construct college enrollment rates from the CPS, I count any individual who is currently in their first year or has more than one year of college education \footnote{I count individuals with a master's or Ph.D.
+as having been enrolled in college.
+I also count persons enrolled in two-year colleges.}.
+
+This data has several limitations.
+First, the CPS excludes currently incarcerated populations.
+Second, the UCR has well-documented quality issues, such as many counties failing to report in certain years.
+In certain years, entire states failed to report any arrest data.
+Overall, if the effect size is small, the data might be insufficiently powered.
+
+% Findings
+
+I find that the Anti-Drug Abuse Act of 1986 had a modest impact on Black adult male arrest rates and a small negative impact on college enrollment.
+In addition, I find some evidence that an increase in Black adult drug-related arrest rates has a small negative impact on college enrollment rates.
+The Fair Sentencing Act of 2010 is harder to study due to substantial pretrends, and I find some evidence of a potentially positive impact on college enrollment for Black males.
+For my estimates to be considered causal, important pretrend and exclusion restrictions must be satisfied.
+
+% Literature
+This paper heavily builds upon recent work by \cite{britton2022}.
+
+This paper generally contributes to the literature on the effects of incarceration on education and labor outcomes.
+My main contribution to the literature is a relatively imprecise and subpopulation-specific estimate of the causal effect of an increase in Black adult drug-related arrest rates on college enrollment.
+
+Some prior literature includes \cite{aizer} which evaluates the relationship between juvenile incarceration and later life outcomes using a judge-IV research design.
+They find that juvenile incarceration "results in large decreases in the likelihood of high school completion and large increases in the likelihood of adult incarceration." \cite{western} evaluates the impact of incarceration on labor market outcomes.
+\cite{mitchell2016effect} finds that changes in drug arrest rates did not reduce the rate of drug offenses but had substantial negative impacts on employment outcomes for Black males.
+\cite{hatzenbuehler2015collateral} finds that high incarceration rates have psychiatric impacts on non-incarcerated populations, implying that if the federal drug acts have a large impact on arrest rates, there may be spillover effects.
+
+\section{Background}
 
@@
 The \cite{drug_control_money} estimated that drug control funding increased from \$2.9 billion in 1986 to \$4.8 billion in 1987.
+The Act has faced additional criticism as in recent years researchers such as \cite{bewley2005incarceration} have found that "there is little correlation between incarceration rates and drug use prevalence; and the impact of enforcement action on price is much less powerful than other market factors."
 
@@
 \cite{bjs_1986} reported that from 1980 to 1986, the number of federal drug law violations that resulted in convictions increased by 134\% to a total of 12,285 convictions in 1986 \footnote{Federal convictions of all other types increased by 27\%.}.
-The same report also notes that average prison sentences for drug offenders increased by 33\% less than four years to over five years.
+The BJS report also notes that average prison sentences for drug offenders increased by 33\% less than four years to over five years.
 
@@
 Though the act did not completely equalize the sentencing for crack and powder cocaine, it represented a significant step toward a fairer criminal justice system and demonstrated the government's commitment to addressing the consequences of previous drug policies.
-A \cite{ussc} report estimated that implementing the Fair Sentencing Act of 2010 resulted in the saving of 29,653 bed years \footnote{The same report also found that the Fair Sentencing Act of 2010 did not "disrupt the ongoing decline in the number of people who reported using crack cocaine in the last year."}.
-
-Existing literature:
-\begin{itemize}[itemsep=0.05mm, parsep=0pt]
-  \item The Labor Market Consequences of Incarceration- Western, Kling, Weiman (2016)
-  \item Juvenile Incarceration, Human Capital, and Future Crime: Evidence from Randomly Assigned Judges - Aizer, Doyle (2015)
-  \item Evan Rose papers: The Impact of Incarceration on Employment and Earnings, etc
-\end{itemize}
+A \cite{ussc} report estimated that implementing the Fair Sentencing Act of 2010 resulted in the saving of 29,653 bed years \footnote{The same \cite{ussc} report also found that the Fair Sentencing Act of 2010 did not "disrupt the ongoing decline in the number of people who reported using crack cocaine in the last year."}.
 
@@
 States with high Black juvenile normalized arrest rates include AL, DE, DC, GA, IL, KY, LA, MD, MS, MO, NJ, NC, PA, and SC.
-Note that states without any UCR Program drug arrest data are omitted from this analysis.}.
-I also utilize both the adult and juvenile arrest rates in two parallel analyses.
-This approach has the advantage of allowing me to examine both the first-stage and reduced-form impact of the federal acts enabling me to calculate an instrumented difference-in-differences (DDIV) estimate.
+Note that states without any UCR Program drug arrest data are omitted from this analysis.
+See figure \ref{fig:heatmap} for a heatmap of high-intensity states in 1984.}.
+I primarily rely on data on adult arrests instead of juvenile arrests due to effect sizes and issues with pretrends \footnote{As discussed in the introduction, \cite{aizer} finds that juvenile incarceration has a larger impact on education than adult incarceration.
+However, since states with high adult arrests tend to have high juvenile arrest rates, my estimates are robust to which arrest rate is used.}.
 I examine the first-stage impact where the outcome is the change in drug-related arrest rates and the reduced-form impact where the outcome is college-enrollment.
@@
 where $\alpha_s$ and $\gamma_t$ are individual and time fixed effects, $X'_{st}$ is a vector of control variables, and $\epsilon_{st}$ represents a shock uncorrelated with the policy.
-The coefficients $\{\beta_m \}^{M}_{m=-G}$ summarize the magnitude of the dynamic effects and are displayed in an event-study plot.
-If the first-stage arrest rates are trending similarly before the passage of the Anti-Drug Abuse Act of 1986 and the Fair Sentencing Act of 2010, I expect the coefficients associated with pre-periods to be small and statistically insignificant.
+The coefficients $\{\beta_m \}^{M}_{m=-G}$ summarize the magnitude of the dynamic effects and are displayed in an event-study plot \footnote{Since the Anti-Drug Abuse Act was passed in October, I normalize the $\beta$ in 1986 to be zero.
+Similarly, since the Fair Sentencing Act of 2010 was passed in August, I normalize the $\beta$ on 2010 to be zero.}.
+When testing for pre-trends, if the first-stage arrest rates are trending similarly before the passage of the Anti-Drug Abuse Act of 1986 and the Fair Sentencing Act of 2010, I expect the coefficients associated with pre-periods to be small and statistically insignificant.
 
@@
 For the reduced form estimates, I report three specifications of the difference-in-difference estimates: the first omits control variables and fixed effects, the second omits fixed effects, and the third is the full regression as specified in \ref{eq:did}.
+To address issues of low power associated with event study tests for pre-trends in both the first stage and reduced form regressions, I implemented suggestions from \cite{roth2022}, which include calculating the slope of a linear violation of parallel trends that a pre-trends test would detect a specified fraction of the time, the expected value of the coefficients conditional on passing the pre-test under the hypothesized trend, and useful statistics such as power, Bayes Factor, and likelihood ratio.
+
+Overall, examining both the first-stage and reduced-form impact of the federal has the advantage of enabling me to estimate the impact of arrest rates on college enrollment for Black males.
+I conduct an instrumented difference-in-differences (DDIV) estimate where the endogenous variable is arrest rates and the instrument is an indicator for living in a high-intensity state.
+I follow the advice given in \cite{ddiv}.
+For my DDIV estimates to be causal, the exclusion restriction must be satisfied, i.e.
+it must be the case that college enrollment is only impacted through changes in arrest rates.
+I report the DDIV estimator as the simple ratio of means, and I also calculate the DDIV estimator via two-stage least squares (2SLS).
+To check whether my estimates may be affected by the weak-instrument problem, I report F-statistics.
 
@@
 All analyses use CPS October supplement final person weights and limit the sample to Black males aged 18-24 at the time of the passage of the federal act.
-
-\textbf{Counterfactual groups}
-\begin{itemize}[itemsep=0.05mm, parsep=0pt]
-  \item Black males vs white males
-  \begin{itemize}
-    \item Identifying assumption: absent of the Anti-Drug Abuse Act of 1986, black and white male educational outcomes would have trended similarly.
-  \end{itemize}
-  \item Black males vs black females
-  \item Black males aged 18-24 vs black males aged 28-34 at the time of the act
-  \item High vs low drug use
-\end{itemize}
 
@@
 In my analysis, I use Black adult arrests and Black juvenile arrests related to all drug crimes \footnote{The UCR includes data on drug offenses at a more granular level, such as type of drug, weight, and sale to a minor.}.
-Since I needed arrest data at the state and year level, I constructed a normalized arrest rate per 100,000 by averaging the counties in a state together and dividing by the state's population in a given year \footnote{The population in each state-year was taken from the CPS.}.
+Since I needed arrest data at the state and year level, I constructed a normalized arrest rate per 100,000 by averaging the arrest rate for counties with available data in a state together and dividing by the state's population in the given year \footnote{The population in each state-year was taken from the CPS.}.
 In any analysis where I used both UCR and CPS data, I merged the two datasets at the state and year level.
@@
 
-Finally, I used unemployment data at the state by year level from the \cite{unemployment_data}. For analysis at the state by year level, I simply collapse the dataset.
+Finally, I used unemployment data at the state-by-year level from the \cite{unemployment_data}. For analysis at the state-by-year level, I simply collapsed the dataset.
 
@@
 
+In this section, I evaluate the impact of the Anti-Drug Abuse Act of 1986. In the next section, I discuss the Fair Sentencing Act of 2010.
+
 \subsubsection{First Stage Estimates}
 
-\subsubsection{Placebo Tests}
+I first estimate the impact of the Anti-Drug Abuse Act of 1986 on drug-related arrest rates for Black adults and Black juveniles separately by looking at changes in arrest rates in high-drug arrest states relative to the low-drug arrest states before and after 1986.
+
+The results are presented in figure \ref{fig:ab_es_1986}, figure \ref{fig:jb_es_1986}, and table (XYZ).
+
+For Black adults, using the event study model detailed in \ref{eq:state_level_es}, I find an increase in drug-related arrest rate associated with the Anti-Drug Abuse Act with gains between 3.08 and 12.71 arrests per 100,000 during each post-expansion year.
+Using the difference-in-difference model specified in \ref{eq:did}, I find a statistically significant increase of 45.13 arrests per 100,000.
+The estimates for years 2 and 3 after the expansion are larger than the estimates for years 1 and 4, indicating that the effect of the law took some time to "kick in", and the effect potentially decreased in later years.
+`'
+To check for pretrends, in my event study model, I test the joint null hypothesis that all of the pretreatment event study coefficients are zero through an F-test, which I report at the bottom of each event study figure.
+In this case, in figure \ref{fig:ab_es_1986}, I get a $p$-value of 0.50, which increases my confidence in the parallel trends assumption.
+As a further check, I also include plots of raw outcomes over time in figure  \ref{fig:raw_college_highlowab_1986}.
+
+This suggests that the Anti-Drug Abuse Act had an impact on the justice system by incarcerated people that would have otherwise not been incarcerated, ruling out the possibility that the Act might have only affected persons who would have been incarcerated regardless by extending their sentence length (through mandatory minimum sentencing requirements).
+Therefore, although the concern that the only populations impacted by the Anti-Drug Abuse Act would not have attended college in the absence of the Act is still valid \footnote{If the populations primarily impacted by the Anti-Drug Abuse Act were not going to attend college in the absence of the Act, I would expect the Act to have no impact on college enrollment.}, this result does provide some evidence against that argument.
+
+\subsection{Reduced Form Estimates}
+
+The results are presented in figure \ref{fig:reducedform_ab}, figure \ref{fig:reducedform_jb}, and table (XYZ).
+
+I also use my second and third empirical strategies.
+For my second empirical strategy, I look to estimate the impact of the Act on college enrollment on Black males by using White males as a counterfactual group.
+
+\subsubsection{Robustness Checks}
 
@@
 
-\subsubsection{Placebo Tests}
+\subsubsection{Robustness Checks}
 
@@
 
-\subsection{Future Research}
+\subsection{Limitation}
+
+\subsection{Implications for Policy}
+
+\subsection{Implications for Future Research}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%BIB%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \clearpage

### 2023-04-18 source/analysis/pretrends_roth.R

@@ -1,41 +1,0 @@
-devtools::install_github("jonathandroth/pretrends")
-
-library(pretrends)
-
-#Load the coefficients, covariance matrix, and time periods
-beta <- c(-159.57987, -142.62841, -72.994561, 116.48307, 216.60878, 339.87964, 0)
-
-sigma <- matrix(c(19451.866, 12441.605, 5325.1719, -1520.1857, -2540.8618, -5247.2621,0,
-                  12441.605, 9783.414, 4275.8322, -2165.672, -4300.2952, -6634.0827,0,
-                  5325.1719, 4275.8322, 2543.7204, -1111.3112, -2485.4035,-3763.9298,0,
-                  -1520.1857,-2165.672,-1111.3112,8866.4137, 12543.886, 13942.985,0,
-                  -2540.8618, -4300.2952,-2485.4035, 12543.886, 21874.095, 24929.135,0,
-                  -5247.2621, -6634.0827, -3763.9298, 13942.985, 24929.135, 30176.604,0,
-                  0,0,0,0,0,0,0)
-                , nrow = 7, ncol = 7)
-isSymmetric(sigma)
-tVec <- c(-4,-3,-2,0,1,2,-1)
-referencePeriod <- -1 #This is the omitted period in the regression
-data.frame(t = tVec, beta = beta)
-
-#Compute slope that gives us 50% power
-slope50 <-
-  slope_for_power(sigma = sigma,
-                  targetPower = 0.5,
-                  tVec = tVec,
-                  referencePeriod = referencePeriod)
-slope50
-
-pretrendsResults <- 
-  pretrends(betahat = beta, 
-            sigma = sigma, 
-            tVec = tVec, 
-            referencePeriod = referencePeriod,
-            deltatrue = slope50 * (tVec - referencePeriod))
-
-pretrendsResults$event_plot
-
-#df_power shows stats about power of pre-test against hypothesized trend
-pretrendsResults$df_power
-
-pretrendsResults$event_plot_pretest

### 2023-04-18 source/figures/heatmap/heatmap.py

@@ -1,0 +1,47 @@
+import pandas as pd
+import plotly.express as px
+
+def main():
+    df = pd.read_csv('data/UCR_ICPSR/clean/ucr_avg_ab_alloffenses_1986.csv')
+    df = construct_state_abrev_col(clean(df))
+    plot(df)
+
+def clean(df):
+    df["year"] = pd.to_numeric(df["year"])
+    offense_to_drop = ["180", "185", "18A", "18B", "18C", "18D", "18E", "18F", "18G", "18H"]
+    for offense in offense_to_drop:
+        df = df.drop(df[df.OFFENSE == offense ].index)
+    for offense in range(180, 190):
+        df = df.drop(df[df.OFFENSE == str(offense) ].index)
+    df = df.drop(df[df.year != 1984].index)
+    df["ab"] = pd.to_numeric(df["ab"])
+    return df
+
+def plot(df):
+    fig = px.choropleth(df,
+                    locations='state_abbreviation', 
+                    locationmode="USA-states", 
+                    scope="usa",
+                    color='ab',
+                    color_continuous_scale="orrd", 
+                    hover_name='state_abbreviation',
+                    range_color=[0, 30],
+                    labels={'ab': 'Arrest rate'}
+                    )
+    fig.show()
+    #fig.write_image("/Users/rayhuang/Documents/Thesis-git/output/figures/heatmap/ab_heatmap.png")
+    # image is v low quality, download it from browser
+
+def construct_state_abrev_col(df):
+    state_code_to_abbreviation = {
+    1: 'AL', 2: 'AZ', 3: 'AR', 4: 'CA', 5: 'CO', 6: 'CT', 7: 'DE', 8: 'DC', 9: 'FL', 10: 'GA', 11: 'ID', 12: 'IL', 13: 'IN',
+    14: 'IA', 15: 'KS', 16: 'KY', 17: 'LA',
+    18: 'ME', 19: 'MD', 20: 'MA', 21: 'MI', 22: 'MN', 23: 'MS', 24: 'MO', 25: 'MT', 26: 'NE', 27: 'NV', 28: 'NH', 29: 'NJ',
+    30: 'NM', 31: 'NY', 32: 'NC', 33: 'ND', 34: 'OH', 35: 'OK', 36: 'OR', 37: 'PA', 38: 'RI', 39: 'SC', 40: 'SD', 41: 'TN', 
[…]

### 2023-04-18 source/figures/power/firststage_ab1986.r

@@ -1,0 +1,32 @@
+#devtools::install_github("jonathandroth/pretrends")
+
+library(pretrends)
+
+#Load the coefficients, covariance matrix, and time periods
+beta <- unlist(read.csv("coefficients_1986ab.csv"))
+sigma <- as.matrix(read.csv("var_cov_1986ab.csv"))
+tVec <- c(-2, -1, 0, 1, 2, 3, 4, 5, 6)
+referencePeriod <- 0 #This is the omitted period in the regression
+data.frame(t = tVec, beta = beta)
+
+#Compute slope that gives us 50% power
+slope50 <-
+  slope_for_power(sigma = sigma,
+                  targetPower = 0.5,
+                  tVec = tVec,
+                  referencePeriod = referencePeriod)
+slope50
+
+pretrendsResults <- 
+  pretrends(betahat = beta, 
+            sigma = sigma, 
+            tVec = tVec, 
+            referencePeriod = referencePeriod,
+            deltatrue = slope50 * (tVec - referencePeriod))
+
+pretrendsResults$event_plot 
+
+#df_power shows stats about power of pre-test against hypothesized trend
+pretrendsResults$df_power
+
+pretrendsResults$event_plot_pretest

### 2023-04-19 output/tables/ddiv/ddiv_show2.tex
Just in case...

@@
 \centering
-\caption{Mean of Drug-related Arrest Rate and College Enrollment Rate By Time and High/low Drug Arrest State}
+\caption{Means of Arrest Rate and College Enrollment Rate By Pre and Post-Period and High-Intensity States}
 \resizebox{0.9\linewidth}{!}{
@@
 \hline
-& \multicolumn{3}{c}{Drug-Related Arrest Rate} & \multicolumn{3}{c}{College Enrollment} \\ 
+& \multicolumn{3}{c}{Drug-related arrest rate} & \multicolumn{3}{c}{College enrollment} \\ 
 \cline{2-4} \cline{5-7}

### 2023-04-19 source/paper/appendix_figures.tex
Just in case...

--- 2023-04-12 source/paper/figures.tex
@@
-  % High vs low arrest states pretrends
-
-  \begin{figure}[h]
-    \centering
-    \caption{College Enrollment By States with High vs Low Black Adult Drug Arrest Rates}%
-    \subfloat[\centering 1986]{{\includegraphics[width=7cm]{pretrends/1986/college_enroll_bydrugarrests_1986.png} }}%
-    \qquad
-    \subfloat[\centering 2010]{{\includegraphics[width=7cm]{pretrends/2010/college_enroll_bydrugarrests_2010.png} }}%
-    \label{fig:raw_college_highlowab_1986}%
-  \end{figure}
-  \begin{figure}[h]
-    \centering
-    \caption{College Enrollment By States with High vs Low Black Juvenile Drug Arrest Rates}%
-    \subfloat[\centering 1986]{{\includegraphics[width=7cm]{pretrends/1986/college_enroll_bydrugarrests_jb_1986.png} }}%
-    \qquad
-    \subfloat[\centering 2010]{{\includegraphics[width=7cm]{pretrends/2010/college_enroll_bydrugarrests_jb_2010.png} }}%
-    \label{fig:raw_college_highlowjb_1986}%
-  \end{figure}
-
-  \begin{footnotesize}
-    \noindent Note: These figures report the proportion enrolled in college plotted over time using CPS data from 1984-1992 and 2005-2016 for high black adult/juvenile drug arrest states and low black adult/juvenile drug arrest states, where high black adult/juvenile drug arrest states are defined to be those above the 75th percentile in 1984 and 2008.
-A vertical line is drawn to denote the passage of the Anti-Drug Abuse Act of 1986 and the Fair Sentencing Act of 2010.
-The sample is defined as black males aged 18-24 in 1986 and 2010 who were not incarcerated at the time of the survey.
-  \end{footnotesize}
-
-  \clearpage
-
-  % Arrest rate pretrends
-
-  \begin{figure}[h]
-    \centering
-    \caption{Adult Black Arrest Rate Per 100,000}%
-    \subfloat[\centering 1986]{{\includegraphics[width=7cm]{pretrends/1986/ab.png} }}%
-    \qquad
-    \subfloat[\centering 2010]{{\includegraphics[width=7cm]{pretrends/2010/ab.png} }}%
-    \label{fig:raw_ab}%
-  \end{figure}
-  \begin{figure}[h]
-    \centering
-    \caption{Juvenile Black Arrest Rate Per 100,000}%
-    \subfloat[\centering 1986]{{\includegraphics[width=7cm]{pretrends/1986/ab.png} }}%
-    \qquad
-    \subfloat[\centering 2010]{{\includegraphics[width=7cm]{pretrends/2010/jb.png} }}%
-    \label{fig:raw_jb}%
-  \end{figure}
-
-  \begin{footnotesize}
-    \noindent Note: These figures report the drug crime arrest rate per 100,000 for black adults and black juveniles separately over time using CPS-UCR merged data from 1984-1992 and 2005-2016.
-A vertical line is drawn to denote the passage of the Anti-Drug Abuse Act of 1986 and the Fair Sentencing Act of 2010.
-  \end{footnotesize}
-
-  \clearpage
-
 % 1986 pretrends
@@
     \centering
-    \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_drug_eventstudy_1986.png}
-    \label{fig:ab_es_1986}
-  \end{figure}
-
-  \begin{footnotesize}
-    \noindent Note: This figure reports coefficients from the estimation of equation \ref{eq:state_level_es} evaluating the impact of the Anti-Drug Abuse Act of 1986 on arrest rates per 100,000 related to drug violations using CPS and UCR data from 1982-1992.
-Event time $0 \coloneqq 1986$.
-The coefficients represent the change in outcomes for high-drug arrest states relative to non-high-drug arrest states, where high black adult drug arrest states are defined to be those above the 75th percentile in 1984.
-The sample is defined as black males aged 18-24 in 1986 who were not incarcerated at the time of the survey.
-Control variables include population and unemployment rates at the state-year level.
-Right tail arrest rate outliers were winsorizing at the 95\% level.
-  \end{footnotesize}
-
-  \clearpage
-
-  %\begin{figure*}[h]
-   % \caption{Pretrends for Event study 1986, AB arrest rate 18F}
-   % \includegraphics[width=1\textwidth]{roth_test.png}
-  %\end{figure*}
-
-  %Power: 0.499. Bayes.Factor: 0.550.  Likelihood.Ratio: 2.024
-
-  %\clearpage
-
-  \begin{figure}[h]
-    \caption{Effect of Fair Sentencing Act on Drug-related Arrest Rate of Adult Black Men, Comparing States with High and Low Black Adult Drug-Related Arrest Rate}
-    \centering
-    \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_drug_eventstudy_2010_ab.png}
-    \label{fig:ab_es_2010}
-  \end{figure}
-
-  \begin{footnotesize}
-    \noindent Note: This figure reports coefficients from the estimation of equation 1 evaluating the impact of the Fair Sentencing Act of 2010 on arrest rates per 100,000 related to drug violations using CPS and UCR data from 2005-2015.
-Event time $0 \coloneqq 2010$.
-The coefficients represent the change in outcomes for high black adult drug arrest states relative to non-high-drug arrest states, where high-drug arrest states are defined to be those above the 75th percentile in 2008.
-The sample is defined as black males aged 18-24 in 2010 who were not incarcerated at the time of the survey.
-Control variables include population and unemployment rates at the state-year level.
-  \end{footnotesize}
-
-\clearpage
-
-  \begin{figure}[h]
-    \caption{Effect of Anti-Drug Abuse Act on Drug-related Arrest Rate of Black Men, Comparing States with High and Low Black Juvenile Drug-Related Arrest Rate}
-    \centering
-    \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_drug_eventstudy_1986_jb.png}
-    \label{fig:jb_es_1986}
-  \end{figure}
-
-  \begin{footnotesize}
-    \noindent Note: This figure reports coefficients from the estimation of equation 1 evaluating the impact of the Anti-Drug Abuse Act of 1986 on arrest rates per 100,000 related to drug violations using CPS and UCR data from 1982-1992.
-Event time $0 \coloneqq 1986$.
-The coefficients represent the change in outcomes for high black juvenile drug arrest states relative to non-high-drug arrest states, where high-drug arrest states are defined to be those above the 75th percentile in 1984.
-The sample is defined as black males aged 18-24 in 1986 who were not incarcerated at the time of the survey.
-Control variables include population and unemployment rates at the state-year level.
-  \end{footnotesize}
-
-\clearpage
-
-\begin{figure}[h]
-    \caption{Effect of Fair Sentencing Act on Drug-related Arrest Rate of Juvenile Black Men, Comparing States with High and Low Black Juvenile Drug-Related Arrest Rate}
-    \centering
-    \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_drug_eventstudy_2010_jb.png}
-    \label{fig:jb_es_2010}
-  \end{figure}
-
-  \begin{footnotesize}
-    \noindent Note: This figure reports coefficients from the estimation of equation \ref{eq:1} evaluating the impact of the Fair Sentencing act of 2010 on arrest rates per 100,000 related to drug violations using CPS and UCR data from 2005-2015.
-Event time $0 \coloneqq 2010$.
-The coefficients represent the change in outcomes for high black juvenile drug arrest states relative to non-high-drug arrest states, where high-drug arrest states are defined to be those above the 75th percentile in 2008.
-The sample is defined as black males aged 18-24 in 2010 who were not incarcerated at the time of the survey.
-Control variables include population and unemployment rates at the state-year level.
-  \end{footnotesize}
-
-  \clearpage
-
-  \begin{figure}[h]
-    \centering
-    \caption{Distribution of Black Juvenile Drug-Related Arrest Rates By State / Year}%
-    \subfloat[\centering 1986]{{\includegraphics[width=7cm]{descriptive/norm_jb_100000_density_1986} }}%
-    \qquad
-    \subfloat[\centering 2010]{{\includegraphics[width=7cm]{descriptive/norm_jb_100000_density_2010.png} }}%
-    \label{fig:density_jb}%
+    \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_drug_eventstudy_1986_extended_years.png}
+    \label{fig:b1}
   \end{figure}
   \begin{footnotesize}
-    \noindent Note: These figures report the kernel density estimates for the normalized drug-related black juvenile arrest rate at the state-by-year level. 
+    \noindent Note: footnote TO BE UPDATED
   \end{footnotesize}

### 2023-04-19 source/paper/figures.tex
Just in case...

@@
+   % Arrest rate pretrends
+
+   \begin{figure}[h]
+    \centering
+    \caption{Adult Black Arrest Rate Per 100,000}%
+    \subfloat[\centering 1986]{{\includegraphics[width=7cm]{pretrends/1986/ab.png} }}%
+    \qquad
+    \subfloat[\centering 2010]{{\includegraphics[width=7cm]{pretrends/2010/ab.png} }}%
+    \label{fig:raw_ab}%
+  \end{figure}
+  \begin{figure}[h]
+    \centering
+    \caption{Juvenile Black Arrest Rate Per 100,000}%
+    \subfloat[\centering 1986]{{\includegraphics[width=7cm]{pretrends/1986/ab.png} }}%
+    \qquad
+    \subfloat[\centering 2010]{{\includegraphics[width=7cm]{pretrends/2010/jb.png} }}%
+    \label{fig:raw_jb}%
+  \end{figure}
+
+  \begin{footnotesize}
+    \noindent Note: These figures report the drug crime arrest rate per 100,000 for black adults and black juveniles separately over time using CPS-UCR merged data from 1984-1992 and 2005-2016.
+A vertical line is drawn to denote the passage of the Anti-Drug Abuse Act of 1986 and the Fair Sentencing Act of 2010.
+  \end{footnotesize}
+
+  \clearpage
+
   % High vs low arrest states pretrends
@@
 
-  % Arrest rate pretrends
-
   \begin{figure}[h]
+    \caption{Black Adult Drug-related Arrest Rate Per 100,000 in 1984} 
     \centering
-    \caption{Adult Black Arrest Rate Per 100,000}%
-    \subfloat[\centering 1986]{{\includegraphics[width=7cm]{pretrends/1986/ab.png} }}%
-    \qquad
-    \subfloat[\centering 2010]{{\includegraphics[width=7cm]{pretrends/2010/ab.png} }}%
-    \label{fig:raw_ab}%
-  \end{figure}
-  \begin{figure}[h]
-    \centering
-    \caption{Juvenile Black Arrest Rate Per 100,000}%
-    \subfloat[\centering 1986]{{\includegraphics[width=7cm]{pretrends/1986/ab.png} }}%
-    \qquad
-    \subfloat[\centering 2010]{{\includegraphics[width=7cm]{pretrends/2010/jb.png} }}%
-    \label{fig:raw_jb}%
-  \end{figure}
-
-  \begin{footnotesize}
-    \noindent Note: These figures report the drug crime arrest rate per 100,000 for black adults and black juveniles separately over time using CPS-UCR merged data from 1984-1992 and 2005-2016.
-A vertical line is drawn to denote the passage of the Anti-Drug Abuse Act of 1986 and the Fair Sentencing Act of 2010.
-  \end{footnotesize}
-
-  \clearpage
-
-% 1986 pretrends
-
-\begin{figure}[h]
-    \centering
-    \caption{College Enrollment Around 1984}%
-    \subfloat[\centering By race]{{\includegraphics[width=7cm]{pretrends/1986/college_enroll_byrace_1986.png} }}%
-    \qquad
-    \subfloat[\centering By sex]{{\includegraphics[width=7cm]{pretrends/1986/college_enroll_bysex_1986.png} }}%
-    \label{fig:raw_college_1986}%
-  \end{figure}
-
-  \begin{figure}[h]
-    \centering
-    \caption{Family Income Around 1984}%
-    \subfloat[\centering By race]{{\includegraphics[width=7cm]{pretrends/1986/faminc_byrace_1986.png} }}%
-    \qquad
-    \subfloat[\centering By sex]{{\includegraphics[width=7cm]{pretrends/1986/faminc_bysex_1986.png} }}%
-    \label{fig:raw_faminc_1986}%
-  \end{figure}
-
-  \begin{footnotesize}
-    \noindent Note: These figures report the outcomes for various subgroups plotted over time using CPS data from 1984-1992.
-Figure \ref{fig:raw_college_1986} reports the proportion enrolled in college, while figure \ref{fig:raw_faminc_1986} reports the average family income.
-A vertical line is drawn to denote the passage of the Anti-Drug Abuse Act of 1986.
-The universe of samples is defined as participants aged 18-24 in 1986 who were not incarcerated at the time of the survey.
-  \end{footnotesize}
-
-  \clearpage
-
-  % 2010 pretrends
-
-  \begin{figure}[h]
-    \centering
-    \caption{College Enrollment Around 2010}%
-    \subfloat[\centering By race]{{\includegraphics[width=7cm]{pretrends/2010/college_enroll_byrace_2010.png} }}%
-    \qquad
-    \subfloat[\centering By sex]{{\includegraphics[width=7cm]{pretrends/2010/college_enroll_bysex_2010.png} }}%
-    \label{fig:raw_college_2010}%
-  \end{figure}
-
-  \begin{figure}[h]
-    \centering
-    \caption{Family Income Around 2010}%
-    \subfloat[\centering By race]{{\includegraphics[width=7cm]{pretrends/2010/faminc_byrace_2010.png} }}%
-    \qquad
-    \subfloat[\centering By sex]{{\includegraphics[width=7cm]{pretrends/2010/faminc_bysex_2010.png} }}%
-    \label{fig:raw_faminc_2010}%
-  \end{figure}
-
-  \begin{footnotesize}
-    \noindent Note: These figures report the outcomes for various subgroups plotted over time using CPS data from 2005-2016.
-Figure \ref{fig:raw_college_2010} reports the proportion enrolled in college, while figure \ref{fig:raw_faminc_2010} reports the average family income.
-A vertical line is drawn to denote the passage of the Fair Sentencing Act of 2010.
-The universe of samples is defined as participants aged 18-24 in 2010 who were not incarcerated at the time of the survey.
-  \end{footnotesize}
-
-  \clearpage
-
-  \begin{figure}[h]
-    \caption{Black Adult Drug-related Arrest Rate in 1984}
-    \centering
-    \includegraphics[width=1\textwidth]{heatmap/ab1986.png}
+    \includegraphics[width=0.8\textwidth]{heatmap/ab1986.png}
     \label{fig:heatmap}
@@
 
+  \vspace*{8mm}
+
+  \begin{figure}[h]
+    \centering
+    \caption{Distribution of Black Adult Drug-Related Arrest Rates}%
+    \subfloat[\centering 1984]{{\includegraphics[width=7cm]{descriptive/norm_jb_100000_density_1986} }}%
+    \qquad
+    \subfloat[\centering 2008]{{\includegraphics[width=7cm]{descriptive/norm_jb_100000_density_2010.png} }}%
+    \label{fig:density_jb}%
+  \end{figure}
+  \begin{footnotesize}
+    \noindent Note: These figures report the kernel density estimates for the normalized drug-related Black adult arrest rate in 1984 and 2008.
+The vertical line denotes the 75th percentile.
+Right tail outliers were winsorized at the 95\% level for both figures.
+  \end{footnotesize}
+
   \clearpage
+
   % Event study
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{eventstudy/high_drug_use/high_drug_eventstudy_1986.png}
+    \includegraphics[width=0.7\textwidth]{eventstudy/high_drug_use/high_drug_eventstudy_1986.png}
     \label{fig:ab_es_1986}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{eventstudy/high_drug_use/high_drug_eventstudy_nofe_1986.png}
+    \includegraphics[width=0.7\textwidth]{eventstudy/high_drug_use/high_drug_eventstudy_nofe_1986.png}
     \label{fig:ab_es_1986_nofe}
@@
 Control variables include population and unemployment rates at the state-year level.
-Right tail arrest rate outliers were winsorizing at the 95\% level.
-  \end{footnotesize}
-
-  \clearpage
-
-  \begin{figure}[h]
-    \caption{Effect of Fair Sentencing Act on Drug-related Arrest Rate of Adult Black Men, Comparing States with High and Low Black Adult Drug-Related Arrest Rate}
-    \centering
-    \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_drug_eventstudy_2010_ab.png}
-    \label{fig:ab_es_2010}
-  \end{figure}
-
-  \begin{footnotesize}
-    \noindent Note: This figure reports coefficients from the estimation of equation 1 evaluating the impact of the Fair Sentencing Act of 2010 on arrest rates per 100,000 related to drug violations using CPS and UCR data from 2005-2015.
-Event time $0 \coloneqq 2010$.
-The coefficients represent the change in outcomes for high black adult drug arrest states relative to non-high-drug arrest states, where high-drug arrest states are defined to be those above the 75th percentile in 2008.
-The sample is defined as black males aged 18-24 in 2010 who were not incarcerated at the time of the survey.
-Control variables include population and unemployment rates at the state-year level.
+Right tail arrest rate outliers were winsorized at the 95\% level.
   \end{footnotesize}
@@
   \begin{figure}[h]
-    \caption{Effect of Fair Sentencing Act on Drug-related Arrest Rate of Juvenile Black Men, Comparing States with High and Low Black Juvenile Drug-Related Arrest Rate}
     \centering
-    \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_drug_eventstudy_2010_jb.png}
-    \label{fig:jb_es_2010}
+    \caption{Additional Pretrend Testing for Coefficients from Figure 7}%
+    \subfloat[\centering Linear pretrend]{{\includegraphics[width=7cm]{pretrends/power/firststage_linear_ab1986.png} }}%
+    \qquad
+    \subfloat[\centering Quadratic pretrend]{{\includegraphics[width=7cm]{pretrends/power/firststage_quad_ab1986.png} }}%
+    \label{fig:pretrends_roth}%
   \end{figure}
@@
   \begin{footnotesize}
-    \noindent Note: This figure reports coefficients from the estimation of equation \ref{eq:1} evaluating the impact of the Fair Sentencing act of 2010 on arrest rates per 100,000 related to drug violations using CPS and UCR data from 2005-2015.
+    \noindent Note: These two figures were constructed using an R package written by \cite{roth2022}.
+The figures and pretrend statistics were calculated using the estimated coefficients from Figure 7 and their corresponding covariance matrixes.
+The slope in Figure A was constructed such that the power would be about 0.5, while the quadratic trend in Figure B was chosen visually.
+
+    Figure A statistics: 1) power = 0.499, 2) Bayes Factor = 0.549, 3) likelihood ratio = 0.033.
+
+    Figure B statistics: 1) power = 0.155, 2) Bayes Factor = 0.928, 3) likelihood ratio = 2.323.
+  \end{footnotesize}
+
+  \clearpage
+
+  \begin{figure}[h]
+    \centering
+    \caption{Effect of Fair Sentencing Act on Drug-related Arrest Rate of Adult Black Men, Comparing High and Low-Intensity States}%
+    \subfloat[\centering Using adults arrests]{{\includegraphics[width=7cm]{eventstudy/high_drug_use/high_drug_eventstudy_2010_ab.png} }}%
+    \qquad
+    \subfloat[\centering Using juvenile arrests]{{\includegraphics[width=7cm]{eventstudy/high_drug_use/high_drug_eventstudy_2010_jb.png} }}%
+    \label{fig:fs_es_2010}%
+  \end{figure}
+
+  \begin{footnotesize}
+    \noindent Note: These figures report coefficients from the estimation of equation 1 evaluating the impact of the Fair Sentencing Act of 2010 on arrest rates per 100,000 related to drug violations using CPS-UCR merged data from 2005-2015.
+Figure A defines high-intensity states using Black adult arrests, while Figure B defines high-intensity states using Black juvenile arrests.
 Event time $0 \coloneqq 2010$.
-The coefficients represent the change in outcomes for high black juvenile drug arrest states relative to non-high-drug arrest states, where high-drug arrest states are defined to be those above the 75th percentile in 2008.
+The coefficients represent the change in outcomes for high black adult drug arrest states relative to non-high-drug arrest states, where high-drug arrest states are defined to be those above the 75th percentile in 2008.
 The sample is defined as black males aged 18-24 in 2010 who were not incarcerated at the time of the survey.
@@
   \centering
-    \caption{Distribution of Black Adult Drug-Related Arrest Rates}%
-    \subfloat[\centering 1984]{{\includegraphics[width=7cm]{descriptive/norm_jb_100000_density_1986} }}%
+  \caption{Effect of Fair Sentencing Act on the College Enrollment Rate of Adult Black Men, Comparing High and Low-Intensity States}%
+  \subfloat[\centering Using adults arrests]{{\includegraphics[width=7cm]{eventstudy/high_drug_use/reducedform_ab1986.png} }}%
   \qquad
-    \subfloat[\centering 2008]{{\includegraphics[width=7cm]{descriptive/norm_jb_100000_density_2010.png} }}%
-    \label{fig:density_jb}%
+  \subfloat[\centering Using juvenile arrests]{{\includegraphics[width=7cm]{eventstudy/high_drug_use/reducedform_jb1986.png} }}%
+  \label{fig:rs_es_1986}%
 \end{figure}
+
 \begin{footnotesize}
-    \noindent Note: These figures report the kernel density estimates for the normalized drug-related Black adult arrest rate in 1984 and 2008.
-The vertical line denotes the 75th percentile.
-Right tail outliers were winsorized at the 95\% level for both figures.
+  \noindent Note: These figures report coefficients from the estimation of equation 1 evaluating the impact of the Anti-Drug Abuse Act of 1986 on college enrollment rates using CPS-UCR merged data from 1984-1992.
+Figure A defines high-intensity states using Black adult arrests, while Figure B defines high-intensity states using Black juvenile arrests.
+Event time $0 \coloneqq 1986$.
+The coefficients represent the change in outcomes for high black adult drug arrest states relative to non-high-drug arrest states, where high-drug arrest states are defined to be those above the 75th percentile in 1984.
+The sample is defined as black males aged 18-24 in 1986 who were not incarcerated at the time of the survey.
+Control variables include population and unemployment rates at the state-year level.
 \end{footnotesize}
@@
   \centering
-  \caption{Effect of ADAA and FSA on the College Enrollment Rate of Adult Black Men, Comparing States with High and Low Black Adult Drug-Related Arrest Rates}%
-  \subfloat[\centering 1986]{{\includegraphics[width=7cm]{eventstudy/high_drug_use/reducedform_ab1986.png} }}%
+  \caption{Effect of Fair Sentencing Act on the College Enrollment Rate of Adult Black Men, Comparing High and Low-Intensity States}%
+  \subfloat[\centering Using adults arrests]{{\includegraphics[width=7cm]{eventstudy/high_drug_use/reducedform_ab1986.png} }}%
   \qquad
-  \subfloat[\centering 2010]{{\includegraphics[width=7cm]{eventstudy/high_drug_use/reducedform_ab2010.png} }}%
-  \label{fig:reducedform_ab}%
+  \subfloat[\centering Using juvenile arrests]{{\includegraphics[width=7cm]{eventstudy/high_drug_use/reducedform_jb2010.png} }}%
+  \label{fig:rf_jb_es_2010}%
 \end{figure}
-\begin{figure}[h]
-  \centering
-  \caption{Effect of ADAA and FSA on the College Enrollment Rate of Adult Black Men, Comparing States with High and Low Black Juvenile Drug-Related Arrest Rates}%
-  \subfloat[\centering 1986]{{\includegraphics[width=7cm]{eventstudy/high_drug_use/reducedform_jb1986.png} }}%
-  \qquad
-  \subfloat[\centering 2010]{{\includegraphics[width=7cm]{eventstudy/high_drug_use/reducedform_ab1986.png} }}%
-  \label{fig:reducedform_jb}%
-\end{figure}
+
+\begin{footnotesize}
+  \noindent Note: These figures report coefficients from the estimation of equation 1 evaluating the impact of the Fair Sentencing Act of 2010 on college enrollment rates using CPS-UCR merged data from 2005-2015.
+Figure A defines high-intensity states using Black adult arrests, while Figure B defines high-intensity states using Black juvenile arrests.
+Event time $0 \coloneqq 2010$.
+The coefficients represent the change in outcomes for high black adult drug arrest states relative to non-high-drug arrest states, where high-drug arrest states are defined to be those above the 75th percentile in 2008.
+The sample is defined as black males aged 18-24 in 2010 who were not incarcerated at the time of the survey.
+Control variables include population and unemployment rates at the state-year level.
+\end{footnotesize}
+
+\clearpage

### 2023-04-19 source/paper/main.tex
Just in case...

@@
 
-% Challenges???
-
-The endogeneity problem at hand
-
 % This paper
@@
 I use three separate research designs.
-The first and primary research design leverages variations in the intensity of drug arrests across different states.
+The first and primary research design combats the endogeneity problem by leveraging variations in the intensity of drug arrests across different states.
 High-intensity states are defined as states with Black adult drug-related arrest rates above the 75th percentile two years before the passage of the federal drug act (e.g.
@@
 % Literature
-This paper heavily builds upon recent work by \cite{britton2022}.
+This paper heavily builds upon recent work by \cite{britton2022}, who estimates the impact of the Anti-Drug Abuse Act on college enrollment and the impact of state-level legislation on college enrollment.
+She finds that "Black males had a 2.2 percentage point decrease in the relative probability of college enrollment after the passage of the Anti-Drug Abuse Act of 1986." I build upon her work by introducing a new counterfactual group that allows the impact to be split into a first-stage and reduced-form.
+I also introduce more modern and robust methods to deal with the issue of pretrends, and I spend some time replicating her results.
 
@@
 
-Some prior literature includes \cite{aizer} which evaluates the relationship between juvenile incarceration and later life outcomes using a judge-IV research design.
+Some related prior literature includes \cite{aizer} which evaluates the relationship between juvenile incarceration and later life outcomes using a judge-IV research design.
 They find that juvenile incarceration "results in large decreases in the likelihood of high school completion and large increases in the likelihood of adult incarceration." \cite{western} evaluates the impact of incarceration on labor market outcomes.
@@
 \cite{hatzenbuehler2015collateral} finds that high incarceration rates have psychiatric impacts on non-incarcerated populations, implying that if the federal drug acts have a large impact on arrest rates, there may be spillover effects.
+
+The rest of the paper is organized as such: in section 2 I summarize the history and known impacts of the Anti-Drug Abuse Act and Fair Sentencing Act.
+In section 3 I describe my empirical strategies, and in section 4 I discuss the data and its flaws.
+I present my results in section 5, and I close in section 6 with conclusions and implications.
 
@@
 For the reduced form estimates, I report three specifications of the difference-in-difference estimates: the first omits control variables and fixed effects, the second omits fixed effects, and the third is the full regression as specified in \ref{eq:did}.
+To increase power, I also include difference-in-difference regressions with a continuous treatment variable instead of an indicator variable.
+
 To address issues of low power associated with event study tests for pre-trends in both the first stage and reduced form regressions, I implemented suggestions from \cite{roth2022}, which include calculating the slope of a linear violation of parallel trends that a pre-trends test would detect a specified fraction of the time, the expected value of the coefficients conditional on passing the pre-test under the hypothesized trend, and useful statistics such as power, Bayes Factor, and likelihood ratio.
@@
 I report the DDIV estimator as the simple ratio of means, and I also calculate the DDIV estimator via two-stage least squares (2SLS).
+If the exclusion restriction is satisfied, then my estimate applies to populations whose arrest rate was increased by the federal drug act.
 To check whether my estimates may be affected by the weak-instrument problem, I report F-statistics.
@@
 drug possession, drug distribution, assault, robbery, etc) and also records data on the age \footnote{The UCR data separately tracks arrest rates for adult and juvenile cases.} and race of the arrested.
-In my analysis, I use Black adult arrests and Black juvenile arrests related to all drug crimes \footnote{The UCR includes data on drug offenses at a more granular level, such as type of drug, weight, and sale to a minor.}.
+In my analysis, I use Black adult arrests and Black juvenile arrests related to all drug crimes \footnote{The universe of all drug crimes corresponds to code 18 in the UCR program data.
+The UCR program includes data on drug offenses at a more granular level, such as type of drug, weight, and sale to a minor.}.
 Since I needed arrest data at the state and year level, I constructed a normalized arrest rate per 100,000 by averaging the arrest rate for counties with available data in a state together and dividing by the state's population in the given year \footnote{The population in each state-year was taken from the CPS.}.
-In any analysis where I used both UCR and CPS data, I merged the two datasets at the state and year level.
+In any analysis where I used both UCR and CPS data, I merged the two datasets at the state and year level \footnote{The merged dataset is henceforth referenced as CPS-UCR merged dataset}.
 
@@
 The estimates for years 2 and 3 after the expansion are larger than the estimates for years 1 and 4, indicating that the effect of the law took some time to "kick in", and the effect potentially decreased in later years.
-`'
+
 To check for pretrends, in my event study model, I test the joint null hypothesis that all of the pretreatment event study coefficients are zero through an F-test, which I report at the bottom of each event study figure.
 In this case, in figure \ref{fig:ab_es_1986}, I get a $p$-value of 0.50, which increases my confidence in the parallel trends assumption.
-As a further check, I also include plots of raw outcomes over time in figure  \ref{fig:raw_college_highlowab_1986}.
+I additionally included plots of raw outcomes over time in figure  \ref{fig:raw_college_highlowab_1986}.
+As an additional robustness check, I implement suggestions from \cite{roth2022} in figure \ref{fig:pretrends_roth} \footnote{Using Roth's R package "pretrends", I calculate statistics about the power of the pre-test against the hypothesized trend.
+I calculate the power defined as the probability that I would find a significant pretrend under the hypothesized pretrend, the Bayes Factor defined as the ratio of the probability of failing to reject the pretest under the hypothesized trend relative to under parallel trends, and the likelihood ratio which is defined to be the ratio of the likelihood of the observed coefficients under the hypothesized trend relative to under parallel trends.}.
+Overall, the results imply that if there exists a pretrend, a quadratic pretrends is more worrying than the linear pretrend, as I have less power to detect a significant pretrend and the likelihood ratio is much higher.
 
@@
 
-\subsection{Reduced Form Estimates}
+\subsubsection{Reduced Form Estimates}
 
@@
 
-I also use my second and third empirical strategies.
-For my second empirical strategy, I look to estimate the impact of the Act on college enrollment on Black males by using White males as a counterfactual group.
+Notably, in Table 2 when examining a simple difference in means, the difference in college enrollment rates between pre and post-period for high and low-intensity states for Black adult drug-related arrests is -2.3\%, which matches the result in \cite{britton2022}
+
+\subsubsection{Second Stage Estimates}
+
+The second stage DDIV results are presented in Table 3.
+Overall, I find a small negative effect of arrest rates on college enrollment in all three 2SLS specifications; however, the coefficients are small and statistically insignificant with large standard errors.
+If I scale the variables up, my estimate (with fixed effects and control variables) implies that if the arrest rate increased by 1000 Black Adult drug-related arrests per 100,000, then the college enrollment rate would decline by approximately 2.5 persons.
+
+To test for the weak-instrument problem, I also report F-statistics from the first-stage regression, following conventional advice from \cite{staiger1997precise}.
+In my case, I find an F-statistic ranging from 15.9 to 20.2, providing evidence that my estimates are not biased by the weak-instrument problem.
+
+\subsubsection{Additional Reduced Form Estimates}
 
@@
 
+I find that the first empirical strategy leveraging variation between high and low-intensity states is not an appropriate research design for studying the impact of the Fair Sentencing Act of 2010 on drug-related arrest rates.
+The results of the event study regressions specified in equation \ref{eq:state_level_es} can be found in figures XYZ.
+The coefficients provide strong evidence of significant pretrends in arrest rates before the passage of the Fair Sentencing Act.
+
 \subsubsection{Reduced form estimates}
@@
 
-\subsection{Limitation}
+To the best of my knowledge, my paper presents the first direct estimate of the relationship between drug-related arrest rates and college enrollment.
+
+\subsection{Limitations}
+
+estimates are downards biased -cps and ucr missing key data
 
@@
 
-\subsection{Implications for Future Research}
+\subsection{Future Research}
 
-estimates are downards biased -cps and ucr missing key data
-
-\subsection{Future Research}
+Other ideas for future research include exploring the impact of state-level policies on arrest rates and educational outcomes.
+\cite{britton2022} uses differences in marijuana laws, and future research can leverage other drug laws while introducing modern methods such as synthetic control designs.
 synthetic control methods, etc
@@
 \clearpage
-\nocite{*}
-\singlespacing
 \bibliographystyle{jpe}
@@
 \begin{appendices}
+  \section{Data}
+  I include a summary statistics table for the CPS data that is not merged with the UCR program data.
+
   \section{Additional Results}
@@
   \section{First stage arrest rate estimates}
+  I include tables for the equation \ref{eq:state_level_es} estimates presented in figures XYZ.
+
   In \cite{britton2022}, when examining the impact of the Anti-Drug Abuse Act of 1986, she commences her analysis in 1984 due to "fluctuations in Black college enrollment during the early 1980s that were unrelated to the emergence of drug markets \cite{nces}".
-  % Start appendix figures
+
+  \section{Reduced form college enrollment estimates}
+  I include tables for the equation \ref{eq:state_level_es} estimates presented in figures XYZ.
+
   \clearpage
 
-  \begin{figure}[h]
-    \caption{Effect of Anti-Drug Abuse Act on Drug-related Arrest Rate of Adult Black Men, Comparing States with High and Low Black Adult Drug-Related Arrest Rates}
-    \centering
-    \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_drug_eventstudy_1986_extended_years.png}
-    \label{fig:b1}
-  \end{figure}
+  % Appendix figures
+  \input{appendix_figures}
 
+  \clearpage
+
+  % Appendix tables
+  \import{../../output/tables/summ_stats/}{cps_only_summ_stats.tex}
   \begin{footnotesize}
-    \noindent Note: footnote
+    \noindent Note: Sample means with education supplement weights are calculated from the CPS October supplement dataset from 1984 to 1992 and 2000 to 2016.
+The sample in columns 1 and 2 is defined as persons aged 18-24 in 1986, and the sample in columns 3 and 4 is defined as persons aged 18-24 in 2010, both of whom were not incarcerated at the time of the survey.
+This table is partially replicated from \cite{britton2022}.
   \end{footnotesize}
+  \clearpage
+  % First stage event study table
+  \import{../../output/tables/eventstudy}{eventstudy_firststage.tex}
+
+  \clearpage
+
+  % Reduced form
+  \import{../../output/tables/eventstudy}{eventstudy_reducedform.tex}
 

### 2023-04-19 source/paper/tables.tex
Update
Just in case...

@@
 \begin{footnotesize}
-  \noindent Note: Sample means (with education weights) are displayed from the CPS October supplement merged with the UCR dataset from 1984-1992 and 2000-2016.
-The sample in columns 1 and 2 are defined as persons aged 18-24 in 1986, and the sample in columns 3 and 4 are defined as persons aged 18-24 in 2010, who were not incarcerated at the time of the survey.
-This table is partially replicated from \cite{britton2022}.
+  \noindent Note: Sample means with education supplement weights are calculated from the CPS-UCR merged dataset from 1984 to 1992 and 2000 to 2016.
+The sample in columns 1 and 2 is defined as persons aged 18-24 in 1986, and the sample in columns 3 and 4 is defined as persons aged 18-24 in 2010, both of whom were not incarcerated at the time of the survey.
 \end{footnotesize}
 
-\import{../../output/tables/summ_stats/}{cps_only_summ_stats.tex}
 \clearpage
 
-%\import{../../output/tables/summ_stats/}{ucr_summ_stats.tex}
+\import{../../output/tables/ddiv}{ddiv_show2.tex}
+\begin{footnotesize}
+  \noindent Note: The CPS-UCR merged dataset is used for this table.
+Mean estimates are weighted using CPS October supplement weights.
+No controls or fixed effects were used, and significance stars are omitted.
+Robust standard errors are clustered at the state level.
+The sample is defined as males aged 18-24 in 1986 who were not incarcerated at the time of the survey.
+\end{footnotesize}
 
-% Britton Table 2
-\import{../../output/tables/}{britton_table2_DiD.tex}
+\clearpage
+
+\import{../../output/tables/ddiv}{iv.tex}
+\begin{footnotesize}
+  \noindent Note: The CPS-UCR merged dataset is used for this table.
+Estimates are weighted using CPS October supplement weights.
+The controls used at the individual level include age, age-squared, Latino ethnicity, and binned family income.
+The controls used at the state level include unemployment and population.
+  Robust standard errors are clustered at the state level. The sample is defined as males aged 18-24 in 1986 who were not incarcerated at the time of the survey. 
+\end{footnotesize}
+
+\clearpage
+
+%DiD High/low intensity
+
+\import{../../output/tables/}{DiD_1986_high_low.tex}
 \begin{footnotesize}
@@
 Robust standard errors are clustered at the state level.
-Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income.
-The sample is defined as black and white males aged 18-24 in 1986 who were not incarcerated at the time of the survey.
-  This table is partially replicated from \cite{britton2022}.
-\end{footnotesize}
-
-\import{../../output/tables/}{britton_table2_DiD_control_experiment.tex}
-\begin{footnotesize}
-  \noindent Note: Estimates are weighted using CPS October supplement weights.
-Robust standard errors are clustered at the state level.
-Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income.
-The sample is defined as black and white males aged 30-50 in 1986 who were not incarcerated at the time of the survey.
-  This table is a control experiment for table 2 in \cite{britton2022}.
-\end{footnotesize}
-\clearpage
-
-\import{../../output/tables/}{britton_table3_DiD.tex}
-\begin{footnotesize}
-  \noindent Note: Estimates are weighted using CPS October supplement weights.
-Robust standard errors are clustered at the state level.
-Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income.
-The sample is defined as black males and black females aged 18-24 in 1986 who were not incarcerated at the time of the survey.
-  This table is partially replicated from \cite{britton2022}.
-\end{footnotesize}
-
-\import{../../output/tables/}{britton_table3_DiD_control_experiment.tex}
-\begin{footnotesize}
-  \noindent Note: Estimates are weighted using CPS October supplement weights.
-Robust standard errors are clustered at the state level.
-Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income.
-The sample is defined as black males and black females aged 30-50 in 1986 who were not incarcerated at the time of the survey.
-  This table is a control experiment for table 3 in \cite{britton2022}.
-\end{footnotesize}
-\clearpage
-
-\import{../../output/tables/}{fair_sentencing_DiD_t1.tex}
-\begin{footnotesize}
-  \noindent Note: Estimates are weighted using CPS October supplement weights.
-Robust standard errors are clustered at the state level.
-Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income.
-The sample is defined as black and white males aged 18-24 in 2010 who were not incarcerated at the time of the survey.
-\end{footnotesize}
-
-\import{../../output/tables/}{fair_sentencing_DiD_t1_control_experiment.tex}
-\begin{footnotesize}
-  \noindent Note: Estimates are weighted using CPS October supplement weights.
-Robust standard errors are clustered at the state level.
-Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income.
-The sample is defined as black and white males aged 30-50 in 2010 who were not incarcerated at the time of the survey.
-\end{footnotesize}
-\clearpage
-
-\import{../../output/tables/}{fair_sentencing_DiD_t2.tex}
-\begin{footnotesize}
-  \noindent Note: Estimates are weighted using CPS October supplement weights.
-Robust standard errors are clustered at the state level.
-Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income.
-The sample is defined as black males and females aged 18-24 in 2010 who were not incarcerated at the time of the survey.
-\end{footnotesize}
-
-\import{../../output/tables/}{fair_sentencing_DiD_t2_control_experiment.tex}
-\begin{footnotesize}
-  \noindent Note: Estimates are weighted using CPS October supplement weights.
-Robust standard errors are clustered at the state level.
-Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income.
-The sample is defined as black males and females aged 30-50 in 2010 who were not incarcerated at the time of the survey.
-\end{footnotesize}
-\clearpage
-
-\import{../../output/tables/}{DiD_1986_high_low.tex}
-\begin{footnotesize}
-  \noindent Note: Treated observations are defined as those living in states with a high-drug arrest rate for black adults, where high black adult drug arrest states are defined to be those above the 75th percentile in 1984.
-Estimates are weighted using CPS October supplement weights.
-Robust standard errors are clustered at the state level.
-Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income.
+The controls used include age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income.
 The sample is defined as males aged 18-24 in 1986 who were not incarcerated at the time of the survey.
@@
 \begin{footnotesize}
-  \noindent Note: Treatment is continuous.
-Estimates are weighted using CPS October supplement weights.
+  \noindent Note: Estimates are weighted using CPS October supplement weights.
 Robust standard errors are clustered at the state level.
@@
 \begin{footnotesize}
-  \noindent Note: Treated observations are defined as those living in states with a high-drug arrest rate for black juveniles, where high black juvenile drug arrest states are defined to be those above the 75th percentile in 1984.
-Estimates are weighted using CPS October supplement weights.
+  \noindent Note: Estimates are weighted using CPS October supplement weights.
 Robust standard errors are clustered at the state level.
-Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income.
+The controls used include age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income.
 The sample is defined as males aged 18-24 in 1986 who were not incarcerated at the time of the survey.
 \end{footnotesize}
+
 \import{../../output/tables/}{DiD_1986_high_low_jb_cont.tex}
@@
 \import{../../output/tables/}{DiD_1986_high_low_jb_cont_control_experiment_female.tex}
+
 \import{../../output/tables/}{DiD_1986_high_low_jb_cont_control_experiment_old.tex}
@@
 
+% Britton Table 2
+\import{../../output/tables/}{britton_table2_DiD.tex}
+\begin{footnotesize}
+  \noindent Note: Estimates are weighted using CPS October supplement weights.
+Robust standard errors are clustered at the state level.
+The controls used include age, age-squared, Latino ethnicity, and binned family income.
+The sample is defined as Black and White males aged 18-24 in 1986 who were not incarcerated at the time of the survey.
+  This table is partially replicated from \cite{britton2022}.
+\end{footnotesize}
+
+\import{../../output/tables/}{britton_table3_DiD.tex}
+\begin{footnotesize}
+  \noindent Note: Estimates are weighted using CPS October supplement weights.
+Robust standard errors are clustered at the state level.
+The controls used include age, age-squared, Latino ethnicity, and binned family income.
+The sample is defined as Black males and Black females aged 18-24 in 1986 who were not incarcerated at the time of the survey.
+This table is partially replicated from \cite{britton2022}.
+\end{footnotesize}
+
+\clearpage
+
+\import{../../output/tables/}{britton_table2_DiD_control_experiment.tex}
+\begin{footnotesize}
+  \noindent Note: Estimates are weighted using CPS October supplement weights.
+Robust standard errors are clustered at the state level.
+The controls used include age, age-squared, Latino ethnicity, and binned family income.
+The sample is defined as Black and White males aged 30-50 in 1986 who were not incarcerated at the time of the survey.
+  This table is a control experiment for table 2 in \cite{britton2022}.
+\end{footnotesize}
+
+\import{../../output/tables/}{britton_table3_DiD_control_experiment.tex}
+\begin{footnotesize}
+  \noindent Note: Estimates are weighted using CPS October supplement weights.
+Robust standard errors are clustered at the state level.
+The controls used include age, age-squared, Latino ethnicity, and binned family income.
+The sample is defined as Black males and Black females aged 30-50 in 1986 who were not incarcerated at the time of the survey.
+  This table is a control experiment for table 3 in \cite{britton2022}.
+\end{footnotesize}
+\clearpage
+
+\import{../../output/tables/}{fair_sentencing_DiD_t1.tex}
+\begin{footnotesize}
+  \noindent Note: Estimates are weighted using CPS October supplement weights.
+Robust standard errors are clustered at the state level.
+The controls used include age, age-squared, Latino ethnicity, and binned family income.
+The sample is defined as Black and White males aged 18-24 in 2010 who were not incarcerated at the time of the survey.
+\end{footnotesize}
+
+\import{../../output/tables/}{fair_sentencing_DiD_t2.tex}
+\begin{footnotesize}
+  \noindent Note: Estimates are weighted using CPS October supplement weights.
+Robust standard errors are clustered at the state level.
+The controls used include age, age-squared, Latino ethnicity, and binned family income.
+The sample is defined as Black males and females aged 18-24 in 2010 who were not incarcerated at the time of the survey.
+\end{footnotesize}
+
+\import{../../output/tables/}{fair_sentencing_DiD_t1_control_experiment.tex}
+\begin{footnotesize}
+  \noindent Note: Estimates are weighted using CPS October supplement weights.
+Robust standard errors are clustered at the state level.
+The controls used include age, age-squared, Latino ethnicity, and binned family income.
+The sample is defined as Black and White males aged 30-50 in 2010 who were not incarcerated at the time of the survey.
+\end{footnotesize}
+
+\import{../../output/tables/}{fair_sentencing_DiD_t2_control_experiment.tex}
+\begin{footnotesize}
+  \noindent Note: Estimates are weighted using CPS October supplement weights.
+Robust standard errors are clustered at the state level.
+The controls used include age, age-squared, Latino ethnicity, and binned family income.
+The sample is defined as Black males and females aged 30-50 in 2010 who were not incarcerated at the time of the survey.
+\end{footnotesize}
+\clearpage
+
 \import{../../output/tables/ddd}{ddd_1986_ab.tex}
@@
 
-\import*{../../output/tables/ddd}{ddd_1986_jb.tex}
+\import{../../output/tables/ddd}{ddd_1986_jb.tex}
 
@@
 
-\import*{../../output/tables/ddd}{ddd_2010_ab.tex}
+\import{../../output/tables/ddd}{ddd_2010_ab.tex}
 
@@
 
-\import*{../../output/tables/ddd}{ddd_2010_jb.tex}
-
-\import{../../output/tables}{ddiv_show.tex}
+\import{../../output/tables/ddd}{ddd_2010_jb.tex}
+\clearpage

### 2023-04-19 source/figures/power/firststage_ab1986.r

@@ -17,6 +17,13 @@ slope50 <-
                   referencePeriod = referencePeriod)
 slope50
 
+quadraticPretrend <-
+  pretrends(betahat = beta, 
+            sigma = sigma, 
+            tVec = tVec, 
+            referencePeriod = referencePeriod,
+            deltatrue = 0.2 * (tVec - referencePeriod)^2)
+
 pretrendsResults <- 
   pretrends(betahat = beta, 
             sigma = sigma, 

### 2023-04-20 source/paper/appendix_figures.tex
Just in case again...

@@
   \begin{footnotesize}
-    \noindent Note: footnote TO BE UPDATED
+    \noindent Note: This figure reports coefficients from the estimation of equation \ref{eq:state_level_es} evaluating the impact of the Anti-Drug Abuse Act of 1986 on arrest rates per 100,000 related to drug violations using CPS and UCR data from 1982-1992.
+Event time $0 \coloneqq 1986$.
+The coefficients represent the change in outcomes for high-drug arrest states relative to non-high-drug arrest states, where high black adult drug arrest states are defined to be those above the 75th percentile in 1984.
+The sample is defined as black males aged 18-24 in 1986 who were not incarcerated at the time of the survey.
+Control variables include population and unemployment rates at the state-year level.
+Right tail arrest rate outliers were winsorized at the 95\% level.
   \end{footnotesize}

### 2023-04-20 source/paper/figures.tex
Just in case again...

@@
-   % Arrest rate pretrends
+   % Arrest rate pre-trends
 
@@
 
-  % High vs low arrest states pretrends
+  % High vs low arrest states pre-trends
 
@@
     \centering
-    \caption{Additional Pretrend Testing for Coefficients from Figure 7}%
-    \subfloat[\centering Linear pretrend]{{\includegraphics[width=7cm]{pretrends/power/firststage_linear_ab1986.png} }}%
+    \caption{Additional Pre-trend Testing for Coefficients from Figure 7}%
+    \subfloat[\centering Linear pre-trend]{{\includegraphics[width=7cm]{pretrends/power/firststage_linear_ab1986.png} }}%
     \qquad
-    \subfloat[\centering Quadratic pretrend]{{\includegraphics[width=7cm]{pretrends/power/firststage_quad_ab1986.png} }}%
-    \label{fig:pretrends_roth}%
+    \subfloat[\centering Quadratic pre-trend]{{\includegraphics[width=7cm]{pretrends/power/firststage_quad_ab1986.png} }}%
+    \label{fig:pre-trends_roth}%
   \end{figure}
@@
   \begin{footnotesize}
-    \noindent Note: These two figures were constructed using an R package written by \cite{roth2022}.
-The figures and pretrend statistics were calculated using the estimated coefficients from Figure 7 and their corresponding covariance matrixes.
+    \noindent Note: These two figures were constructed using an R package written by Roth (2022).
+The figures and pre-trend statistics were calculated using the estimated coefficients from Figure 7 and their corresponding covariance matrixes.
 The slope in Figure A was constructed such that the power would be about 0.5, while the quadratic trend in Figure B was chosen visually.
+The blue expectation after pretesting coefficients represents the expected value of the coefficients conditional on passing the pre-test under the hypothesized trend.
 
@@
   \centering
-  \caption{Effect of Fair Sentencing Act on the College Enrollment Rate of Adult Black Men, Comparing High and Low-Intensity States}%
+  \caption{Effect of Anti-Drug Abuse Act on the College Enrollment Rate of Adult Black Men, Comparing High and Low-Intensity States}%
   \subfloat[\centering Using adults arrests]{{\includegraphics[width=7cm]{eventstudy/high_drug_use/reducedform_ab1986.png} }}%
@@
   \caption{Effect of Fair Sentencing Act on the College Enrollment Rate of Adult Black Men, Comparing High and Low-Intensity States}%
-  \subfloat[\centering Using adults arrests]{{\includegraphics[width=7cm]{eventstudy/high_drug_use/reducedform_ab1986.png} }}%
+  \subfloat[\centering Using adults arrests]{{\includegraphics[width=7cm]{eventstudy/high_drug_use/reducedform_ab2010.png} }}%
   \qquad

### 2023-04-20 source/paper/main.tex
Just in case again...

@@
     \href{mailto:ray_huang@brown.edu}{ray\_huang@brown.edu}.
-     I am grateful to Peter Hull at Brown University for serving as my advisor and for providing me with fantastic feedback and guidance.
+     I am grateful to Peter Hull for serving as my advisor and for providing me with fantastic feedback and guidance.
 I would also like to thank Alison Lodermeier and Francesco Ferlenga for their generous comments and support.
@@
 High-intensity states are defined as states with Black adult drug-related arrest rates above the 75th percentile two years before the passage of the federal drug act (e.g.
-for the Anti-Drug Abuse Act, 1984 was used.) I compare high-intensity states to low-intensity states, and I calculate both the first stage and reduced form estimates where the first stage is the impact of the act on Black adult drug-related arrest rates and the reduced form is the impact of the act on college enrollment.
+for the Anti-Drug Abuse Act, 1984 was used).
+When examining Figure \ref{fig:raw_ab}a, it seems like the rise in arrest rates in high-intensity states started increasing at a faster pace.
+I compare high-intensity states to low-intensity states, and I calculate both the first stage and reduced form estimates where the first stage is the impact of the act on Black adult drug-related arrest rates and the reduced form is the impact of the act on college enrollment.
 For additional supplemental analysis, I adapt the second and third research designs in \cite{britton2022} to estimate the impact of the federal drug acts on college enrollment at the individual level.
@@
 
-I find that the Anti-Drug Abuse Act of 1986 had a modest impact on Black adult male arrest rates and a small negative impact on college enrollment.
-In addition, I find some evidence that an increase in Black adult drug-related arrest rates has a small negative impact on college enrollment rates.
-The Fair Sentencing Act of 2010 is harder to study due to substantial pretrends, and I find some evidence of a potentially positive impact on college enrollment for Black males.
-For my estimates to be considered causal, important pretrend and exclusion restrictions must be satisfied.
+I find evidence that the Anti-Drug Abuse Act of 1986 had a modest impact on Black adult male arrest rates and a small negative impact on college enrollment.
+In addition, I find some evidence that an increase in Black adult drug-related arrest rates has a small negative impact on college enrollment.
+The Fair Sentencing Act of 2010 is harder to study due to substantial pre-trends \footnote{When looking Figure \ref{fig:raw_ab}b, there does not seem to be a change in arrest rates after the passage of the Fair Sentencing Act, suggesting that any results may be driven by pre-trends.
+I will formalize this finding in the results section.}, but I find some evidence of a potentially positive impact on college enrollment for Black males.
+For my estimates to be considered causal, important pre-trend and exclusion restrictions must be satisfied.
 
@@
 This paper heavily builds upon recent work by \cite{britton2022}, who estimates the impact of the Anti-Drug Abuse Act on college enrollment and the impact of state-level legislation on college enrollment.
-She finds that "Black males had a 2.2 percentage point decrease in the relative probability of college enrollment after the passage of the Anti-Drug Abuse Act of 1986." I build upon her work by introducing a new counterfactual group that allows the impact to be split into a first-stage and reduced-form.
-I also introduce more modern and robust methods to deal with the issue of pretrends, and I spend some time replicating her results.
+She finds that "Black males had a 2.2 percentage point decrease in the relative probability of college enrollment after the passage of the Anti-Drug Abuse Act of 1986." I build upon her work by introducing a new counterfactual group that allows the impact to be split into a first stage and reduced form.
+I also introduce more modern and robust methods to deal with the issue of pre-trends, and I spend some time replicating her results.
 
@@
 See figure \ref{fig:heatmap} for a heatmap of high-intensity states in 1984.}.
-I primarily rely on data on adult arrests instead of juvenile arrests due to effect sizes and issues with pretrends \footnote{As discussed in the introduction, \cite{aizer} finds that juvenile incarceration has a larger impact on education than adult incarceration.
+I primarily rely on data on adult arrests instead of juvenile arrests due to effect sizes and issues with pre-trends \footnote{As discussed in the introduction, \cite{aizer} finds that juvenile incarceration has a larger impact on education than adult incarceration.
 However, since states with high adult arrests tend to have high juvenile arrest rates, my estimates are robust to which arrest rate is used.}.
-I examine the first-stage impact where the outcome is the change in drug-related arrest rates and the reduced-form impact where the outcome is college-enrollment.
+I examine the first stage impact where the outcome is the change in drug-related arrest rates and the reduced form impact where the outcome is college-enrollment.
 The first stage is evaluated using an event-study model that allows me to assess the evolution of relative outcomes while controlling for fixed differences across states and national trends over time.
@@
 Similarly, since the Fair Sentencing Act of 2010 was passed in August, I normalize the $\beta$ on 2010 to be zero.}.
-When testing for pre-trends, if the first-stage arrest rates are trending similarly before the passage of the Anti-Drug Abuse Act of 1986 and the Fair Sentencing Act of 2010, I expect the coefficients associated with pre-periods to be small and statistically insignificant.
+In each event-study plot I also include the difference between the average of the post-period and pre-period coefficients; to account for potential pre-trends, I also report the average of the post-period coefficients, which is equivalent to the average treatment effect on the treated (ATT).
+When testing for pre-trends, if the first stage arrest rates are trending similarly before the passage of the Anti-Drug Abuse Act of 1986 and the Fair Sentencing Act of 2010, I expect the coefficients associated with pre-periods to be small and statistically insignificant.
 
@@
 To address issues of low power associated with event study tests for pre-trends in both the first stage and reduced form regressions, I implemented suggestions from \cite{roth2022}, which include calculating the slope of a linear violation of parallel trends that a pre-trends test would detect a specified fraction of the time, the expected value of the coefficients conditional on passing the pre-test under the hypothesized trend, and useful statistics such as power, Bayes Factor, and likelihood ratio.
+If the parallel trends assumption is satisfied, then my first stage and reduced form estimates would identify the average treatment effect on the treated.
 
-Overall, examining both the first-stage and reduced-form impact of the federal has the advantage of enabling me to estimate the impact of arrest rates on college enrollment for Black males.
+Overall, examining both the first stage and reduced form impact of the federal has the advantage of enabling me to estimate the impact of arrest rates on college enrollment for Black males.
 I conduct an instrumented difference-in-differences (DDIV) estimate where the endogenous variable is arrest rates and the instrument is an indicator for living in a high-intensity state.
@@
 
-Finally, I also include a triple difference-differences specification, where the first difference is pre and post-time periods, the second difference is race, and the third difference is living in a high or low-Black drug arrest state.
-The identifying assumption for the triple difference is
+Finally, for supplemental analysis, I also include a triple difference-differences specification in the appendix, where the first difference is pre and post-time periods, the second difference is race, and the third difference is living in a high or low-Black drug arrest state.
+If White men have a similar first stage pre-trend to Black males in high vs low-intensity states, the triple difference-difference specification will remove that bias from that specific pre-trend.
 
@@
 In all the regression specifications, I estimate the equation using ordinary least squares (OLS).
-I also follow the recommendations outlined in \cite{duflo_did} and report heteroskedasticity-robust standard errors that are clustered at the state level.
+I also follow the recommendations outlined in \cite{duflo_did} and calculate heteroskedasticity-robust standard errors that are clustered at the state level.
 All analyses use CPS October supplement final person weights and limit the sample to Black males aged 18-24 at the time of the passage of the federal act.
@@
 
-It is important to note that the UCR data has several limitations.
+It is important to note that the UCR data has several substantial limitations.
 First and foremost, many counties failed to report their arrest rates for certain years.
@@
 This is likely to bias our estimates downwards, as Florida has high rates of drug use and sales \footnote{Florida is the epicenter of the recent prescription drug epidemic in the United States \citep{lee}, and most Colombian cocaine was initially transported to the United States through the Caribbean and Florida \citep{williams}.}.
-What does the criminology literature have to say on the matter?
-\cite{gove} conclude that the personal characteristics of the offender have minor effects on whether the crime is reported and that the UCR is a valid indicator for serious crimes.
+In the criminology literature, \cite{gove} conclude that the personal characteristics of the offender have minor effects on whether the crime is reported and that the UCR is a valid indicator for serious crimes.
 \cite{lynch} conclude that "missing data are substantial in the UCR program and certainly worthy of attention.
@@
 For example, the 99th percentile was 142 arrests in a certain state year, but the outlier would have over 1000 arrests.
-To deal with these extreme outliers (which are very likely to be erroneous), I implement a 95\% right tail winsorization \footnote{I use winsorization over trimming because it is likely the case that the outliers still belong to the distribution.}.
+To deal with these extreme outliers (which are very likely to be erroneous), I implement a 95\% right tail winsorization \footnote{I use winsorization over trimming since it is likely the case that the outliers still belong to the distribution.}.
 
@@
 
-Tables 1 and 2 report sample means separately for the pre and post-periods of both the Anti-Drug Abuse Act of 1986 and the Fair Sentencing Act of 2010.
+Tables 1 and A1 (in the appendix) report sample means separately for the pre and post-periods of both the Anti-Drug Abuse Act of 1986 and the Fair Sentencing Act of 2010.
 Table 1 uses the CPS-UCR linked dataset (which drops unmerged observations), while Table 2 uses the CPS dataset only.
-Comparing Table 1 to Table 2 provides a rough test for evaluating whether the states with missing UCR data certain years in are substantially different from the state without missing data.
+
+Comparing Table 1 to Table A1 provides a rough test for evaluating whether the states with missing UCR data certain years in are substantially different from the state without missing data.
 The number of observations is slightly smaller in the CPS-UCR merged dataset, except for the 2010-2016 period which is much smaller (likely due to the missing UCR data from Florida).
@@
 
-Looking at Table 1, in all periods, about 15\% of the sample is Black.
+In Table 1, in all periods, about 15\% of the sample is Black.
+The total proportion of males enrolled in college fluctuates heavily, but the proportion of Black males enrolled in college is more stable, as most of the fluctuations in total male college enrollment are driven by non-Black males.
+Overall, my summary statistics in Table 1 and A1 are similar to the one presented in \cite{britton2022}, but there remain minor differences.
 
-Overall, my summary statistics table is similar to the one presented in \cite{britton2022}, but there are some minor differences.
+In figure \ref{fig:heatmap} I presented a heatmap of Black adult drug-related arrests in 1984, two years before the passage of the Anti-Drug Abuse Act.
+I also present kernel density estimates of the distribution of arrest rates at the state level in figure \ref{fig:density_jb} with a vertical line denoting high-intensity states.
 
@@
 
+In the first subsection, I first evaluate the impact of the Anti-Drug Abuse Act of 1986, broken down into the first stage, reduced form, and second stage.
+In the next subsection, I discuss the Fair Sentencing Act of 2010.
+
+For important event-study figures, I include tables in the appendix with all the coefficients of interest.
+
 \subsection{Anti-Drug Abuse Act of 1986}
-
-In this section, I evaluate the impact of the Anti-Drug Abuse Act of 1986. In the next section, I discuss the Fair Sentencing Act of 2010.
 
@@
 
-The results are presented in figure \ref{fig:ab_es_1986}, figure \ref{fig:jb_es_1986}, and table (XYZ).
+The first stage results are presented in figures \ref{fig:ab_es_1986}, \ref{fig:ab_es_1986_nofe}, \ref{fig:jb_es_1986}, table 2, and table A2 in the appendix.
 
-For Black adults, using the event study model detailed in \ref{eq:state_level_es}, I find an increase in drug-related arrest rate associated with the Anti-Drug Abuse Act with gains between 3.08 and 12.71 arrests per 100,000 during each post-expansion year.
-Using the difference-in-difference model specified in \ref{eq:did}, I find a statistically significant increase of 45.13 arrests per 100,000.
-The estimates for years 2 and 3 after the expansion are larger than the estimates for years 1 and 4, indicating that the effect of the law took some time to "kick in", and the effect potentially decreased in later years.
+For Black adults, using the event study model detailed in equation \ref{eq:state_level_es}, I find an increase in drug-related arrest rate associated with the Anti-Drug Abuse Act with gains between 3.08 and 12.71 arrests per 100,000 during each post-expansion year.
+When using the event-study model specified in equation \ref{eq:state_level_es}, I find that the average between the post and pre-period coefficients is 2.96, and the ATT is a bit larger at 3.85 arrests with a similar standard error.
+The estimates for years 2 and 3 in the post-period are larger than the estimates for years 1 and 4, 5, and 6, indicating that the effect of the law took some time to "kick in", and the effect potentially decreased in the later years \footnote{I confirmed that the large standard errors in certain post-periods were not due to coding errors by regressing the outcome in said year minus outcome in year zero on the treatment group.}.
+If I omit fixed effects from the event-study model (in Figure \ref{fig:ab_es_1986_nofe}), the event-study model estimates a larger and statistically significant effect, where the difference between the post and pre-periods is 7.1 with a robust, clustered standard error of 2.5.
+Similarly when using the difference-in-difference model specified in equation \ref{eq:did}, I find a statistically insignificant increase of approximately 3.3 arrests per 100,000.
 
-To check for pretrends, in my event study model, I test the joint null hypothesis that all of the pretreatment event study coefficients are zero through an F-test, which I report at the bottom of each event study figure.
-In this case, in figure \ref{fig:ab_es_1986}, I get a $p$-value of 0.50, which increases my confidence in the parallel trends assumption.
-I additionally included plots of raw outcomes over time in figure  \ref{fig:raw_college_highlowab_1986}.
-As an additional robustness check, I implement suggestions from \cite{roth2022} in figure \ref{fig:pretrends_roth} \footnote{Using Roth's R package "pretrends", I calculate statistics about the power of the pre-test against the hypothesized trend.
-I calculate the power defined as the probability that I would find a significant pretrend under the hypothesized pretrend, the Bayes Factor defined as the ratio of the probability of failing to reject the pretest under the hypothesized trend relative to under parallel trends, and the likelihood ratio which is defined to be the ratio of the likelihood of the observed coefficients under the hypothesized trend relative to under parallel trends.}.
-Overall, the results imply that if there exists a pretrend, a quadratic pretrends is more worrying than the linear pretrend, as I have less power to detect a significant pretrend and the likelihood ratio is much higher.
+To check for pre-trends in my event study model, I test the joint null hypothesis that all of the pretreatment event study coefficients are zero through an F-test, which I report at the bottom of each event study figure.
+In this case, in figure \ref{fig:ab_es_1986}, I get a $p$-value of 0.27, which increases my confidence in the parallel trends assumption.
+I additionally included plots of raw outcomes over time in Figure \ref{fig:raw_college_highlowab_1986}.
+As an additional robustness check, I implement suggestions from \cite{roth2022} in figure \ref{fig:pre-trends_roth} \footnote{Using Roth's R package "pre-trends", I calculate the power defined as the probability that I would find a significant pre-trend under the hypothesized pre-trend, the Bayes Factor defined as the ratio of the probability of failing to reject the pretest under the hypothesized trend relative to under parallel trends, and the likelihood ratio which is defined to be the ratio of the likelihood of the observed coefficients under the hypothesized trend relative to under parallel trends.}.
+The results from Roth's pre-trend package imply that if there exists a pre-trend, a quadratic pre-trends is more worrying than the linear pre-trend, as I have less power to detect a significant pre-trend and the likelihood ratio is much higher.
+Notably, if there exists a pre-trend, figure \ref{fig:ab_es_1986} suggests that the pre-trend is possibly negative, which would imply that my first stage estimates are biased downwards.
 
@@
 
-\subsubsection{Reduced Form Estimates}
+\subsubsection{Reduced Form Estimates from High vs Low-Intensity States}
 
-The results are presented in figure \ref{fig:reducedform_ab}, figure \ref{fig:reducedform_jb}, and table (XYZ).
+The results from comparing high to low-intensity states are presented in figure \ref{fig:rs_es_1986} and tables 4 and 5.
 
-Notably, in Table 2 when examining a simple difference in means, the difference in college enrollment rates between pre and post-period for high and low-intensity states for Black adult drug-related arrests is -2.3\%, which matches the result in \cite{britton2022}
+In figure \ref{fig:rs_es_1986}, I find that there is likely a pre-trend, as I calculate an f-statistic of 0.035.
+However, the pre-trend appears to be in the opposite direction of the effect, implying that if there existed a pre-trend, my model would underestimate the effect of the Anti-Drug Abuse Act on college enrollment, i.e.
+my estimate would be biased upwards.
+I calculate that the average between the post and pre-period coefficients is -0.0004, and the ATT is -0.02 which is equivalent to a 2\% decrease in the probability of enrollment, matching the estimate in \cite{britton2022}.
+Similar to the first stage, I find that the effect size increases at first in years 1, 2, and 3, then the effect stops increasing around year 4.
+Overall, I find my estimates reduced form estimates are quite noisy.
+
+I also present simple difference-in-difference estimates of the treatment effect in tables 4 and 5.
+To increase power, I also calculated the same regression model, except I used continuous treatment (arrest rates) instead.
+My difference-in-difference estimates are consistent with the event-study results, as most are small, negative, and statistically insignificant.
 
@@
 
-The second stage DDIV results are presented in Table 3.
-Overall, I find a small negative effect of arrest rates on college enrollment in all three 2SLS specifications; however, the coefficients are small and statistically insignificant with large standard errors.
-If I scale the variables up, my estimate (with fixed effects and control variables) implies that if the arrest rate increased by 1000 Black Adult drug-related arrests per 100,000, then the college enrollment rate would decline by approximately 2.5 persons.
+In table 2, I present a simple table of means without any controls or fixed effects to consolidate the results from the first stage and reduced form models.
+Notably, in table 2, when examining a simple difference in means, the difference in college enrollment probability between pre and post-period for high and low-intensity states for Black adult drug-related arrests is -2.3\%, which matches the result in \cite{britton2022} The instrumented difference in difference estimate from this table is equivalent the ratio between the reduced form and first stage, which is -0.2326/3.332 = -0.0698 = -6.9\%.
 
-To test for the weak-instrument problem, I also report F-statistics from the first-stage regression, following conventional advice from \cite{staiger1997precise}.
-In my case, I find an F-statistic ranging from 15.9 to 20.2, providing evidence that my estimates are not biased by the weak-instrument problem.
+The more robust second stage DDIV results are estimated via 2SLS and are presented in table 3.
+Overall, I find a small negative effect of arrest rates on college enrollment in all three specifications; however, the coefficients are small and statistically insignificant with large standard errors.
+Notably, my 2SLS estimates are at least 10 times the magnitude of the OLS estimate (presented in column 1).
+If I scale the variables up, my most robust estimate (with fixed effects and control variables) implies that if the arrest rate increased by 1000 Black Adult drug-related arrests per 100,000, then the probability of college enrollment for a Black male would decline by approximately 2.5\%, once again, matching the estimate found in \cite{britton2022}.
+
+To test for the weak-instrument problem, I also report F-statistics from the first stage regression, following conventional advice from \cite{staiger1997precise}.
+In my case, I find an F-statistic ranging from 15.9 to 20.2, providing evidence that my estimates are likely not biased by the weak-instrument problem.
 
@@
 
-\subsubsection{Robustness Checks}
+The results from the second and third empirical strategies (following the approach in \cite{britton2022}) are presented in tables 10 and 11.
+My estimates from using White males as a counterfactual group are similar to Britton's, except my estimates are a bit larger, with a decrease in the probability of college enrollment for Black males between 3.3\% and 5.7\%.
+When I use Black females as a counterfactual group, I find smaller, statistically insignificant estimates of approximately -1.6\%.
+To test for pre-trends, I plot the raw outcomes by treatment group overtime.
+These outcome figures can be found in the appendix.
 
@@
 
-Notably, any effect is likely not due to the mandatory sentencing minimum, but rather, is due to the overall lightening of sentences / prosecutions. \cite{ussc} found that
+Notably, any effect is likely not due to the mandatory sentencing minimum, but rather, is due to the overall lightening of sentences / prosecutions.
+\cite{ussc} found that in the years before the Fair Sentencing Act was passed, the proportion in prison with minimum sentencing requirements was in the single digits.
 
@@
 
-I find that the first empirical strategy leveraging variation between high and low-intensity states is not an appropriate research design for studying the impact of the Fair Sentencing Act of 2010 on drug-related arrest rates.
-The results of the event study regressions specified in equation \ref{eq:state_level_es} can be found in figures XYZ.
-The coefficients provide strong evidence of significant pretrends in arrest rates before the passage of the Fair Sentencing Act.
+I attempt first to estimate the impact of the Fair Sentencing Act on drug-related arrest rates for Black adults and Black juveniles separately by looking at changes in arrest rates in high-drug arrest intensity states relative to the low-drug arrest intensity states before and after 2010.
+I find that empirical strategy is not an appropriate research design for studying the impact of the Fair Sentencing Act of 2010 on drug-related arrest rates due to the failure of the parallel trends assumption.
+The results of the event study regressions specified in equation \ref{eq:state_level_es} can be found in figure \ref{fig:fs_es_2010}.
+The coefficients provide strong evidence of significant pre-trends in arrest rates before the passage of the Fair Sentencing Act, and the calculated f-statistics is essentially 0.
+
+In this case, the pre-trend is trending in the same direction as the measured effect.
+I.e.
+my estimated effect is likely larger than the true effect.
+Using adult arrests, I find that the difference between the post and pre-period coefficients is -20.8, while the ATT is -22.8.
 
@@
 
-\subsubsection{Robustness Checks}
+The results from comparing high to low-intensity states are presented in figure \ref{fig:rf_jb_es_2010} and tables A4 and A5 in the appendix.
+Similar to the first stage result, I find significant pre-trends trending in the same direction as the effect.
+I conclude that comparing high and low-intensity states is not an approach research design for measuring the reduced form impact of the Fair Sentencing Act on the probability of college enrollment.
+
+I next use White males as a counterfactual group to Black males, and the results are presented in table 14.
+
+\subsubsection{Second Stage Estimate}
+
+Due to significant pre-trends in both the first stage and reduced form estimates, I refrain from calculating a second stage estimate for the Fair Sentencing Act.
+
+\subsection{Robustness Checks} %update to reflect both 1986 and 2010
+
+I present numerous robustness checks.
+
+For the first empirical strategy, I leverage variation in Black juvenile arrests as a robustness check.
+I calculated both the first-stage and reduced form, and the results are presented in figures \ref{fig:jb_es_1986} and \ref{fig:rs_es_1986}.
+Overall, I find that the estimates are similar between the models using adult arrest and the models using juvenile arrests.
+Using juvenile results tends to lead to smaller estimates, but at the same time, the pre-trends are potentially worse.
+
+As a robustness check for the reduced form estimates from comparing high vs low-intensity states, I run the same regressions using Black juvenile arrests instead of Black adult arrests, and I present the results in tables 6 and 7.
+I also run two separate control experiments in tables 8 and 9.
+In table 8, I limit my sample to females exclusively, and in table 8, I use Black males aged 30-50 in 1986.
+In both cases, I find very small, insignificant results.
+
+For the second stage estimate, I include multiple regression specifications in table 3.
+My 2SLS estimates are somewhat robust to model specification; however, the effect size does increase when I add fixed effects and control variables.
+
+To check the robustness of my additional reduced form estimates from using White males and Black females as counterfactual groups, I estimate the same model while restricting the sample to Males aged 30-50 in tables 12 and 13
 
@@
 
-estimates are downards biased -cps and ucr missing key data
+It is important to summarize and acknowledge several important issues this study faces.
+
+First, many assumptions must be satisfied for the estimates presented in this paper to be interpreted as causal.
+For the first stage and reduced form estimates, the parallel trends assumption must be satisfied.
+For the instrumented difference in differences estimate to be causal, the exclusion restriction must be satisfied.
+While I include many checks for these assumptions, some more convincing than others, certain assumptions may still be invalid.
+In particular, I found that the Fair Sentencing Act was especially difficult to study due to failed parallel trend assumptions.
+
+On the data side, the poor quality of the UCR program's arrest data may bias my estimates.
+Many counties failed to report arrest data, and it's highly unlikely that counties randomly failed to report data.
+Furthermore, since the population impacted by these Acts is so small, the CPS dataset may not be sufficiently powered to answer the research questions presented in this paper.
+
+Finally, it may be the case that the subpopulation impacted by these Acts would not have attended college with or without the treatment.
+In other words, the local average treatment effect might have been 0, and in many instances, my estimates are very close to 0.
+However, it is unclear whether my estimates are small due to insufficient power and noise or the true local average treatment effect being 0.
 
@@
 \cite{britton2022} uses differences in marijuana laws, and future research can leverage other drug laws while introducing modern methods such as synthetic control designs.
-synthetic control methods, etc
+
 other datasets e.g. ACA
@@
 
-\begin{appendices}
+\clearpage
+\appendix
+\section*{Appendix}
+\beginsupplement
+
   \section{Data}
@@
   \section{First stage arrest rate estimates}
-  I include tables for the equation \ref{eq:state_level_es} estimates presented in figures XYZ.
+  I include a table (A2) for the equation \ref{eq:state_level_es} estimates presented in figure \ref{fig:ab_es_1986}.
 
@@
   \section{Reduced form college enrollment estimates}
-  I include tables for the equation \ref{eq:state_level_es} estimates presented in figures XYZ.
+  I include a table (A3) for the equation \ref{eq:state_level_es} estimates presented in figure \ref{fig:rs_es_1986}.
+
+  Although it is likely the case that my estimates of the impact of the Fair Sentencing Act of 2010 using high vs low-intensity states is biased by significant pre-trends, in table A4 and A5 I include simple difference-in-difference estimates under three similar specifications; table A4 uses discrete treatment while table A5 uses continuous treatment.
+Overall my estimates imply a small negative effect on college enrollment probability, but my estimates are not sufficiently powered to be statistically significant.
+
+  In tables A6-A8, I include the triple difference-in-differences results.
+I use both adult and juvenile arrests for the Anti-Drug Abuse Act, but I omit the juvenile table from the Fair Sentencing Act analysis since the pre-trends assumption is already quite weak.
+Counter to my previous results, when using adult arrest rates in the 1986 Act, I find a significant, positive effect on college enrollment.
+However, the significance drops away when I switch to juvenile arrests as a robustness check.
+Since the bias needs to be the same in each difference-in-difference estimate, if the parallel trends assumption is not satisfied, the triple difference-in-difference estimators may be more biased than my normal estimates.
 
@@
 
-\end{appendices}
+  \clearpage
+
+  % Fair Sentencing Act High/low intensity
+
+  \import{../../output/tables/}{DiD_2010_high_low.tex}
+  \begin{footnotesize}
+    \noindent Note: Treated observations are defined as those living in states with a high-drug arrest rate for black adults, where high black adult drug arrest states are defined to be those above the 75th percentile in 2008.
+Estimates are weighted using CPS October supplement weights.
+Robust standard errors are clustered at the state level.
+Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income.
+The sample is defined as males aged 18-24 in 1986 who were not incarcerated at the time of the survey.
+  \end{footnotesize}
+
+  \import{../../output/tables/}{DiD_2010_high_low_cont.tex}
+  \begin{footnotesize}
+    \noindent Note: Estimates are weighted using CPS October supplement weights.
+Robust standard errors are clustered at the state level.
+Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income.
+The sample is defined as males aged 18-24 in 2010 who were not incarcerated at the time of the survey.
+  \end{footnotesize}
+  \clearpage
+
+  \import{../../output/tables/ddd}{ddd_1986_ab.tex}
+\begin{footnotesize}
+  \noindent Note: Column 4 is from a regression where all the covariates excluding the triple-interaction term and the controls are included as fixed effects.
+Estimates are weighted using CPS October supplement weights.
+Robust standard errors are clustered at the state level.
+The controls used include age, age-squared, Latino ethnicity, and binned family income.
+The sample is defined as males aged 18-24 in 1986 who were not incarcerated at the time of the survey.
+\end{footnotesize}
+\clearpage
+
+\import{../../output/tables/ddd}{ddd_1986_jb.tex}
+\begin{footnotesize}
+  \noindent Note: Column 4 is from a regression where all the covariates excluding the triple-interaction term and the controls are included as fixed effects.
+Estimates are weighted using CPS October supplement weights.
+Robust standard errors are clustered at the state level.
+The controls used include age, age-squared, Latino ethnicity, and binned family income.
+The sample is defined as males aged 18-24 in 1986 who were not incarcerated at the time of the survey.
+\end{footnotesize}
+
+\clearpage
+
+\import{../../output/tables/ddd}{ddd_2010_ab.tex}
+\begin{footnotesize}
+  \noindent Note: Column 4 is from a regression where all the covariates excluding the triple-interaction term and the controls are included as fixed effects.
+Estimates are weighted using CPS October supplement weights.
+Robust standard errors are clustered at the state level.
+The controls used include age, age-squared, Latino ethnicity, and binned family income.
+The sample is defined as males aged 18-24 in 2010 who were not incarcerated at the time of the survey.
+\end{footnotesize}
+
+\clearpage
 

### 2023-04-20 source/paper/tables.tex
Just in case again...

@@
 
-\import{../../output/tables/}{DiD_2010_high_low.tex}
-\begin{footnotesize}
-  \noindent Note: Treated observations are defined as those living in states with a high-drug arrest rate for black adults, where high black adult drug arrest states are defined to be those above the 75th percentile in 2008.
-Estimates are weighted using CPS October supplement weights.
-Robust standard errors are clustered at the state level.
-Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income.
-The sample is defined as males aged 18-24 in 1986 who were not incarcerated at the time of the survey.
-\end{footnotesize}
-
-\import{../../output/tables/}{DiD_2010_high_low_cont.tex}
-\begin{footnotesize}
-  \noindent Note: Treatment is continuous.
-Estimates are weighted using CPS October supplement weights.
-Robust standard errors are clustered at the state level.
-Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income.
-The sample is defined as males aged 18-24 in 2010 who were not incarcerated at the time of the survey.
-\end{footnotesize}
-\clearpage
-
 % Britton Table 2
@@
 \end{footnotesize}
+\clearpage
 
@@
 \clearpage
-
-\import{../../output/tables/ddd}{ddd_1986_ab.tex}
-\begin{footnotesize}
-  \noindent Note: CPS data from 1984-1992.
-  The sample is defined as males aged 18-24 in 1986 who were not incarcerated at the time of the survey.
-\end{footnotesize}
-
-\clearpage
-
-\import{../../output/tables/ddd}{ddd_1986_jb.tex}
-
-\clearpage
-
-\import{../../output/tables/ddd}{ddd_2010_ab.tex}
-
-\clearpage
-
-\import{../../output/tables/ddd}{ddd_2010_jb.tex}
-\clearpage

### 2023-04-21 source/paper/appendix_figures.tex
Update

@@
 
-  % 2010 pretrends
-
-  \begin{figure}[h]
-    \centering
-    \caption{College Enrollment Around 2010}%
-    \subfloat[\centering By race]{{\includegraphics[width=7cm]{pretrends/2010/college_enroll_byrace_2010.png} }}%
-    \qquad
-    \subfloat[\centering By sex]{{\includegraphics[width=7cm]{pretrends/2010/college_enroll_bysex_2010.png} }}%
-    \label{fig:raw_college_2010}%
-  \end{figure}
-
-  \begin{figure}[h]
-    \centering
-    \caption{Family Income Around 2010}%
-    \subfloat[\centering By race]{{\includegraphics[width=7cm]{pretrends/2010/faminc_byrace_2010.png} }}%
-    \qquad
-    \subfloat[\centering By sex]{{\includegraphics[width=7cm]{pretrends/2010/faminc_bysex_2010.png} }}%
-    \label{fig:raw_faminc_2010}%
-  \end{figure}
-
-  \begin{footnotesize}
-    \noindent Note: These figures report the outcomes for various subgroups plotted over time using CPS data from 2005-2016.
-Figure \ref{fig:raw_college_2010} reports the proportion enrolled in college, while figure \ref{fig:raw_faminc_2010} reports the average family income.
-A vertical line is drawn to denote the passage of the Fair Sentencing Act of 2010.
-The universe of samples is defined as participants aged 18-24 in 2010 who were not incarcerated at the time of the survey.
-  \end{footnotesize}
-
   \clearpage
@@
     \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_drug_eventstudy_1986_extended_years.png}
-    \label{fig:b1}
+    \label{fig:a3}
   \end{figure}

### 2023-04-21 source/paper/figures.tex
Update

@@
     \noindent Note: These two figures were constructed using an R package written by Roth (2022).
+Relative time 0 represents 1986.
 The figures and pre-trend statistics were calculated using the estimated coefficients from Figure 7 and their corresponding covariance matrixes.
@@
 \clearpage  
+% 2010 pretrends
+
+\begin{figure}[h]
+  \centering
+  \caption{College Enrollment Around 2010}%
+  \subfloat[\centering By race]{{\includegraphics[width=7cm]{pretrends/2010/college_enroll_byrace_2010.png} }}%
+  \qquad
+  \subfloat[\centering By sex]{{\includegraphics[width=7cm]{pretrends/2010/college_enroll_bysex_2010.png} }}%
+  \label{fig:raw_college_2010}%
+\end{figure}
+
+\begin{figure}[h]
+  \centering
+  \caption{Family Income Around 2010}%
+  \subfloat[\centering By race]{{\includegraphics[width=7cm]{pretrends/2010/faminc_byrace_2010.png} }}%
+  \qquad
+  \subfloat[\centering By sex]{{\includegraphics[width=7cm]{pretrends/2010/faminc_bysex_2010.png} }}%
+  \label{fig:raw_faminc_2010}%
+\end{figure}
+
+\begin{footnotesize}
+  \noindent Note: These figures report the outcomes for various subgroups plotted over time using CPS data from 2005-2016.
+Figure \ref{fig:raw_college_2010} reports the proportion enrolled in college, while figure \ref{fig:raw_faminc_2010} reports the average family income.
+A vertical line is drawn to denote the passage of the Fair Sentencing Act of 2010.
+The universe of samples is defined as participants aged 18-24 in 2010 who were not incarcerated at the time of the survey.
+\end{footnotesize}
+
+\clearpage

### 2023-04-21 source/paper/main.tex
Update

@@
 
-\title{Arrest Rates and College Enrollment:
+\title{Drug-Related Arrest Rates and College Enrollment:
 \texorpdfstring{\\}{} Examining the Impact of Two Federal Drug Control Acts}
@@
      I am grateful to Peter Hull for serving as my advisor and for providing me with fantastic feedback and guidance.
-I would also like to thank Alison Lodermeier and Francesco Ferlenga for their generous comments and support.
-A replication archive is available at https://github.com/rayhuang11/EconSeniorThesisRH.}
+This paper would not have been possible without his help.
+I would also like to thank Alison Lodermeier and Francesco Ferlenga for their very generous comments and support.
+A replication archive (forthcoming) is available at https://github.com/rayhuang11/fakelink.}
      \\Brown University, Honors Thesis}
@@
 \begin{abstract}
-\noindent I examine the impact of two federal drug acts on college enrollments and earnings among Black males by using a variety of counterfactual groups.
-The Anti-Drug Act of 1986 transformed the formerly rehabilitation-focused justice system into a punitive one, imposed sentencing minimums and disparities.
+\noindent I examine the impact of two federal drug acts on the drug-related arrest rate and the probability of college enrollment among Black males aged 18-24 by using a variety of counterfactual groups.
+The Anti-Drug Abuse Act of 1986 transformed the formerly rehabilitation-focused justice system into a punitive one, imposing sentencing minimums and increasing racial disparities.
 The Fair Sentencing Act of 2010 was intended to reverse some of these policies.
-I construct estimates of the impact of these two acts on the college enrollment of Black males aged 18-24 using three distinct counterfactual groups: 1) comparing states with high drug arrests to states with low drug arrests, 2) Black males to White males, and 3) Black males to Black females.
-I also evaluate the first stage impact of the two Acts on drug-related arrests.
-I find that
-
+I construct estimates of the impact of these two acts by comparing high-intensity to low-intensity drug-arrest states.
+I also use White males and Black females as two additional counterfactual groups.
+Although my estimates are quite noisy, I find that the Anti-Drug Abuse Act had a small, positive effect on arrest rates and resulted in an approximate 2\% decrease in the probability of college enrollment.
+The second-stage estimates imply that an increase in drug-related arrest rates has a small, negative impact on the probability of college enrollment for Black males.
+I find some evidence of differential pre-treatment trends in outcomes which makes the Fair Sentencing Act particularly difficult to analyze.
 \end{abstract}
@@
 \begin{quote}
-  There’s 2.2 million people in the American prison system, and half a million of those are locked up for drug offenses.
+  \textit{There’s 2.2 million people in the American prison system, and half a million of those are locked up for drug offenses.
 A lot of them were in the same boat as me: victims of the mandatory minimum.
 Passed by Congress in 1986, it’s the reason hundreds of thousands of nonviolent people, mostly black and brown people, are rotting in prison...
-I’d been in prison for ten years by the time my petition reached the Supreme Court.
-(HONY Interview)
+I’d been in prison for ten years by the time my petition reached the Supreme Court.}
+  \hspace*{\fill} (HONY Interview, 2022)
 \end{quote}
@@
 In 2010, the Fair Sentencing Act was passed, which aimed to undo many of the racial disparities potentially caused by the Anti-Drug Abuse Act.
-In this paper, I look to investigate the link between drug enforcement policies and educational outcomes, as I examine the impact of the Anti-Drug Abuse Act of 1986 and Fair Sentencing Act of 2010 on both drug-related arrest rates and college enrollment among Black males.
+In this paper, I investigate the link between drug enforcement policies and educational outcomes, as I examine the impact of the Anti-Drug Abuse Act of 1986 and Fair Sentencing Act of 2010 on both drug-related arrest rates and college enrollment among Black males.
 
@@
 This paper has two main objectives.
-First, I look to estimate the impact of the Anti-Drug Abuse Act of 1986 and the Fair Sentencing Act of 2010 on drug-related arrests.
+First, I investigate the impact of the Anti-Drug Abuse Act of 1986 and the Fair Sentencing Act of 2010 on drug-related arrests.
 The second objective is to evaluate the impact of the two acts on college enrollment rates for Black males.
@@
 When examining Figure \ref{fig:raw_ab}a, it seems like the rise in arrest rates in high-intensity states started increasing at a faster pace.
-I compare high-intensity states to low-intensity states, and I calculate both the first stage and reduced form estimates where the first stage is the impact of the act on Black adult drug-related arrest rates and the reduced form is the impact of the act on college enrollment.
+I compare high-intensity states to low-intensity states, and I calculate both the first-stage and reduced-form estimates where the first-stage is the impact of the act on Black adult drug-related arrest rates and the reduced-form is the impact of the act on college enrollment.
 For additional supplemental analysis, I adapt the second and third research designs in \cite{britton2022} to estimate the impact of the federal drug acts on college enrollment at the individual level.
@@
 
-I use repeated cross-sectional data from the Current Population Survey October education supplement for data at the individual level, and I limit my analysis to persons aged 18-24 at the time of the passage of the act.
-For data on arrests, I use data from the Uniform Crime Reporting Program, which contains information on the number of arrests by race, crime type, and juvenile crimes.
+I use repeated cross-sectional data from the Current Population Survey (CPS) October education supplement for data at the individual level, and I limit my analysis to persons aged 18-24 at the time of the passage of the act.
+For data on arrests, I use data from the Uniform Crime Reporting (UCR) Program, which contains information on the number of arrests by race, crime type, and juvenile crimes.
 To construct college enrollment rates from the CPS, I count any individual who is currently in their first year or has more than one year of college education \footnote{I count individuals with a master's or Ph.D.
@@
 This paper heavily builds upon recent work by \cite{britton2022}, who estimates the impact of the Anti-Drug Abuse Act on college enrollment and the impact of state-level legislation on college enrollment.
-She finds that "Black males had a 2.2 percentage point decrease in the relative probability of college enrollment after the passage of the Anti-Drug Abuse Act of 1986." I build upon her work by introducing a new counterfactual group that allows the impact to be split into a first stage and reduced form.
+She finds that "Black males had a 2.2 percentage point decrease in the relative probability of college enrollment after the passage of the Anti-Drug Abuse Act of 1986." I build upon her work by introducing a new counterfactual group that allows the impact to be split into a first-stage and reduced form.
 I also introduce more modern and robust methods to deal with the issue of pre-trends, and I spend some time replicating her results.
@@
 
-Some related prior literature includes \cite{aizer} which evaluates the relationship between juvenile incarceration and later life outcomes using a judge-IV research design.
+Some related prior literature includes \cite{aizer}, which evaluates the relationship between juvenile incarceration and later life outcomes using a judge-IV research design.
 They find that juvenile incarceration "results in large decreases in the likelihood of high school completion and large increases in the likelihood of adult incarceration." \cite{western} evaluates the impact of incarceration on labor market outcomes.
@@
 
-The rest of the paper is organized as such: in section 2 I summarize the history and known impacts of the Anti-Drug Abuse Act and Fair Sentencing Act.
-In section 3 I describe my empirical strategies, and in section 4 I discuss the data and its flaws.
+The rest of the paper is organized as such: in section 2, I summarize the history and known impacts of the Anti-Drug Abuse Act and Fair Sentencing Act.
+In section 3, I describe my empirical strategies, and in section 4, I discuss the data and its flaws.
 I present my results in section 5, and I close in section 6 with conclusions and implications.
@@
 The \cite{drug_control_money} estimated that drug control funding increased from \$2.9 billion in 1986 to \$4.8 billion in 1987.
-The Act has faced additional criticism as in recent years researchers such as \cite{bewley2005incarceration} have found that "there is little correlation between incarceration rates and drug use prevalence; and the impact of enforcement action on price is much less powerful than other market factors."
+The Act has faced additional criticism, as in recent years, researchers such as \cite{bewley2005incarceration} have found that "there is little correlation between incarceration rates and drug use prevalence; and the impact of enforcement action on price is much less powerful than other market factors."
 
-It is important to note that due to the War on Drugs, arrest rates and sentencing times were trending up even before the Anti-Drug Abuse Act of 1986.
+Due to the War on Drugs, arrest rates and sentencing times were trending up even before the Anti-Drug Abuse Act of 1986.
 \cite{bjs_1986} reported that from 1980 to 1986, the number of federal drug law violations that resulted in convictions increased by 134\% to a total of 12,285 convictions in 1986 \footnote{Federal convictions of all other types increased by 27\%.}.
-The BJS report also notes that average prison sentences for drug offenders increased by 33\% less than four years to over five years.
+The BLS report also notes that average prison sentences for drug offenders increased by 33\%, from less than four years to just over five years.
 
-The Fair Sentencing Act of 2010 was a piece of legislation enacted by the United States Congress to address the sentencing disparities between crack and powder cocaine offenses, which had been established by the Anti-Drug Abuse Act of 1986.
-The 2010 act aimed to reduce the disproportionate impact of drug laws on minority and low-income communities by amending the previously imposed 100-to-1 sentencing disparity.
+The Fair Sentencing Act of 2010 was a piece of legislation enacted by the United States Congress to address the sentencing disparities between crack and powder cocaine offenses by amending the previously imposed 100-to-1 sentencing disparity.
 Under the new legislation, the ratio was reduced to 18-to-1, meaning that it now took 28 grams of crack cocaine to trigger a mandatory minimum sentence of 5 years, instead of the previous 5 grams, while the threshold for powder cocaine remained at 500 grams.
 Furthermore, the Fair Sentencing Act eliminated the mandatory minimum sentence for simple possession of crack cocaine, emphasizing a more equitable approach to drug offenses.
-Though the act did not completely equalize the sentencing for crack and powder cocaine, it represented a significant step toward a fairer criminal justice system and demonstrated the government's commitment to addressing the consequences of previous drug policies.
+Although the act did not completely equalize the sentencing for crack and powder cocaine, it represented a significant step toward a fairer criminal justice system and demonstrated the government's commitment to addressing the consequences of previous drug policies.
 A \cite{ussc} report estimated that implementing the Fair Sentencing Act of 2010 resulted in the saving of 29,653 bed years \footnote{The same \cite{ussc} report also found that the Fair Sentencing Act of 2010 did not "disrupt the ongoing decline in the number of people who reported using crack cocaine in the last year."}.
@@
 
-I take three discrete approaches to my empirical strategy, establishing three unique counterfactual groups for identifying the impact of the Anti-Drug Abuse Act of 1986 and the Fair Sentencing Act of 2010 on college enrollment rates.
+I take three discrete approaches to my empirical strategy, establishing three unique counterfactual groups for identifying the impact of the Anti-Drug Abuse Act of 1986 and the Fair Sentencing Act of 2010.
 
-My first and primary empirical approach looks at changes in college enrollment rates in high drug arrest states relative to the low drug arrest states before and after the passage of both the 1986 and 2010 acts where high drug arrest states are defined as states above the 75th percentile two years before the passage of the federal law \footnote{For the Anti-Drug Abuse Act of 1986, states with high Black adult normalized arrest rates include CT, DC, GA, IL, MD, MA, MO, NJ, NY, and TN.
+My first and primary empirical approach looks at changes in college enrollment rates in high-intensity drug arrest states relative to the low-intensity drug arrest states before and after the passage of both the 1986 and 2010 acts.
+High-intensity drug arrest states are defined as states above the 75th percentile two years before the passage of the federal law \footnote{For the Anti-Drug Abuse Act of 1986, states with high Black adult normalized arrest rates include CT, DC, GA, IL, MD, MA, MO, NJ, NY, and TN.
 States with high Black juvenile normalized arrest rates include AR, CT, DE, DC, ME, MD, MA, MT, NJ, SD, and TN.
@@
 States with high Black juvenile normalized arrest rates include AL, DE, DC, GA, IL, KY, LA, MD, MS, MO, NJ, NC, PA, and SC.
-Note that states without any UCR Program drug arrest data are omitted from this analysis.
-See figure \ref{fig:heatmap} for a heatmap of high-intensity states in 1984.}.
-I primarily rely on data on adult arrests instead of juvenile arrests due to effect sizes and issues with pre-trends \footnote{As discussed in the introduction, \cite{aizer} finds that juvenile incarceration has a larger impact on education than adult incarceration.
-However, since states with high adult arrests tend to have high juvenile arrest rates, my estimates are robust to which arrest rate is used.}.
-I examine the first stage impact where the outcome is the change in drug-related arrest rates and the reduced form impact where the outcome is college-enrollment.
-The first stage is evaluated using an event-study model that allows me to assess the evolution of relative outcomes while controlling for fixed differences across states and national trends over time.
+Note that state-years without drug arrest data are omitted from the analysis.}.
+I primarily rely on data on adult arrests instead of juvenile arrests due to issues with pre-trends \footnote{As discussed in the introduction, \cite{aizer} finds that juvenile incarceration has a larger impact on education than adult incarceration.
+However, since states with high adult arrests tend to have high juvenile arrest rates, my estimates are robust to which arrest rate is used.
+I also present estimates using the juvenile arrest rate.}.
+I examine both the first-stage impact where the outcome is the change in drug-related arrest rates and the reduced-form impact where the outcome is college-enrollment.
+The first-stage is evaluated using an event-study model that allows me to assess the evolution of relative outcomes while controlling for fixed differences across states and national trends over time.
 Using data at the state ($s$) by year ($t$) level, I estimate:
@@
 In each event-study plot I also include the difference between the average of the post-period and pre-period coefficients; to account for potential pre-trends, I also report the average of the post-period coefficients, which is equivalent to the average treatment effect on the treated (ATT).
-When testing for pre-trends, if the first stage arrest rates are trending similarly before the passage of the Anti-Drug Abuse Act of 1986 and the Fair Sentencing Act of 2010, I expect the coefficients associated with pre-periods to be small and statistically insignificant.
+When testing for pre-trends, if the first-stage arrest rates are trending similarly before the passage of the Anti-Drug Abuse Act of 1986 and the Fair Sentencing Act of 2010, I expect the coefficients associated with pre-periods to be small and statistically insignificant.
 
-For the reduced form estimates, I follow a similar approach where use an event-study model identical to the model specified in \ref{eq:state_level_es}, except I replace ($s$) with($i$), as data is at the individual by year level.
-In addition to the event study analyses, I also report traditional difference-in-differences estimates as a summary of the effect across all post-expansion years using the following regression specification at the individual ($i$) by year ($t$) level:
+For the reduced-form estimates, I follow a similar approach where I use an event-study model identical to the model specified in \ref{eq:state_level_es}, except I replace ($s$) with($i$), as data is at the individual by year level.
+In addition to the event study regressions, I also report traditional difference-in-differences estimates as a summary of the effect across all post-expansion years using the following regression specification at the individual ($i$) by year ($t$) level:
 
@@
 where $\zeta_s$ and $\xi_t$ are fixed effects at the state and year level, $D_{i}$ is an indicator for belonging to the treatment group (in this case, states with high drug arrests), $Post_t$ is a time indicator for belonging to the post-period, $D_i Post_t$ is the interaction term where $\beta$ is potentially the causal effect of the federal policy if the identifying assumptions are satisfied, and $X'_{it}$ is a vector of control variables.
-For the reduced form estimates, I report three specifications of the difference-in-difference estimates: the first omits control variables and fixed effects, the second omits fixed effects, and the third is the full regression as specified in \ref{eq:did}.
+For the reduced-form estimates, I report three specifications of the difference-in-difference estimates: the first omits control variables and fixed effects, the second omits fixed effects, and the third is the full regression as specified in \ref{eq:did}.
 To increase power, I also include difference-in-difference regressions with a continuous treatment variable instead of an indicator variable.
 
-To address issues of low power associated with event study tests for pre-trends in both the first stage and reduced form regressions, I implemented suggestions from \cite{roth2022}, which include calculating the slope of a linear violation of parallel trends that a pre-trends test would detect a specified fraction of the time, the expected value of the coefficients conditional on passing the pre-test under the hypothesized trend, and useful statistics such as power, Bayes Factor, and likelihood ratio.
-If the parallel trends assumption is satisfied, then my first stage and reduced form estimates would identify the average treatment effect on the treated.
+To address issues of low power associated with event study tests for pre-trends in the first stage, I implemented suggestions from \cite{roth2022}, which include calculating the slope of a linear violation of parallel trends that a pre-trends test would detect a specified fraction of the time, the expected value of the coefficients conditional on passing the pre-test under the hypothesized trend, and useful statistics such as power, Bayes Factor, and likelihood ratio.
+If the parallel trends assumption is satisfied, then my first-stage and reduced-form estimates would identify the local causal effect.
 
-Overall, examining both the first stage and reduced form impact of the federal has the advantage of enabling me to estimate the impact of arrest rates on college enrollment for Black males.
-I conduct an instrumented difference-in-differences (DDIV) estimate where the endogenous variable is arrest rates and the instrument is an indicator for living in a high-intensity state.
+Overall, examining both the first-stage and reduced-form impact of the federal has the advantage of enabling me to estimate the impact of arrest rates on college enrollment for Black males.
+I use an instrumented difference-in-differences (DDIV) estimator where the endogenous variable is arrest rates and the instrument is an indicator for living in a high-intensity state.
 I follow the advice given in \cite{ddiv}.
@@
 Finally, for supplemental analysis, I also include a triple difference-differences specification in the appendix, where the first difference is pre and post-time periods, the second difference is race, and the third difference is living in a high or low-Black drug arrest state.
-If White men have a similar first stage pre-trend to Black males in high vs low-intensity states, the triple difference-difference specification will remove that bias from that specific pre-trend.
+If White men have a similar first-stage pre-trend to Black males in high vs low-intensity states, the triple difference-difference specification will remove that bias from that specific pre-trend.
 
-To test whether the identifying assumptions for the three counterfactual groups were satisfied, aside from including event-study plots, I included plots of the raw outcomes over time.
+To help test whether the identifying assumptions for the three counterfactual groups were satisfied, aside from including event-study plots, I include plots of the raw outcomes over time.
 
@@
 To conduct my analysis, I use data from three sources.
-My primary data source is the Current Population Survey (CPS) October Education Supplement from 1980-2016, which I accessed via the IPUMS-CPS database \citep{ipums_cps} \footnote{Following \cite{britton2022}, for most of my analysis of the Anti-Drug Abuse Act of 1986, I only use years from 1984 onwards.
-Further discussion of this point is included in the appendix.}.
+My primary data source is the Current Population Survey (CPS) October Education Supplement from 1980-2016, which I accessed via the IPUMS-CPS database \citep{ipums_cps} \footnote{Following \cite{britton2022}, for my analysis of the Anti-Drug Abuse Act of 1986, I only use data from years from 1984 and onwards due to potential pre-trends in earlier years.
+Further discussion is included in the appendix.}.
 The Current Population Survey Education Supplement (CPS) is an annual cross-sectional survey conducted by the United States Census Bureau and the Bureau of Labor Statistics, collecting data from a nationally representative sample of approximately 60,000 households.
@@
 For data on arrests, I used the Uniform Crime Reporting (UCR) Program Data from the \cite{ucr}.
-The UCR Program is a data collection initiative led by the FBI, which amasses crime statistics from local law enforcement agencies throughout the United States, and the UCR data is commonly used for crime-related social science research topics.
+The UCR Program is a data collection initiative led by the FBI, which amasses crime statistics from local law enforcement agencies throughout the United States, and the UCR data is commonly used for crime-related social science research.
 The UCR Program has data at the county-year level and includes information on the number of arrests for each arrest type (e.g.
-drug possession, drug distribution, assault, robbery, etc) and also records data on the age \footnote{The UCR data separately tracks arrest rates for adult and juvenile cases.} and race of the arrested.
+drug possession, drug distribution, assault, robbery, etc) and also records data on the age \footnote{The UCR data separately tracks arrest rates for adults and juveniles.} and race of the arrested.
 In my analysis, I use Black adult arrests and Black juvenile arrests related to all drug crimes \footnote{The universe of all drug crimes corresponds to code 18 in the UCR program data.
 The UCR program includes data on drug offenses at a more granular level, such as type of drug, weight, and sale to a minor.}.
-Since I needed arrest data at the state and year level, I constructed a normalized arrest rate per 100,000 by averaging the arrest rate for counties with available data in a state together and dividing by the state's population in the given year \footnote{The population in each state-year was taken from the CPS.}.
+Since I'm using arrest data at the state-by-year level, I constructed a normalized arrest rate per 100,000 by averaging the arrest rate for counties with available data in a state together, dividing by the state's population in the given year, and scaling up.
+\footnote{The population in each state-year was taken from the UCR.}.
 In any analysis where I used both UCR and CPS data, I merged the two datasets at the state and year level \footnote{The merged dataset is henceforth referenced as CPS-UCR merged dataset}.
@@
 First and foremost, many counties failed to report their arrest rates for certain years.
-Secondly, the UCR's hierarchical reporting system requires that only the most severe crime be recorded in cases of multiple offenses, which may skew the data.
+Secondly, the UCR's hierarchical reporting system requires that only the most severe crime be recorded in cases of multiple offenses, which may result in undercounting.
 Finally, variations in reporting practices among different law enforcement agencies, as well as changes in reporting standards over time, can affect the consistency and comparability of the data.
@@
 For example, the 99th percentile was 142 arrests in a certain state year, but the outlier would have over 1000 arrests.
-To deal with these extreme outliers (which are very likely to be erroneous), I implement a 95\% right tail winsorization \footnote{I use winsorization over trimming since it is likely the case that the outliers still belong to the distribution.}.
+To deal with these extreme outliers (which are very likely to be erroneous), I implement a 95\% right tail winsorization \footnote{I use winsorization over trimming since it is likely the case that the outliers still belong to the distribution and occurred because of reporting error.}.
 
-Finally, I used unemployment data at the state-by-year level from the \cite{unemployment_data}. For analysis at the state-by-year level, I simply collapsed the dataset.
+Finally, I used unemployment data at the state-by-year level from the \cite{unemployment_data}.
 
@@
 Tables 1 and A1 (in the appendix) report sample means separately for the pre and post-periods of both the Anti-Drug Abuse Act of 1986 and the Fair Sentencing Act of 2010.
-Table 1 uses the CPS-UCR linked dataset (which drops unmerged observations), while Table 2 uses the CPS dataset only.
+Table 1 uses the CPS-UCR linked dataset (which drops unmerged observations), while Table A1 uses the CPS dataset only.
 
@@
 The number of observations is slightly smaller in the CPS-UCR merged dataset, except for the 2010-2016 period which is much smaller (likely due to the missing UCR data from Florida).
-The "enrolled in college" row is approximately identical between Table 1 and Table 2, and the proportion of Blacks and males is also largely the same.
+The "enrolled in college" row is approximately identical between Table 1 and Table A1, and the proportion of Blacks and males is also largely the same.
 
@@
 
-In figure \ref{fig:heatmap} I presented a heatmap of Black adult drug-related arrests in 1984, two years before the passage of the Anti-Drug Abuse Act.
+In figure \ref{fig:heatmap}, I present a heatmap of Black adult drug-related arrests in 1984, two years before the passage of the Anti-Drug Abuse Act.
 I also present kernel density estimates of the distribution of arrest rates at the state level in figure \ref{fig:density_jb} with a vertical line denoting high-intensity states.
@@
 
-I first estimate the impact of the Anti-Drug Abuse Act of 1986 on drug-related arrest rates for Black adults and Black juveniles separately by looking at changes in arrest rates in high-drug arrest states relative to the low-drug arrest states before and after 1986.
+I first estimate the impact of the Anti-Drug Abuse Act of 1986 on drug-related arrest rates for Black adults by looking at changes in arrest rates in high-intensity relative to low-intensity states before and after 1986.
 
-The first stage results are presented in figures \ref{fig:ab_es_1986}, \ref{fig:ab_es_1986_nofe}, \ref{fig:jb_es_1986}, table 2, and table A2 in the appendix.
+The first-stage results are presented in figures \ref{fig:ab_es_1986}, \ref{fig:ab_es_1986_nofe}, \ref{fig:jb_es_1986}, table 2, and table A2 in the appendix.
 
 For Black adults, using the event study model detailed in equation \ref{eq:state_level_es}, I find an increase in drug-related arrest rate associated with the Anti-Drug Abuse Act with gains between 3.08 and 12.71 arrests per 100,000 during each post-expansion year.
-When using the event-study model specified in equation \ref{eq:state_level_es}, I find that the average between the post and pre-period coefficients is 2.96, and the ATT is a bit larger at 3.85 arrests with a similar standard error.
-The estimates for years 2 and 3 in the post-period are larger than the estimates for years 1 and 4, 5, and 6, indicating that the effect of the law took some time to "kick in", and the effect potentially decreased in the later years \footnote{I confirmed that the large standard errors in certain post-periods were not due to coding errors by regressing the outcome in said year minus outcome in year zero on the treatment group.}.
+When using the event-study model specified in equation \ref{eq:state_level_es}, I find that the average between the post and pre-period coefficients is 2.96, and the ATT \footnote{The ATT is calculated as the average of the post-period coefficients.} is a bit larger at 3.85 arrests with a similar standard error.
+The estimates for years 2 and 3 in the post-period are larger than the estimates for years 1 and 4, 5, and 6, indicating that the effect of the law took some time to "kick in", and the effect potentially decreased in the later years \footnote{I confirmed that the large standard errors in certain post-periods were not due to coding errors by regressing the outcome in the year of interest minus outcome in year zero on the treatment group.}.
 If I omit fixed effects from the event-study model (in Figure \ref{fig:ab_es_1986_nofe}), the event-study model estimates a larger and statistically significant effect, where the difference between the post and pre-periods is 7.1 with a robust, clustered standard error of 2.5.
@@
 
-To check for pre-trends in my event study model, I test the joint null hypothesis that all of the pretreatment event study coefficients are zero through an F-test, which I report at the bottom of each event study figure.
+To check for pre-trends in my event study model, I test the joint null hypothesis that all of the pre-treatment event study coefficients are zero via an F-test, which I report at the bottom of each event study figure.
 In this case, in figure \ref{fig:ab_es_1986}, I get a $p$-value of 0.27, which increases my confidence in the parallel trends assumption.
@@
 As an additional robustness check, I implement suggestions from \cite{roth2022} in figure \ref{fig:pre-trends_roth} \footnote{Using Roth's R package "pre-trends", I calculate the power defined as the probability that I would find a significant pre-trend under the hypothesized pre-trend, the Bayes Factor defined as the ratio of the probability of failing to reject the pretest under the hypothesized trend relative to under parallel trends, and the likelihood ratio which is defined to be the ratio of the likelihood of the observed coefficients under the hypothesized trend relative to under parallel trends.}.
-The results from Roth's pre-trend package imply that if there exists a pre-trend, a quadratic pre-trends is more worrying than the linear pre-trend, as I have less power to detect a significant pre-trend and the likelihood ratio is much higher.
-Notably, if there exists a pre-trend, figure \ref{fig:ab_es_1986} suggests that the pre-trend is possibly negative, which would imply that my first stage estimates are biased downwards.
+The results from Roth's pre-trend package imply that if there exists a pre-trend, a quadratic pre-trend is more worrying than the linear pre-trend, as I have less power to detect a significant pre-trend and the likelihood ratio is much higher.
+However, a quadratic pre-trend is also less likely than a linear one.
+Notably, if there exists a pre-trend, figure \ref{fig:ab_es_1986} suggests that the pre-trend is possibly negative, which would imply that my first-stage estimates have attenuation bias.
 
-This suggests that the Anti-Drug Abuse Act had an impact on the justice system by incarcerated people that would have otherwise not been incarcerated, ruling out the possibility that the Act might have only affected persons who would have been incarcerated regardless by extending their sentence length (through mandatory minimum sentencing requirements).
-Therefore, although the concern that the only populations impacted by the Anti-Drug Abuse Act would not have attended college in the absence of the Act is still valid \footnote{If the populations primarily impacted by the Anti-Drug Abuse Act were not going to attend college in the absence of the Act, I would expect the Act to have no impact on college enrollment.}, this result does provide some evidence against that argument.
+This suggests that the Anti-Drug Abuse Act had an impact on the justice system by incarcerated people that would have otherwise not been incarcerated, ruling out the possibility that the Act only impacted persons who would have been incarcerated regardless by extending their sentence length (through mandatory minimum sentencing requirements).
+Therefore, although the concern that the only populations impacted by the Anti-Drug Abuse Act would not have attended college in the absence of the Act is still valid \footnote{If the populations primarily impacted by the Anti-Drug Abuse Act were not going to attend college in the absence of the Act, I would expect the Act to have no impact on college enrollment.}, this result does provide some counter-evidence.
 
-\subsubsection{Reduced Form Estimates from High vs Low-Intensity States}
+\subsubsection{Reduced Form Estimates from Comparing High vs Low-Intensity States}
 
@@
 In figure \ref{fig:rs_es_1986}, I find that there is likely a pre-trend, as I calculate an f-statistic of 0.035.
-However, the pre-trend appears to be in the opposite direction of the effect, implying that if there existed a pre-trend, my model would underestimate the effect of the Anti-Drug Abuse Act on college enrollment, i.e.
-my estimate would be biased upwards.
-I calculate that the average between the post and pre-period coefficients is -0.0004, and the ATT is -0.02 which is equivalent to a 2\% decrease in the probability of enrollment, matching the estimate in \cite{britton2022}.
-Similar to the first stage, I find that the effect size increases at first in years 1, 2, and 3, then the effect stops increasing around year 4.
-Overall, I find my estimates reduced form estimates are quite noisy.
+However, the pre-trend appears to be in the opposite direction of the effect, implying that if there existed a linear pre-trend, my model would underestimate the effect of the Anti-Drug Abuse Act on college enrollment, i.e.
+my estimate would once again be attenuated.
+I calculate that the average between the post and pre-period coefficients is -0.0004, and the ATT is -0.02 which is equivalent to a 2\% decrease in the probability of college enrollment, matching the estimate in \cite{britton2022}.
+Similar to the first stage, I find that the effect size increases at first in years 1, 2, and 3, and then the effect stops increasing around year 4.
+Overall, I find my estimates reduced-form estimates are quite noisy.
 
 I also present simple difference-in-difference estimates of the treatment effect in tables 4 and 5.
-To increase power, I also calculated the same regression model, except I used continuous treatment (arrest rates) instead.
+To increase power, I also calculated the same regression model, except I used a continuous treatment (arrest rates) variable instead.
 My difference-in-difference estimates are consistent with the event-study results, as most are small, negative, and statistically insignificant.
@@
 
-In table 2, I present a simple table of means without any controls or fixed effects to consolidate the results from the first stage and reduced form models.
-Notably, in table 2, when examining a simple difference in means, the difference in college enrollment probability between pre and post-period for high and low-intensity states for Black adult drug-related arrests is -2.3\%, which matches the result in \cite{britton2022} The instrumented difference in difference estimate from this table is equivalent the ratio between the reduced form and first stage, which is -0.2326/3.332 = -0.0698 = -6.9\%.
+In table 2, I present a simple table of means without any controls or fixed effects to consolidate the results from the first-stage and reduced-form models.
+Notably, in table 2, when examining a simple difference in means, the difference in college enrollment probability between pre and post-period for high and low-intensity states for Black adult drug-related arrests is -2.3\%, which once again matches the result in \cite{britton2022} The instrumented difference in difference estimate from this table is equivalent the ratio between the reduced-form and first stage, which is -0.2326/3.332 = -0.0698 = -6.9\%.
 
-The more robust second stage DDIV results are estimated via 2SLS and are presented in table 3.
+The more robust second-stage instrumented difference-in-difference coefficients are estimated via 2SLS and are presented in table 3.
 Overall, I find a small negative effect of arrest rates on college enrollment in all three specifications; however, the coefficients are small and statistically insignificant with large standard errors.
 Notably, my 2SLS estimates are at least 10 times the magnitude of the OLS estimate (presented in column 1).
-If I scale the variables up, my most robust estimate (with fixed effects and control variables) implies that if the arrest rate increased by 1000 Black Adult drug-related arrests per 100,000, then the probability of college enrollment for a Black male would decline by approximately 2.5\%, once again, matching the estimate found in \cite{britton2022}.
+If I scale the variables up, my most robust estimate (with fixed effects and control variables) implies that if the arrest rate increased by 10 Black Adult drug-related arrests per 100,000, then the probability of college enrollment for a Black male would decline by approximately 2.5\%.
+My 2SLS estimate with just controls gives us a much smaller estimate, implying that if the arrest rate increased by 10 Black Adult drug-related arrests per 100,000, then the probability of college enrollment for a Black male would decline by approximately 0.4\%.
 
-To test for the weak-instrument problem, I also report F-statistics from the first stage regression, following conventional advice from \cite{staiger1997precise}.
+I also report F-statistics from the first-stage regression, following conventional advice from \cite{staiger1997precise}.
 In my case, I find an F-statistic ranging from 15.9 to 20.2, providing evidence that my estimates are likely not biased by the weak-instrument problem.
 
-\subsubsection{Additional Reduced Form Estimates}
+\subsubsection{Additional Reduced-Form Estimates}
 
@@
 When I use Black females as a counterfactual group, I find smaller, statistically insignificant estimates of approximately -1.6\%.
-To test for pre-trends, I plot the raw outcomes by treatment group overtime.
+To test for pre-trends, I plot the raw outcomes by treatment group over time.
 These outcome figures can be found in the appendix.
@@
 
-Notably, any effect is likely not due to the mandatory sentencing minimum, but rather, is due to the overall lightening of sentences / prosecutions.
-\cite{ussc} found that in the years before the Fair Sentencing Act was passed, the proportion in prison with minimum sentencing requirements was in the single digits.
+Due to pre-treatment trends in outcomes, I find it difficult to study the Fair Sentencing Act using my research design.
+The next few sections are mostly dedicated to discussing the failures associated with my approach.
+
+It is important to note that any effect on any outcome where the Fair Sentencing Act is the treatment is not due to the elimination of the mandatory sentencing minimum but rather, is due to the overall lightening of drug-related prosecutions.
+\cite{ussc} found that in the years before the Fair Sentencing Act was passed, the raw count of offenders in prison due to the minimum sentencing requirements was already in the single digits.
 
@@
 
-In this case, the pre-trend is trending in the same direction as the measured effect.
-I.e.
-my estimated effect is likely larger than the true effect.
-Using adult arrests, I find that the difference between the post and pre-period coefficients is -20.8, while the ATT is -22.8.
+Using adult arrests, I find that the difference between the post and pre-period coefficients is -20.8, while the ATT is -22.8 Black adult drug-related arrests per 100,000.
+However, in this case, the pre-trend is trending in the same direction as the measured effect.
+Therefore, my estimated effect is likely significantly larger than the true effect.
 
@@
 The results from comparing high to low-intensity states are presented in figure \ref{fig:rf_jb_es_2010} and tables A4 and A5 in the appendix.
-Similar to the first stage result, I find significant pre-trends trending in the same direction as the effect.
-I conclude that comparing high and low-intensity states is not an approach research design for measuring the reduced form impact of the Fair Sentencing Act on the probability of college enrollment.
+Similar to the first-stage result, I find significant pre-trends trending in the same direction as the effect.
+I conclude that comparing high and low-intensity states is not an approach research design for measuring the reduced-form impact of the Fair Sentencing Act on the probability of college enrollment.
 
-I next use White males as a counterfactual group to Black males, and the results are presented in table 14.
+I next use White males as a counterfactual group to Black males, and the results from the difference-in-differences regression are presented in table 14.
+Finally, I use Black females as a counterfactual group to Black males, and the results from the difference-in-differences regression are presented in table 15.
+For both estimates, the coefficient of interest is statistically significant and negative, which is the opposite of the expected result.
+This estimate is not very reliable and is likely driven by an invalid research design.
+
+As a rough test of the parallel trends assumption for comparing Black males to White males and Black females during the Fair Sentencing Act of 2010, I include graphs of raw outcomes over time in figures \ref{fig:raw_college_2010} and \ref{fig:raw_faminc_2010}.
+Although the parallel trends assumption looks reasonable in the college enrollment graph in figure \ref{fig:raw_college_2010}, the parallel trends assumption seems to be violated when plotting the family income covariate, demonstrated in figure \ref{fig:raw_faminc_2010}.
 
@@
 
-Due to significant pre-trends in both the first stage and reduced form estimates, I refrain from calculating a second stage estimate for the Fair Sentencing Act.
+Due to significant pre-trends in both the first-stage and reduced-form estimates, I refrain from calculating a second-stage estimate for the Fair Sentencing Act.
 
-\subsection{Robustness Checks} %update to reflect both 1986 and 2010
+\subsection{Robustness Checks} % update to reflect both 1986 and 2010
 
-I present numerous robustness checks.
+For the first empirical strategy where I compare high and low-intensity states, I repeat my calculations using Black juvenile arrests as a robustness check.
+I calculated both the first-stage and reduced form, and the results are presented in figures \ref{fig:jb_es_1986}, \ref{fig:rs_es_1986}, \ref{fig:fs_es_2010}, and \ref{fig:rf_jb_es_2010}.
+Overall, I find that the estimates are similar between the models using adult arrest and the models using juvenile arrests.
+Using juvenile arrests tends to lead to smaller estimates, but the pre-trends are likely more significant.
 
-For the first empirical strategy, I leverage variation in Black juvenile arrests as a robustness check.
-I calculated both the first-stage and reduced form, and the results are presented in figures \ref{fig:jb_es_1986} and \ref{fig:rs_es_1986}.
-Overall, I find that the estimates are similar between the models using adult arrest and the models using juvenile arrests.
-Using juvenile results tends to lead to smaller estimates, but at the same time, the pre-trends are potentially worse.
-
-As a robustness check for the reduced form estimates from comparing high vs low-intensity states, I run the same regressions using Black juvenile arrests instead of Black adult arrests, and I present the results in tables 6 and 7.
+As a robustness check for the reduced-form estimates from comparing high vs low-intensity states, I run the same regressions using Black juvenile arrests instead of Black adult arrests, and I present the results in tables 6 and 7.
 I also run two separate control experiments in tables 8 and 9.
-In table 8, I limit my sample to females exclusively, and in table 8, I use Black males aged 30-50 in 1986.
+In table 8, I limit my sample to females exclusively, and in table 9, I use Black males aged 30-50 in 1986.
 In both cases, I find very small, insignificant results.
 
-For the second stage estimate, I include multiple regression specifications in table 3.
-My 2SLS estimates are somewhat robust to model specification; however, the effect size does increase when I add fixed effects and control variables.
-
-To check the robustness of my additional reduced form estimates from using White males and Black females as counterfactual groups, I estimate the same model while restricting the sample to Males aged 30-50 in tables 12 and 13
+To check the robustness of my additional reduced-form estimates from using White males and Black females as counterfactual groups for the Anti-Drug Abuse Act, I estimate the same model while restricting the sample to Males aged 30-50 in tables 12 and 13 and find mostly insignificant results.
+I extend the same robustness check to the Fair Sentencing Act in tables 16 and 17, and I find some evidence that the parallel trends assumption is not holding, as my estimates tend to be large and statistically significant, especially in the control experiment using males aged 30-50.
 
@@
 
+I find some evidence that the Anti-Drug Abuse Act of 1986 modestly increased drug-related arrest rates and decreased college enrollment rates among Black men.
 To the best of my knowledge, my paper presents the first direct estimate of the relationship between drug-related arrest rates and college enrollment.
+I estimated that if the drug-arrest rate in Black adults increased by 10 persons per 100,000, the probability of college enrollment would decrease by 0.4\% to 2.5\%.
+
+Using the estimated average treatment effect on the treated (ATT=3.85) (to eliminate potential biases from pre-trends) for the Anti-Drug Abuse Act from the CPS-UCR merged sample, my back-of-the-envelope calculations approximately imply an approximate total increase of 2,600 Black adult drug-related arrests in each year in the treated states \footnote{Using population from data from the 1980 Census, I find approximately 68 million people reside in high-intensity states.
+Juvenile arrests are not included in this calculation.
+For see a list of treated states, see the empirical strategy section.}.
+When I apply my first-stage estimate to my second-stage estimates, I find that the total college enrollment in  treated states decreased by 900 to 5,600 students in each year \footnote{I calculated the change in college enrollment by using national college enrollment count for Black undergraduates in 1986 (776,000) from the Census multiplied by high-intensity state population to national population ratio in 1980 (68 million / 220 million), divided by 4 to account for the size of each entering class, multiplied by the ATT (3.85), multiplied by the second-stage estimated treatment effect.}.
+The upper range of my back-of-the-envelope calculations implies that spillover effects might exist.
+It is important to note that my back-of-the-envelope estimates are extremely imprecise and require all the causal assumptions to hold.
+
+I find limited results for the Fair Sentencing Act of 2010 due to parallel trend assumptions that are very unlikely to hold.
+The Fair Sentencing Act is hard to study from a causal inference perspective.
+The report by the \cite{ussc} presents a reasonable analysis of the impact by looking at changes in outcomes.
 
@@
 It is important to summarize and acknowledge several important issues this study faces.
-
 First, many assumptions must be satisfied for the estimates presented in this paper to be interpreted as causal.
-For the first stage and reduced form estimates, the parallel trends assumption must be satisfied.
-For the instrumented difference in differences estimate to be causal, the exclusion restriction must be satisfied.
+For the first-stage and reduced-form estimates, the parallel trends assumption must be satisfied, and for the instrumented difference in differences estimate to be causal, the exclusion restriction must also be satisfied.
 While I include many checks for these assumptions, some more convincing than others, certain assumptions may still be invalid.
-In particular, I found that the Fair Sentencing Act was especially difficult to study due to failed parallel trend assumptions.
 
@@
 Many counties failed to report arrest data, and it's highly unlikely that counties randomly failed to report data.
-Furthermore, since the population impacted by these Acts is so small, the CPS dataset may not be sufficiently powered to answer the research questions presented in this paper.
+Furthermore, since the subpopulation impacted by these acts is small, the CPS dataset may not be sufficiently powered to answer the research questions presented in this paper.
 
-Finally, it may be the case that the subpopulation impacted by these Acts would not have attended college with or without the treatment.
+Finally, it may be the case that the subpopulation impacted by these acts would not have attended college with or without the treatment.
 In other words, the local average treatment effect might have been 0, and in many instances, my estimates are very close to 0.
-However, it is unclear whether my estimates are small due to insufficient power and noise or the true local average treatment effect being 0.
-
-\subsection{Implications for Policy}
+However, it is unclear whether my estimates are small due to insufficient power and noise or the true local average treatment effect being zero.
 
@@
 Other ideas for future research include exploring the impact of state-level policies on arrest rates and educational outcomes.
-\cite{britton2022} uses differences in marijuana laws, and future research can leverage other drug laws while introducing modern methods such as synthetic control designs.
-
-other datasets e.g. ACA
-better arrest data, county/metropolitan level
-other outcomes
+\cite{britton2022} uses differences in marijuana laws, and future research can leverage variation in other drug laws while introducing modern methods such as synthetic control designs.
+Spillover effects may also be important to investigate.
+Further confirmation of the results in this paper using better-quality arrest data will result in much more precise and trustworthy estimates.
+In particular, there is still much to study about the Fair Sentencing Act of 2010, especially since I find my research design is not appropriate.
+With better datasets, future researchers can also focus on labor and health outcomes.
 
@@
   \section{Data}
-  I include a summary statistics table for the CPS data that is not merged with the UCR program data.
+  I include a summary statistics table for the CPS data that is not merged with the UCR program data. The CPS unmerged dataset is used in any analysis that does not require arrest data.
 
-  \section{Additional Results}
-  The contents...
   \section{First stage arrest rate estimates}
-  I include a table (A2) for the equation \ref{eq:state_level_es} estimates presented in figure \ref{fig:ab_es_1986}.
+  I include table A2 for the equation \ref{eq:state_level_es} estimates presented in figure \ref{fig:ab_es_1986}.
 
   In \cite{britton2022}, when examining the impact of the Anti-Drug Abuse Act of 1986, she commences her analysis in 1984 due to "fluctuations in Black college enrollment during the early 1980s that were unrelated to the emergence of drug markets \cite{nces}".
+I create an event study plot in figure \ref{fig:a3}, and my coefficients provide evidence that there were significant pre-trends before 1984.
 
   \section{Reduced form college enrollment estimates}
-  I include a table (A3) for the equation \ref{eq:state_level_es} estimates presented in figure \ref{fig:rs_es_1986}.
 
-  Although it is likely the case that my estimates of the impact of the Fair Sentencing Act of 2010 using high vs low-intensity states is biased by significant pre-trends, in table A4 and A5 I include simple difference-in-difference estimates under three similar specifications; table A4 uses discrete treatment while table A5 uses continuous treatment.
+  I include table A3 for the equation \ref{eq:state_level_es} estimates presented in figure \ref{fig:rs_es_1986}.
+
+  Although it is likely the case that my estimates of the impact of the Fair Sentencing Act of 2010 using high vs low-intensity states are biased by significant pre-trends, in tables A4 and A5 I include simple difference-in-difference estimates under three similar specifications; table A4 uses discrete treatment while table A5 uses continuous treatment.
 Overall my estimates imply a small negative effect on college enrollment probability, but my estimates are not sufficiently powered to be statistically significant.
@@
   In tables A6-A8, I include the triple difference-in-differences results.
+I find the estimates are similar across various model specifications.
 I use both adult and juvenile arrests for the Anti-Drug Abuse Act, but I omit the juvenile table from the Fair Sentencing Act analysis since the pre-trends assumption is already quite weak.
@@
   \clearpage
-  % First stage event study table
+  % first-stage event study table
   \import{../../output/tables/eventstudy}{eventstudy_firststage.tex}
